### 2016-11-12 ms.tex
I put the abscal paper under version control.

%%
%% Beginning of file 'sample.tex'
%%
%% Modified 2005 December 5
%%
%% This is a sample manuscript marked up using the
%% AASTeX v5.x LaTeX 2e macros.

%% The first piece of markup in an AASTeX v5.x document
%% is the \documentclass command. LaTeX will ignore
%% any data that comes before this command.

%% The command below calls the preprint style
%% which will produce a one-column, single-spaced document.
%% Examples of commands for other substyles follow. Use
%% whichever is most appropriate for your purposes.
%%
%%\documentclass[12pt,preprint]{aastex}

%% manuscript produces a one-column, double-spaced document:

%\documentclass{article}
%\documentclass[twocolumn]{aastex6}
\documentclass{aastex6}
%\documentclass[iop]{emulateapj}

%% preprint2 produces a double-column, single-spaced document:
%\documentclass[preprint2]{aastex}

%% Sometimes a paper's abstract is too long to fit on the
%% title page in preprint2 mode. When that is the case,
%% use the longabstract style option.

%% \documentclass[preprint2,longabstract]{aastex}

%% If you want to create your own macros, you can do so
%% using \newcommand. Your macros should appear before
%% the \begin{document} command.
%%
%% If you are submitting to a journal that translates manuscripts
%% into SGML, you need to follow certain guidelines when preparing
%% your macros. See the AASTeX v5.x Author Guide
%% for information.

%Packages
%\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue]{hyperref}
\usepackage{graphicx}
\usepackage{float}
%\usepackage{caption}
%\usepackage{subcaption}
\usepackage[caption=false]{subfig}

\usepackage{natbib}
\bibliographystyle{astroads}

\newcommand{\vdag}{(v)^\dagger}
\newcommand{\DHSres}{299 - 334}
\newcommand{\DHSresApprox}{300}
\newcommand{\DHSgap}{0.04}

\newcommand{\SOSSrange}{0.6 - 2.5~$\mu$m}
\newcommand{\SOSSrangeto}{0.6 to 2.5~$\mu$m}

%% You can insert a short comment on the title page using the command below.

%\slugcomment{DHS White Paper}

%% If you wish, you may supply running head information, although
%% this information may be modified by the editorial offices.
%% The left head contains a list of authors,
%% usually a maximum of three (otherwise use et al.).  The right
%% head is a modified title of up to roughly 44 characters.
%% Running heads will not print in the manuscript style.

\shorttitle{NIRCam's DHS Mode}
\shortauthors{Schlawin et al.}

%% This is the end of the preamble.  Indicate the beginning of the
%% paper itself with \begin{document}.

\begin{document}

%% LaTeX will automatically break titles if they run longer than
%% one line. However, you may use \\ to force a line break if
%% you desire.

\title{NIRCam Calibration Plan}

%% Use \author, \affil, and the \and command to format
%% author and affiliation information.
%% Note that \email has replaced the old \authoremail command
%% from AASTeX v4.0. You can use \email to mark an email address
%% anywhere in the paper, not just in the front matter.
%% As in the title, use \\ to force line breaks.

\author{E. Schlawin, M. Rieke, G. Rieke, K. Misselt}
\affil{Steward Observatory, Tucson AZ 85721}
\email{eas342@email.arizona.edu}

%% Notice that each of these authors has alternate affiliations, which
%% are identified by the \altaffilmark after each name.  Specify alternate
%% affiliation information with \altaffiltext, with one command per each
%% affiliation.

\altaffiltext{1}{Hubble Postdoctoral Fellow}

%% Mark off your abstract in the ``abstract'' environment. In the manuscript
%% style, abstract will output a Received/Accepted line after the
%% title and affiliation information. No date will appear since the author
%% does not have this information. The dates will be filled in by the
%% editorial office after submission.

\begin{abstract}
The James Webb Space Telescope (JWST) offers unprecedented sensitivity and stability for science.
\end{abstract}

%% Keywords should appear after the \end{abstract} command. The uncommented
%% example has been keyed in ApJ style. See the instructions to authors
%% for the journal to which you are submitting your paper to determine
%% what keyword punctuation is appropriate.

\keywords{instrumentation: spectrographs}

%% From the front matter, we move on to the body of the paper.
%% In the first two sections, notice the use of the natbib \citep
%% and \citet commands to identify citations.  The citations are
%% tied to the reference list via symbolic KEYs. The KEY corresponds
%% to the KEY in the \bibitem in the reference list below. We have
%% chosen the first three characters of the first author's name plus
%% the last two numeral of the year of publication as our KEY for
%% each reference.

%% Authors who wish to have the most important objects in their paper
%% linked in the electronic edition to a data center may do so by tagging
%% their objects with \objectname{} or \object{}.  Each macro takes the
%% object name as its required argument. The optional, square-bracket 
%% argument should be used in cases where the data center identification
%% differs from what is to be printed in the paper.  The text appearing 
%% in curly braces is what will appear in print in the published paper. 
%% If the object name is recognized by the data centers, it will be linked
%% in the electronic edition to the object data available at the data centers  
%%
%% Note that for sources with brackets in their names, e.g. [WEG2004] 14h-090,
%% the brackets must be escaped with backslashes when used in the first
%% square-bracket argument, for instance, \object[\[WEG2004\] 14h-090]{90}).
%%  Otherwise, LaTeX will issue an error.

\section{Introduction}

The James Webb Space Telescope \citep[JWST; e.g.][]{gardner2006SSRv} will need absolute calibration.

\section{Pan-Starrs Photometry}

\section{UKIRT Photometry}

\subsection{Tie-in to 2MASS Photometry}

The stars within the clusters explored will be tied to the measurements of the Sun.
\citet{rieke2008absIRcal} provide recommended adjustments to 2MASS photometry which match well with the Solar spectrum.
We can use existing 2MASS measurements of stars within the UKIRT field of view as a reference for the UKIRT photometry.
There are plenty of sources with 2MASS measurements.
For NGC 2420, for example, there are 300-400 stars within the neighboring arrays and 800 near the cluster (many of which will be contaminated by crowding).

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.4\columnwidth]{aladin_ngc2420_wfcam_square.png}
\caption{One of WFCam's 4 detectors near the cluster NGC 2420 which encompasses 315 objects from the 2MASS point source catalog.}\label{fig:wfcam3}
\end{figure}

\section{Cluster Properties}

The WEBDA database had parameters that were significantly different from the literature.
For example E(B-V) = 0.16 for NGC 6811 whereas \citet{molendaz2016spec6811} has E(B-V) = 0.05.
We therefore did a literature search for the most recent available cluster parameters.

\begin{table}
\centering
\caption{Cluster Parameters}\label{tab:clusterProp}
\begin{tabular}{lrrrr}
\hline \hline
Cluster   					&  E(B-V) 		& Distance Mod 	& [Fe/H] 			& Age \\
          					&     			&    (m - M)$_V$	& 	dex 			& Gyr \\
\hline \hline
NGC 2420\tablenotemark{a}	& 0.04		&  11.88			& -0.05			& 3.0 \\
NGC 6811\tablenotemark{b}	& 0.05 		& 10.29 $\pm$ 0.14	& 0.04 $\pm$ 0.01 	& 1.0 $\pm$ 0.1 \\
\hline
\end{tabular}
%\caption{G2V-type star saturation K band limits are shown for suggested sub-array sizes. The size affects the number of DHS that can be included, so the noise in the DHS spectra over 1.1 -- 1.9$\mu$m at the given saturation limit for a 1 hour transit is shown in column 4 at native R $\sim$ \DHSresApprox\ resolution.}\label{tab:SatSNRsubA}
\tablenotetext{a}{All parameters from \citet{pancino2010chem2420}.}
\tablenotetext{b}{Parameters from \citep{molendaz2016spec6811}}
\end{table}

\section{Spectral Typing of Candidate Analogs}

\subsection{Notes on using \texttt{mkclass}}

\subsubsection{Code System}
The library is organized into files like \texttt{t130l50p00.rbn}.
The \texttt{t130} specifies 10 $\times$ the class coding system of O3 through M9 visible in the code \texttt{code3spt.c}.
In this case, \texttt{t130} means code 13.0 and type B7.
The luminosity class is next \texttt{l50} means V.
We use the \texttt{libnor36} library, which appears to work with the "Roughtype 2" method for non-rectified data.
The code runs into segmentation faults if attempting Roughtype 1 with the \texttt{libnor36} library.

\section{Conclusions}

The James Webb Space Telescope will do unprecedented science with it's great calibration.

\section*{Acknowledgements}
%\acknowledgments

Funding for the NIRCam team is provided by NASA Goddard Spaceflight Center. This research has made use of the WEBDA database, operated at the Department of Theoretical Physics and Astrophysics of the Masaryk University.

%If used, some data was collected from the Open Exoplanet Catalogue \citep{rein2012openExoCat}.

%% In a manner similar to \objectname authors can provide links to dataset
%% hosted at participating data centers via the \dataset{} command.  The
%% second curly bracket argument is printed in the text while the first
%% parentheses argument serves as the valid data set identifier.  Large
%% lists of data set are best provided in a table (see Table 3 for an example).
%% Valid data set identifiers should be obtained from the data center that
%% is currently hosting the data.
%%
%% Note that AASTeX interprets everything between the curly braces in the 
%% macro as regular text, so any special characters, e.g. "#" or "_," must be 
%% preceded by a backslash. Otherwise, you will get a LaTeX error when you 
%% compile your manuscript.  Special characters do not 
%% need to be escaped in the optional, square-bracket argument.

%% In this section, we use  the \subsection command to set off
%% a subsection.  \footnote is used to insert a footnote to the text.

%% Observe the use of the LaTeX \label
%% command after the \subsection to give a symbolic KEY to the
%% subsection for cross-referencing in a \ref command.
%% You can use LaTeX's \ref and \label commands to keep track of
%% cross-references to sections, equations, tables, and figures.
%% That way, if you change the order of any elements, LaTeX will
%% automatically renumber them.

%% This section also includes several of the displayed math environments
%% mentioned in the Author Guide.

%% The equation environment wil produce a numbered display equation.

%% The \notetoeditor{TEXT} command allows the author to communicate
%% information to the copy editor.  This information will appear as a
%% footnote on the printed copy for the manuscript style file.  Nothing will
%% appear on the printed copy if the preprint or
%% preprint2 style files are used.

%% The eqnarray environment produces multi-line display math. The end of
%% each line is marked with a \\. Lines will be numbered unless the \\
%% is preceded by a \nonumber command.
%% Alignment points are marked by ampersands (&). There should be two
%% ampersands (&) per line.

%% Putting eqnarrays or equations inside the mathletters environment groups
%% the enclosed equations by letter. For instance, the eqnarray below, instead
%% of being numbered, say, (4) and (5), would be numbered (4a) and (4b).
%% LaTeX the paper and look at the output to see the results.

%% This section contains more display math examples, including unnumbered
%% equations (displaymath environment). The last paragraph includes some
%% examples of in-line math featuring a couple of the AASTeX symbol macros.

%% The displaymath environment will produce the same sort of equation as
%% the equation environment, except that the equation will not be numbered
%% by LaTeX.
%% If you wish to include an acknowledgments section in your paper,
%% separate it off from the body of the text using the \acknowledgments
%% command.

%% Included in this acknowledgments section are examples of the
%% AASTeX hypertext markup commands. Use \url without the optional [HREF]
%% argument when you want to print the url directly in the text. Otherwise,
%% use either \url or \anchor, with the HREF as the first argument and the
%% text to be printed in the second.

%\acknowledgments

%% To help institutions obtain information on the effectiveness of their
%% telescopes, the AAS Journals has created a group of keywords for telescope
%% facilities. A common set of keywords will make these types of searches
%% significantly easier and more accurate. In addition, they will also be
%% useful in linking papers together which utilize the same telescopes
%% within the framework of the National Virtual Observatory.
%% See the AASTeX Web site at http://aastex.aas.org/
%% for information on obtaining the facility keywords.

%% After the acknowledgments section, use the following syntax and the
%% \facility{} macro to list the keywords of facilities used in the research
%% for the paper.  Each keyword will be checked against the master list during
%% copy editing.  Individual instruments or configurations can be provided 
%% in parentheses, after the keyword, but they will not be verified.

%{\it Facilities:} \facility{Nickel}, \facility{HST (STIS)}, \facility{CXO (ASIS)}.

%% Appendix material should be preceded with a single \appendix command.
%% There should be a \section command for each appendix. Mark appendix
%% subsections with the same markup you use in the main body of the paper.

%% Each Appendix (indicated with \section) will be lettered A, B, C, etc.
%% The equation counter will reset when it encounters the \appendix
%% command and will number appendix equations (A1), (A2), etc.

\appendix

%% The reference list follows the main body and any appendices.
%% Use LaTeX's thebibliography environment to mark up your reference list.
%% Note \begin{thebibliography} is followed by an empty set of
%% curly braces.  If you forget this, LaTeX will generate the error
%% "Perhaps a missing \item?".
%%
%% thebibliography produces citations in the text using \bibitem-\cite
%% cross-referencing. Each reference is preceded by a
%% \bibitem command that defines in curly braces the KEY that corresponds
%% to the KEY in the \cite commands (see the first section above).
%% Make sure that you provide a unique KEY for every \bibitem or else the
%% paper will not LaTeX. The square brackets should contain
%% the citation text that LaTeX will insert in
%% place of the \cite commands.

%% We have used macros to produce journal name abbreviations.
%% AASTeX provides a number of these for the more frequently-cited journals.
%% See the Author Guide for a list of them.

%% Note that the style of the \bibitem labels (in []) is slightly
%% different from previous examples.  The natbib system solves a host
%% of citation expression problems, but it is necessary to clearly
%% delimit the year from the author name used in the citation.
%% See the natbib documentation for more details and options.

\bibliographystyle{apj}
\bibliography{abscal_biblio}

%\clearpage

%% Use the figure environment and \plotone or \plottwo to include
%% figures and captions in your electronic submission.
%% To embed the sample graphics in
%% the file, uncomment the \plotone, \plottwo, and
%% \includegraphics commands
%%
%% If you need a layout that cannot be achieved with \plotone or
%% \plottwo, you can invoke the graphicx package directly with the
%% \includegraphics command or use \plotfiddle. For more information,
%% please see the tutorial on "Using Electronic Art with AASTeX" in the
%% documentation section at the AASTeX Web site, http://aastex.aas.org/
%%
%% The examples below also include sample markup for submission of
%% supplemental electronic materials. As always, be sure to check
%% the instructions to authors for the journal you are submitting to
%% for specific submissions guidelines as they vary from
%% journal to journal.

%% This example uses \plotone to include an EPS file scaled to
%% 80% of its natural size with \epsscale. Its caption
%% has been written to indicate that additional figure parts will be
%% available in the electronic journal.

%\begin{figure}
%\epsscale{.80}
%\plotone{f1.eps}
%\caption{Derived spectra for 3C138 \citep[see][]{heiles03}. Plots for all sources are available
%in the electronic edition of {\it The Astrophysical Journal}.\label{fig1}}
%\end{figure}

%\clearpage

%% Here we use \plottwo to present two versions of the same figure,
%% one in black and white for print the other in RGB color
%% for online presentation. Note that the caption indicates
%% that a color version of the figure will be available online.
%%

%\begin{figure}
%\plottwo{f2.eps}{f2_color.eps}
%\caption{A panel taken from Figure 2 of \citet{rudnick03}. 
%See the electronic edition of the Journal for a color version 
%of this figure.\label{fig2}}
%\end{figure}

%% This figure uses \includegraphics to scale and rotate the still frame
%% for an mpeg animation.

%\begin{figure}
%\includegraphics[angle=90,scale=.50]{f3.eps}
%\caption{Animation still frame taken from \citet{kim03}.
%This figure is also available as an mpeg
%animation in the electronic edition of the
%{\it Astrophysical Journal}.}
%\end{figure}

%% If you are not including electonic art with your submission, you may
%% mark up your captions using the \figcaption command. See the
%% User Guide for details.
%%
%% No more than seven \figcaption commands are allowed per page,
%% so if you have more than seven captions, insert a \clearpage
%% after every seventh one.

%% Tables should be submitted one per page, so put a \clearpage before
%% each one.

%% Two options are available to the author for producing tables:  the
%% deluxetable environment provided by the AASTeX package or the LaTeX
%% table environment.  Use of deluxetable is preferred.
%%

%% Three table samples follow, two marked up in the deluxetable environment,
%% one marked up as a LaTeX table.

%% In this first example, note that the \tabletypesize{}
%% command has been used to reduce the font size of the table.
%% We also use the \rotate command to rotate the table to
%% landscape orientation since it is very wide even at the
%% reduced font size.
%%
%% Note also that the \label command needs to be placed
%% inside the \tablecaption.

%% This table also includes a table comment indicating that the full
%% version will be available in machine-readable format in the electronic
%% edition.

%% If you use the table environment, please indicate horizontal rules using
%% \tableline, not \hline.
%% Do not put multiple tabular environments within a single table.
%% The optional \label should appear inside the \caption command.

%% If the table is more than one page long, the width of the table can vary
%% from page to page when the default \tablewidth is used, as below.  The
%% individual table widths for each page will be written to the log file; a
%% maximum tablewidth for the table can be computed from these values.
%% The \tablewidth argument can then be reset and the file reprocessed, so
%% that the table is of uniform width throughout. Try getting the widths
%% from the log file and changing the \tablewidth parameter to see how
%% adjusting this value affects table formatting.

%% The \dataset{} macro has also been applied to a few of the objects to
%% show how many observations can be tagged in a table.

%% Tables may also be prepared as separate files. See the accompanying
%% sample file table.tex for an example of an external table file.
%% To include an external file in your main document, use the \input
%% command. Uncomment the line below to include table.tex in this
%% sample file. (Note that you will need to comment out the \documentclass,
%% \begin{document}, and \end{document} commands from table.tex if you want
%% to include it in this document.)

%% \input{table}

%% The following command ends your manuscript. LaTeX will ignore any text
%% that appears after it.

\end{document}

%%
%% End of file `sample.tex'.

### 2016-11-15 ms.tex
I added parameters for NGC 2506 from Leet et al. 2012.
I added some thoughts and pushing NIRCam to really bright stars. Also, I added acknowledgements to Pan-Starrs and references to photometr.

@@
 The James Webb Space Telescope (JWST) offers unprecedented sensitivity and stability for science.
+Several of the science areas, such as supernovae measurements for dark energy measurements will require high accuracy absolute calibration.
+We discuss a program to identify calibrators at the low end of the flux scale that will not saturate the NIRCam full frame mode.
+We obtain ground based photometry and spectroscopy of three clusters to find solar analog G2 V stars and a solar model spectrum to infer the fluxes in the NIRCam bands.
+Additionally, we discuss some of the NIRCam modes that can be used to tie JWST calibrations directly to primary calibrator stars.
 \end{abstract}
@@
 
+We obtained $grizy$ Pan-Starrs photometry for all three clusters \citep{magnier2013photLadder,schlafly2012photcal,tonry2012panstarrsPhot}.
+
 \section{UKIRT Photometry}
@@
 NGC 2420\tablenotemark{a}	& 0.04			&  11.88			& -0.05			& 3.0 \\
-NGC 6811\tablenotemark{b}	& 0.05 		& 10.29 $\pm$ 0.14	& 0.04 $\pm$ 0.01 	& 1.0 $\pm$ 0.1 \\
+NGC 2506\tablenotemark{b}	& 0.03 $\pm$0.04	&  				& 0.24 $\pm$ 0.06	& 2.3 $\pm$ 0.2 \\
+NGC 6811\tablenotemark{c}	& 0.05 			& 10.29 $\pm$ 0.14	& 0.04 $\pm$ 0.01 	& 1.0 $\pm$ 0.1 \\
 \hline
@@
 \tablenotetext{a}{All parameters from \citet{pancino2010chem2420}.}
-\tablenotetext{b}{Parameters from \citep{molendaz2016spec6811}}
+\tablenotetext{b}{Parameters from \citet{lee2012openClustphot}}
+\tablenotetext{c}{Parameters from \citet{molendaz2016spec6811}}
 \end{table}
@@
 
+\section{Ways to Observe Really Bright Stars With NIRCam}
+
+There are several ways to improve saturation limits:
+\begin{itemize}
+\item Cut down the aperture size with a Lyot stop. These have 19\% throughput, but make the PSF shapes strange.
+\item Use a neutral density square in the coronagraph mask.
+The neutral density filters have an attenuation of around 10$^3$ or 7.5 mags.
+A color correction would have to be applied for the neutral density filter (since it is wavelength dependent) when transferring to an un-occulted region
+\item Use a long wavelength grism to spread out the light - this could be used in conjunction with a neutral density square
+\item Use a narrowband filter, such as F121N
+\item Use a small subarray - 64 $\times$ 64 is supported for science. There will be an engineering jitter monitoring test with an 8 $\times$ 8 subarray 
+\end{itemize}
+
 \section{Conclusions}
@@
 This research has made use of the WEBDA database, operated at the Department of Theoretical Physics and Astrophysics of the Masaryk University.
+Observations reported here were obtained at the MMT Observatory, a joint facility of the University of Arizona and the Smithsonian Institution.
+The Pan-STARRS1 Surveys (PS1) have been made possible through contributions of the Institute for Astronomy, the University of Hawaii, the Pan-STARRS Project Office, the Max-Planck Society and its participating institutes, the Max Planck Institute for Astronomy, Heidelberg and the Max Planck Institute for Extraterrestrial Physics, Garching, The Johns Hopkins University, Durham University, the University of Edinburgh, Queen's University Belfast, the Harvard-Smithsonian Center for Astrophysics, the Las Cumbres Observatory Global Telescope Network Incorporated, the National Central University of Taiwan, the Space Telescope Science Institute, the National Aeronautics and Space Administration under Grant No.
+NNX08AR22G issued through the Planetary Science Division of the NASA Science Mission Directorate, the National Science Foundation under Grant No.
+AST-1238877, the University of Maryland, and Eotvos Lorand University (ELTE) and the Los Alamos National Laboratory.
 

### 2016-11-23 ms.tex
I put in an acknowledgement to psynphot.
I added the 5 transfer plan George and I discussed to go from direct bright calibrators to faint ones.

@@
 \usepackage{natbib}
+%\usepackage{pdflscape}
 \bibliographystyle{astroads}
@@
 
-The James Webb Space Telescope \citep[JWST; e.g.][]{gardner2006SSRv} will need absolute calibration.
-
-\section{Pan-Starrs Photometry}
-
-We obtained $grizy$ Pan-Starrs photometry for all three clusters \citep{magnier2013photLadder,schlafly2012photcal,tonry2012panstarrsPhot}.
-
-\section{UKIRT Photometry}
-
-\subsection{Tie-in to 2MASS Photometry}
-
-The stars within the clusters explored will be tied to the measurements of the Sun.
-\citet{rieke2008absIRcal} provide recommended adjustments to 2MASS photometry which match well with the Solar spectrum.
-We can use existing 2MASS measurements of stars within the UKIRT field of view as a reference for the UKIRT photometry.
-There are plenty of sources with 2MASS measurements.
-For NGC 2420, for example, there are 300-400 stars within the neighboring arrays and 800 near the cluster (many of which will be contaminated by crowding).
-
-\begin{figure}[!hbtp]
-\centering
-\includegraphics[width=.4\columnwidth]{aladin_ngc2420_wfcam_square.png}
-\caption{One of WFCam's 4 detectors near the cluster NGC 2420 which encompasses 315 objects from the 2MASS point source catalog.}\label{fig:wfcam3}
-\end{figure}
+The James Webb Space Telescope \citep[JWST; e.g.][]{gardner2006SSRv} will need absolute calibration for many of its science goals.
 
@@
 
+\section{Photometry}
+
+We obtained $grizy$ Pan-Starrs photometry for all three clusters \citep{magnier2013photLadder,schlafly2012photcal,tonry2012panstarrsPhot}.
+We also looked up the $g$ - $r$ colors
+
+\section{UKIRT Photometry}
+
+\subsection{Tie-in to 2MASS Photometry}
+
+The stars within the clusters explored will be tied to the measurements of the Sun.
+\citet{rieke2008absIRcal} provide recommended adjustments to 2MASS photometry which match well with the Solar spectrum.
+We can use existing 2MASS measurements of stars within the UKIRT field of view as a reference for the UKIRT photometry.
+There are plenty of sources with 2MASS measurements.
+For NGC 2420, for example, there are 300-400 stars within the neighboring arrays and 800 near the cluster (many of which will be contaminated by crowding).
+
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.4\columnwidth]{aladin_ngc2420_wfcam_square.png}
+\caption{One of WFCam's 4 detectors near the cluster NGC 2420 which encompasses 315 objects from the 2MASS point source catalog.}\label{fig:wfcam3}
+\end{figure}
+
 \section{Spectral Typing of Candidate Analogs}
@@
 
-\section{Ways to Observe Really Bright Stars With NIRCam}
+\section{Transferring to Directly Calibrated Sources}
+
+In addition to observing the primary JWST standards for absolute calibration, it will be possible to observe stars with direct calibration.
+
+\begin{table}
+\centering
+\caption{Direct Calibrated Source to Deep Calibrator}\label{tab:clusterProp}
+\begin{tabular}{lrrrrrr}
+\hline \hline
+Step		& Source						& Spectral Type	& K Mag		& ND Filter		& Subarray	& Filter \\
+\hline \hline
+1		& Direct Calibrator\tablenotemark{a}	& G2 V 			& -1.49		& On	&	32$\times$32	& F466N	\\
+2		& Medium Calibrator				& G2 V			& 6  			& On  &	32$\times$32	& F466N    \\
+3		& Medium Calibrator				& G2 V			& 6  			& Off &	32$\times$32	& F466N    \\
+4		& Faint Calibrator				& G2 V			& 16 			& Off &	32$\times$32	& F466N    \\
+5		& Faint Calibrator				& G2 V			& 16 			& Off &	32$\times$32	& F444W    \\
+6		& Faint Calibrator				& G2 V			& 16 			& Off &	Full Array  	& F444W    \\
+%         &                                      & 
+%
+%Parameter  				&  Step 1			& Step 2			& Step 3			& Step 4 			& Step 5		& Step 6 \\
+%\hline \hline
+%Source					& Direct Calibrator\tablenotemark{a}	& Medium Calibrator	& Medium Calibrator	& Faint Cluster Star	& Faint Cluster Star & Faint Cluster Star\\
+%Spectral Type				& G2 V			& G2 V			& G2 V			& G2 V			& G2 V	& G2 V \\
+%K magnitude				& -1.49			& 6				& 6				& 16				& 16		& 16 \\
+%Neutral Density Filter			& On				& On				& Off				& Off				& Off		& Off\\
+%Subbarray					& 32$\times$32		& 32$\times$32		& 32$\times$32		& 32$\times$32		& 32$\times$32	& Full Frame \\
+%Filter						& F466N			& F466N			& F466N			& F466 N			& F444W 	& F444W\\
+\hline
+\end{tabular}
+\tablenotetext{a}{Any directly calibrated bright source such as the MSX calibrators \citep{price2004msxCal}, $\alpha$ Cen	 A or Vega.}
+\end{table}
+
+\subsection{Ways to Observe Really Bright Stars With NIRCam}
 
@@
 \end{itemize}
+
+Sensitivity and saturation limits make use of \texttt{pysynphot} \citep{lim2015pysynphot} with Phoenix stellar models \citep{allard2012phoenix} ranging from 4.0 to 5.0 in log(g).
 

### 2016-11-24 ms.tex
I added minor updates to the description to the transfer while I wrestle with webbpsf and pynrc for the weird bright source modes.

--- 2016-11-15 ms.tex
@@
 
-\section{Ways to Observe Really Bright Stars With NIRCam}
+\clearpage
+\section{Transferring to Directly Calibrated Sources}
+
+The primary JWST standards for absolute calibration have been tied to directly calibrated photometric sources through transfers, such as with HST's STIS instrument.
+As an independent check on those transfers, NIRCam can be used to observe those directly calibrated sources and transfer from the brightest ($K \sim -1$) sources all the way to the faintest calibrators ($K \sim 16$)
+Observing these bright sources (which are bright naked eye stars!) with JWST's NIRCam can be achieved with a combination of narrowband filters, small subarray sizes, a Lyot stop pupil mask (19\% transmission) and a neutral density (ND) filter.
+The same configuration can then be used on
+
+\begin{table}
+\centering
+\caption{Conversion from Directly Calibrated Source to Deep Calibrator}\label{tab:clusterProp}
+\begin{tabular}{lrrrrrrr}
+\hline \hline
+Step		& Source						& Spectral Type	& K Mag		& ND Filter		& Subarray	& Filter  & t$_{exp}$\\
+\hline \hline
+1		& Direct Calibrator\tablenotemark{a}	& G2 V 			& -1.49		& On	&	32$\times$32	& F466N	& \\
+2		& Medium Calibrator				& G2 V			& 12  		& On  &	32$\times$32	& F466N  &  \\
+3		& Medium Calibrator				& G2 V			& 6  			& Off &	32$\times$32	& F466N  &  \\
+4		& Faint Calibrator				& G2 V			& 16 			& Off &	32$\times$32	& F466N  &  \\
+5		& Faint Calibrator				& G2 V			& 16 			& Off &	32$\times$32	& F444W  &  \\
+6		& Faint Calibrator				& G2 V			& 16 			& Off &	Full Array  	& F444W  &  \\
+\hline
+\end{tabular}
+\tablenotetext{a}{Any directly calibrated bright source such as the MSX calibrators \citep{price2004msxCal}, Sirius, $\alpha$ Cen A or Vega.}
+\vspace{0.05in}
+\end{table}
+
+\subsection{Ways to Observe Really Bright Stars With NIRCam}
 
@@
 
-\section{Conclusions}
-
-The James Webb Space Telescope will do unprecedented science with it's great calibration.
+Sensitivity and saturation limits make use of \texttt{pysynphot} \citep{lim2015pysynphot} with Phoenix stellar models \citep{allard2012phoenix} ranging from 4.0 to 5.0 in log(g).
 

### 2016-11-26 ms.tex
I added a plot to illustrate the proposed NIRCam sensitivity ladder. Still needs a legend.

@@
 \hline \hline
-1		& Direct Calibrator\tablenotemark{a}	& G2 V 			& -1.49		& On	&	32$\times$32	& F466N	& \\
+1		& Direct Calibrator\tablenotemark{a}	& A1 V- G2 		& -1.35		& On	&	32$\times$32	& F466N	& \\
 2		& Medium Calibrator				& G2 V			& 12  		& On  &	32$\times$32	& F466N  &  \\
@@
 \end{table}
+
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.7\columnwidth]{sensitivity_ladder.pdf}
+\caption{Sensitivity ladder going from a narrowband, sub-array, neutral density filter observation of Sirius all the way to a wide band, full array, non-neutral density filter of a faint calibrator.}\label{fig:sensitityLadder}
+\end{figure}
 

### 2016-11-28 ms.tex
I added some more tweaks to the discussion of the ND filter and integration times needed.

@@
 The primary JWST standards for absolute calibration have been tied to directly calibrated photometric sources through transfers, such as with HST's STIS instrument.
-As an independent check on those transfers, NIRCam can be used to observe those directly calibrated sources and transfer from the brightest ($K \sim -1$) sources all the way to the faintest calibrators ($K \sim 16$)
-Observing these bright sources (which are bright naked eye stars!) with JWST's NIRCam can be achieved with a combination of narrowband filters, small subarray sizes, a Lyot stop pupil mask (19\% transmission) and a neutral density (ND) filter.
+As an independent check on those transfers, NIRCam can be used to observe those directly calibrated sources and transfer from the brightest ($K \sim -1$) sources all the way to the faintest calibrators ($K \sim 16$).
+Observing these bright sources (which are bright naked eye stars) with JWST's NIRCam can be achieved with a combination of narrowband filters, small subarray sizes, a Lyot stop pupil mask (19\% transmission) and a neutral density (ND) filter.
 The same configuration can then be used on
@@
 \hline \hline
-Step		& Source						& Spectral Type	& K Mag		& ND Filter		& Subarray	& Filter  & t$_{exp}$\\
+Step		& Source						& Spectral Type	& K Mag		& ND Filter		& Subarray	& Filter  & t$_{exp} (s) $\\
 \hline \hline
-1		& Direct Calibrator\tablenotemark{a}	& A1 V- G2 		& -1.35		& On	&	32$\times$32	& F466N	& \\
+1		& Direct Calibrator\tablenotemark{a}	& A1 V- G2 V		& -1.35		& On	&	32$\times$32	& F466N	& 0.1 \\
 2		& Medium Calibrator				& G2 V			& 12  		& On  &	32$\times$32	& F466N  &  \\
@@
 4		& Faint Calibrator				& G2 V			& 16 			& Off &	32$\times$32	& F466N  &  \\
-5		& Faint Calibrator				& G2 V			& 16 			& Off &	32$\times$32	& F444W  &  \\
-6		& Faint Calibrator				& G2 V			& 16 			& Off &	Full Array  	& F444W  &  \\
+5		& Faint Calibrator				& G2 V			& 16 			& Off &	Full Frame	& F466N  &  \\
+6		& Faint Calibrator				& G2 V			& 16 			& Off &	Full Frame  	& F444W  &  \\
 \hline
@@
 \item Use a neutral density square in the coronagraph mask.
-The neutral density filters have an attenuation of around 10$^3$ or 7.5 mags.
-A color correction would have to be applied for the neutral density filter (since it is wavelength dependent) when transferring to an un-occulted region
+The neutral density filters have an attenuation of around 10$^2.6$ or 6.5 mags.
+A color correction would have to be applied for the neutral density filter (since it is wavelength dependent) when transferring to an un-occulted region.
+Additionally, the Lyot stop that must be in place to use the neutral density filter has a throughput of 19\%, so the total improvement is 8.3 mags
 \item Use a long wavelength grism to spread out the light - this could be used in conjunction with a neutral density square

### 2016-11-30 ms.tex
I added figures for CMD diagrams and fiber placements.
I updated the references for NGC 2506 and redid the flux_diagram to something hopefully more intuitive.

@@
 
-\shorttitle{NIRCam's DHS Mode}
+\shorttitle{NIRCam Flux Calibration}
 \shortauthors{Schlawin et al.}
@@
 The James Webb Space Telescope \citep[JWST; e.g.][]{gardner2006SSRv} will need absolute calibration for many of its science goals.
+Many studies of dark energy make use of Type Ia Supernovae as standard candles and improvements to the absolute flux calibration are important for improving their luminosity distances.
 
@@
 \caption{Cluster Parameters}\label{tab:clusterProp}
-\begin{tabular}{lrrrr}
+\begin{tabular}{lrrrc}
 \hline \hline
@@
 \hline \hline
-NGC 2420\tablenotemark{a}	& 0.04			&  11.88			& -0.05			& 3.0 \\
-NGC 2506\tablenotemark{b}	& 0.03 $\pm$0.04	&  				& 0.24 $\pm$ 0.06	& 2.3 $\pm$ 0.2 \\
-NGC 6811\tablenotemark{c}	& 0.05 			& 10.29 $\pm$ 0.14	& 0.04 $\pm$ 0.01 	& 1.0 $\pm$ 0.1 \\
+NGC 2420\tablenotemark{a}	& 0.04 $\pm$0.03	&  11.88 $\pm$ 0.27	& -0.05 $\pm$ 0.03	& 3 $\pm$ 1 \\
+NGC 2506\tablenotemark{b}	& 0.058 $\pm$ 0.001	&  12.75 $\pm$ 0.10 	& -0.32 $\pm$ 0.03	& 1.85 $\pm$ 0.05 \\
+NGC 6811\tablenotemark{c}	& 0.05 $\pm$0.02	& 10.29 $\pm$ 0.14	& 0.04 $\pm$ 0.01 	& 1.0 $\pm$ 0.1 \\
 \hline
@@
 \tablenotetext{a}{All parameters from \citet{pancino2010chem2420}.}
-\tablenotetext{b}{Parameters from \citet{lee2012openClustphot}}
+\tablenotetext{b}{Parameters from \citet{anthonytwarog2016wiyn2506}. Error bars are formal standard errors of the mean, not necessarily capturing systematics.}
 \tablenotetext{c}{Parameters from \citet{molendaz2016spec6811}}
@@
 
-\section{Photometry}
+\section{Pan-Starrs Photometry}
 
@@
 We also looked up the $g$ - $r$ colors
+
+\begin{figure*}[!t]
+\centering
+\subfloat[NGC 2420]{
+	\includegraphics[width=0.5\textwidth]{sources_ngc2420.png}
+	\label{fig:cmdNGC6811}
+	}
+\subfloat[NGC 2506]{
+	\includegraphics[width=0.5\textwidth]{sources_ngc2506.png}
+	\label{fig:cmdNGC2506}
+	}
+\\
+\subfloat[NGC 6811]{
+	\includegraphics[width=0.5\textwidth]{sources_ngc6811.png}
+	\label{fig:cmdNGC6811}
+	}
+	\caption{Color-magnitudes of the 3 clusters.}
+	\label{fig:cmdPS}
+\end{figure*}
 
@@
 \caption{One of WFCam's 4 detectors near the cluster NGC 2420 which encompasses 315 objects from the 2MASS point source catalog.}\label{fig:wfcam3}
+\end{figure}
+
+\section{NIRCam Footprint}
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.4\columnwidth]{nircam_fov_fibers.pdf}
+\caption{NGC 2420 fibers on the first pass with the FOV of both the A and B modules of NIRCam.
+Only 10 stars fit within NIRCam's FOV.}\label{fig:NCFOV}
 \end{figure}
@@
 \centering
-\includegraphics[width=.7\columnwidth]{sensitivity_ladder.pdf}
-\caption{Sensitivity ladder going from a narrowband, sub-array, neutral density filter observation of Sirius all the way to a wide band, full array, non-neutral density filter of a faint calibrator.}\label{fig:sensitityLadder}
+\includegraphics[width=.6\columnwidth]{flux_ladder.pdf}
+\caption{Sensitivity ladder going a sub-array, neutral density filter observation a MSX standard to a full array, non-neutral density filter of a faint calibrator.}\label{fig:sensitityLadder}
 \end{figure}

### 2016-12-01 ms.tex
I added a comparison of MSX and NIRCam filters.

@@
 Observing these bright sources (which are bright naked eye stars) with JWST's NIRCam can be achieved with a combination of narrowband filters, small subarray sizes, a Lyot stop pupil mask (19\% transmission) and a neutral density (ND) filter.
-The same configuration can then be used on
+The same configuration can then be used on move to fainter sources.
+
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.4\columnwidth]{msx_nircam_filt.pdf}
+\caption{NIRCam filters as compared to the MSX short wavelength filters from \citet{egan1999msxGuide}. F430M best matches the MSX filters.}\label{fig:NCFOV}
+\end{figure}
 
@@
 \caption{Conversion from Directly Calibrated Source to Deep Calibrator}\label{tab:clusterProp}
-\begin{tabular}{lrrrrrrr}
+\begin{tabular}{lrrrrrr}
 \hline \hline
-Step		& Source						& Spectral Type	& K Mag		& ND Filter		& Subarray	& Filter  & t$_{exp} (s) $\\
+Step		& Source						& Spectral Type	& K Mag		& ND Filter		& Subarray	& t$_{exp} (s) $\\
 \hline \hline
-1		& Direct Calibrator\tablenotemark{a}	& A1 V- G2 V		& -1.35		& On	&	32$\times$32	& F466N	& 0.1 \\
-2		& Medium Calibrator				& G2 V			& 12  		& On  &	32$\times$32	& F466N  &  \\
-3		& Medium Calibrator				& G2 V			& 6  			& Off &	32$\times$32	& F466N  &  \\
-4		& Faint Calibrator				& G2 V			& 16 			& Off &	32$\times$32	& F466N  &  \\
-5		& Faint Calibrator				& G2 V			& 16 			& Off &	Full Frame	& F466N  &  \\
-6		& Faint Calibrator				& G2 V			& 16 			& Off &	Full Frame  	& F444W  &  \\
+1		& MSX Calibrator\tablenotemark{a}	& A1 V to M0 III		& -3 to 0.1		& On	&	64$\times$64	&  0.1 \\
+2		& Bright JWST Calibrator			& G2 V			& 6	  		& On  &	32$\times$32	&   \\
+3		& Medium Calibrator				& G2 V			& 6  			& Off &	32$\times$32	&   \\
+4		& Faint Calibrator				& G2 V			& 16 			& Off &	32$\times$32	&   \\
+5		& Faint Calibrator				& G2 V			& 16 			& Off &	Full Frame	&   \\
+6		& Faint Calibrator				& G2 V			& 16 			& Off &	Full Frame  	&   \\
 \hline
 \end{tabular}
-\tablenotetext{a}{Any directly calibrated bright source such as the MSX calibrators \citep{price2004msxCal}, Sirius, $\alpha$ Cen A or Vega.}
+\tablenotetext{a}{Any directly calibrated bright source such as the MSX calibrators \citep{price2004msxCal}, (which include Sirius and Vega) or alternatively $\alpha$ Cen A.}
 \vspace{0.05in}
@@
 \end{itemize}
+
+One could also defocus the stars with a weak lens, but the longer read times needed to capture the hexagon of the weak lens end up with saturation limits that are not as good as the coronagraph.
 

### 2016-12-02 ms.tex
I described the corographic PSF and how that might complicate photometry a bit.

@@
 
-\author{E. Schlawin, M. Rieke, G. Rieke, K. Misselt}
+\author{E. Schlawin, Jarron Leisenring, M. Rieke, G. Rieke, K. Misselt}
 \affil{Steward Observatory, Tucson AZ 85721}
@@
 Sensitivity and saturation limits make use of \texttt{pysynphot} \citep{lim2015pysynphot} with Phoenix stellar models \citep{allard2012phoenix} ranging from 4.0 to 5.0 in log(g).
+
+\subsubsection{Complications with PSF}
+A Lyot pupil mask must be used when imaging through the neutral density squares since the wedges that redirect light through NIRCam's corographic masks and neutral density squares are co-located with the Lyot stop pupil masks.
+In addition to lowering the transmission by a factor of 0.19\%, the Lyot stops spread out the PSF as compared to direct imaging.
+Figure \ref{fig:psfComparison} shows example PSFs calculated with \texttt{webbpsf} \citep{perrin2012webbpsf}.
+Figure \ref{fig:psfDirect} shows the direct image PSF versus the the coronographic PSF (Figure \ref{fig:psfND}) both normalized to the peak pixel.
+
+When using the ND filter and Lyot stop, the aperture photometry must account for the large secondary peaks of the PSF.
+This can be accomplished with a large aperture covering all the secondary peaks assuming that the background levels are low and that there are no nearby sources.
+Alternatively, one could extract the flux from the core of the PSF.
+
+\begin{figure*}
+\centering
+\subfloat[Direct Imaging PSF]{
+	\includegraphics[width=0.45\textwidth]{psf_direct.pdf}
+	\label{fig:psfDirect}
+	}
+\subfloat[NGC 2506]{
+	\includegraphics[width=0.45\textwidth]{psf_ND.pdf}
+	\label{fig:psfND}
+	}
+	\caption{The direct imaging PSF and coronagraphic PSF which is modified by the Lyot stop from \texttt{webbpsf}.
+Both images are normalized by the peak pixel value and have arbitrary array positions.
+Aperture photometry of the sources imaged through the corograph will have to use a large aperture encompassing the 6 outer peaks or apply careful background subtraction.
+Both PSFs were calculated for NIRCam's long wavelength channel with a F444W filter.}
+	\label{fig:psfComparison}
+\end{figure*}
 

### 2016-12-02 ms.tex
I corrected the optical density of the ND filter.

@@
 \item Use a neutral density square in the coronagraph mask.
-The neutral density filters have an attenuation of around 10$^2.6$ or 6.5 mags.
+The neutral density filters have an attenuation of around 10$^3$ or 7.5 mags.
 A color correction would have to be applied for the neutral density filter (since it is wavelength dependent) when transferring to an un-occulted region.
-Additionally, the Lyot stop that must be in place to use the neutral density filter has a throughput of 19\%, so the total improvement is 8.3 mags
+Additionally, the Lyot stop that must be in place to use the neutral density filter has a throughput of 19\%, so the total improvement is 8.8 mags
 \item Use a long wavelength grism to spread out the light - this could be used in conjunction with a neutral density square

### 2016-12-03 ms.tex
I completed the NIRCam flux ladder w/ eposure times needed.

@@
 \caption{Conversion from Directly Calibrated Source to Deep Calibrator}\label{tab:clusterProp}
-\begin{tabular}{lrrrrrr}
+\begin{tabular}{lrrrrrrr}
 \hline \hline
-Step		& Source						& Spectral Type	& K Mag		& ND Filter		& Subarray	& t$_{exp} (s) $\\
+Step		& Source						& Spectral Type	& K Mag		& ND Filter		& Subarray	& Filter & t$_{exp} (s) $\\
 \hline \hline
-1		& MSX Calibrator\tablenotemark{a}	& A1 V to M0 III		& -3 to 0.1		& On	&	64$\times$64	&  0.1 \\
-2		& Bright JWST Calibrator			& G2 V			& 6	  		& On  &	32$\times$32	&   \\
-3		& Medium Calibrator				& G2 V			& 6  			& Off &	32$\times$32	&   \\
-4		& Faint Calibrator				& G2 V			& 16 			& Off &	32$\times$32	&   \\
-5		& Faint Calibrator				& G2 V			& 16 			& Off &	Full Frame	&   \\
-6		& Faint Calibrator				& G2 V			& 16 			& Off &	Full Frame  	&   \\
+1		& MSX Calibrator\tablenotemark{a}	& A1 V to M0 III		& -3 to 0.1		& On	&	64$\times$64	& F430M &  0.2 \\
+2		& Bright JWST Calibrator			& G2 V			& 6	  		& On &	64$\times$64	& F430M &  220 \\
+3		& Bright JWST Calibrator			& G2 V			& 6  			& Off &	64$\times$64	& F430M &  0.1 \\
+4		& Faint Calibrator				& G2 V			& 16 			& Off &	64$\times$64	& F430M &  94 \\
+5		& Faint Calibrator				& G2 V			& 16 			& Off &	Full Frame	& F430M &  107 \\
+6		& Faint Calibrator				& G2 V			& 16 			& Off &	Full Frame  	& F444W &  21 \\
 \hline
 \end{tabular}
-\tablenotetext{a}{Any directly calibrated bright source such as the MSX calibrators \citep{price2004msxCal}, (which include Sirius and Vega) or alternatively $\alpha$ Cen A.}
+\tablenotetext{a}{Any directly calibrated bright source such as the MSX calibrators \citep{price2004msxCal}, (which include Sirius and Vega) or alternatively $\alpha$ Cen A.
+The exposure times given are the times needed to reach at least SNR=200, rounded up to the next group up the ramp.}
 \vspace{0.05in}
@@
 Aperture photometry of the sources imaged through the corograph will have to use a large aperture encompassing the 6 outer peaks or apply careful background subtraction.
-Both PSFs were calculated for NIRCam's long wavelength channel with a F444W filter.}
+Both PSFs were calculated for NIRCam's long wavelength channel with a F430M filter.}
 	\label{fig:psfComparison}

### 2016-12-06 ms.tex
I added info on the MSX calibrator stars spectra and saturation limits.

@@
 The primary JWST standards for absolute calibration have been tied to directly calibrated photometric sources through transfers, such as with HST's STIS instrument.
-As an independent check on those transfers, NIRCam can be used to observe those directly calibrated sources and transfer from the brightest ($K \sim -1$) sources all the way to the faintest calibrators ($K \sim 16$).
-Observing these bright sources (which are bright naked eye stars) with JWST's NIRCam can be achieved with a combination of narrowband filters, small subarray sizes, a Lyot stop pupil mask (19\% transmission) and a neutral density (ND) filter.
-The same configuration can then be used on move to fainter sources.
+As an independent check on those transfers, NIRCam can be used to observe those directly calibrated sources and transfer from the brightest ($K \sim -3$) sources all the way to the faintest calibrators ($K \sim 16$).
+Figure \ref{fig:msxNCfilterOverlap} shows the MSX filters B1 and B2 as compared to the NIRCam long wavelength filters with some overlap and that the F430M filter most closely matches the MSX bands.
+Figure \ref{fig:msxNCfilterOverlap} also shows model spectra from \citet{castelli2004models} for the MSX calibrator stars in \citet{price2004msxCal} near these bandpasses.
+The flux has been normalized for each star at 3.6~$\mu$m and then offset for clarity.
+
+Observing these bright sources (which are bright naked eye stars) with JWST's NIRCam can be achieved with a combination of medium-band filters, small subarray sizes, a Lyot stop pupil mask (19\% transmission) and a neutral density (ND) filter.
+Using \texttt{webbpsf} and the throughputs in a program called \texttt{pynrc}, we calculate the saturation limits for 2 groups in RAPID mode and find a K-magnitude of saturation of -4.0 for an A1 V star like Sirius and -3.7 for an M3 III star like Gacrux.
+This means that the entire sample of stars from \citet{price2004msxCal} are observable in this coronagraphic neutral density mode.
 
@@
 \centering
-\includegraphics[width=.4\columnwidth]{msx_nircam_filt.pdf}
-\caption{NIRCam filters as compared to the MSX short wavelength filters from \citet{egan1999msxGuide}. F430M best matches the MSX filters.}\label{fig:NCFOV}
+\includegraphics[width=.55\columnwidth]{msx_nircam_filt.pdf}
+\caption{NIRCam filter throughputs (top), MSX filter throughputs \citep{egan1999msxGuide} (middle) and model spectra of MSX calibrator stars (bottom).
+F430M best matches the MSX filters.}\label{fig:msxNCfilterOverlap}
 \end{figure}

### 2016-12-09 ms.tex
I added references and acknowledgements for Hectospec and re-organized the section on direct standards.

@@
 \section{Spectral Typing of Candidate Analogs}
+The Hectospec instrument on the MMT \citep{fabricant2005hectospec,mink2007hectoFibers} was used to obtain spectra of candidate solar analogs in the clusters .
 
@@
 \clearpage
+
 \section{Transferring to Directly Calibrated Sources}
@@
 As an independent check on those transfers, NIRCam can be used to observe those directly calibrated sources and transfer from the brightest ($K \sim -3$) sources all the way to the faintest calibrators ($K \sim 16$).
-Figure \ref{fig:msxNCfilterOverlap} shows the MSX filters B1 and B2 as compared to the NIRCam long wavelength filters with some overlap and that the F430M filter most closely matches the MSX bands.
-Figure \ref{fig:msxNCfilterOverlap} also shows model spectra from \citet{castelli2004models} for the MSX calibrator stars in \citet{price2004msxCal} near these bandpasses.
-The flux has been normalized for each star at 3.6~$\mu$m and then offset for clarity.
+Figure \ref{fig:sensitivityLadder} shows a schematic of the steps.
+NIRCam can observe the the Midcourse Survey Experiment (MSX) calibrators \citep{price2004msxCal}, as discussed in Section \ref{sec:brightStarMode}.
+The same instrument configuration, source location would be used to transfer to a JWST standard.
 
-Observing these bright sources (which are bright naked eye stars) with JWST's NIRCam can be achieved with a combination of medium-band filters, small subarray sizes, a Lyot stop pupil mask (19\% transmission) and a neutral density (ND) filter.
-Using \texttt{webbpsf} and the throughputs in a program called \texttt{pynrc}, we calculate the saturation limits for 2 groups in RAPID mode and find a K-magnitude of saturation of -4.0 for an A1 V star like Sirius and -3.7 for an M3 III star like Gacrux.
-This means that the entire sample of stars from \citet{price2004msxCal} are observable in this coronagraphic neutral density mode.
-
-\begin{figure}[!hbtp]
+\begin{figure}[!t]
 \centering
-\includegraphics[width=.55\columnwidth]{msx_nircam_filt.pdf}
-\caption{NIRCam filter throughputs (top), MSX filter throughputs \citep{egan1999msxGuide} (middle) and model spectra of MSX calibrator stars (bottom).
-F430M best matches the MSX filters.}\label{fig:msxNCfilterOverlap}
+\includegraphics[width=.6\columnwidth]{flux_ladder.pdf}
+\caption{Sensitivity ladder going a sub-array, neutral density filter observation a MSX standard to a full array, non-neutral density filter of a faint calibrator.}\label{fig:sensitivityLadder}
 \end{figure}
 
-\begin{table}
+\begin{table}[!b]
 \centering
-\caption{Conversion from Directly Calibrated Source to Deep Calibrator}\label{tab:clusterProp}
+\caption{Conversion from Directly Calibrated Source to Deep Calibrator}\label{tab:conversionSteps}
 \begin{tabular}{lrrrrrrr}
@@
 
-\begin{figure}[!hbtp]
-\centering
-\includegraphics[width=.6\columnwidth]{flux_ladder.pdf}
-\caption{Sensitivity ladder going a sub-array, neutral density filter observation a MSX standard to a full array, non-neutral density filter of a faint calibrator.}\label{fig:sensitityLadder}
-\end{figure}
-
-\subsection{Ways to Observe Really Bright Stars With NIRCam}
+\subsection{Ways to Observe Really Bright Stars With NIRCam}\label{sec:brightStarMode}
 
@@
 Sensitivity and saturation limits make use of \texttt{pysynphot} \citep{lim2015pysynphot} with Phoenix stellar models \citep{allard2012phoenix} ranging from 4.0 to 5.0 in log(g).
+
+\subsection{Tie-in to MSX}
+
+Figure \ref{fig:msxNCfilterOverlap} shows the MSX filters B1 and B2 as compared to the NIRCam long wavelength filters with some overlap and that the F430M filter is the best match with the MSX bands.
+Figure \ref{fig:msxNCfilterOverlap} also shows model spectra from \citet{castelli2004models} for the MSX calibrator stars in \citet{price2004msxCal} near these bandpasses.
+The flux has been normalized for each star at 3.6~$\mu$m and then offset for clarity
+We use the nearest match between the stellar types from the Simbad database and the suggested \citet{castelli2004models} parameters\footnote{http://www.stsci.edu/hst/observatory/crds/castelli\_kurucz\_atlas.html}.
+
+Observing these bright sources (which are bright naked eye stars) with JWST's NIRCam can be achieved with a combination of medium-band filters, small subarray sizes, a Lyot stop pupil mask (19\% transmission) and a neutral density (ND) filter.
+Using \texttt{webbpsf} and the throughputs in a program called \texttt{pynrc}, we calculate the saturation limits for 2 groups in RAPID mode and find a K-magnitude of saturation of -4.0 for an A1 V star like Sirius and -3.7 for an M3 III star like Gacrux.
+This means that the entire sample of stars from \citet{price2004msxCal} are observable in this coronagraphic neutral density mode.
+
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.55\columnwidth]{msx_nircam_filt.pdf}
+\caption{NIRCam filter throughputs (top), MSX filter throughputs \citep{egan1999msxGuide} (middle) and model spectra of MSX calibrator stars (bottom).
+F430M best matches the MSX filters.}\label{fig:msxNCfilterOverlap}
+\end{figure}
 
@@
 Observations reported here were obtained at the MMT Observatory, a joint facility of the University of Arizona and the Smithsonian Institution.
+This paper uses data products produced by the OIR Telescope Data Center, supported by the Smithsonian Astrophysical Observatory.
 The Pan-STARRS1 Surveys (PS1) have been made possible through contributions of the Institute for Astronomy, the University of Hawaii, the Pan-STARRS Project Office, the Max-Planck Society and its participating institutes, the Max Planck Institute for Astronomy, Heidelberg and the Max Planck Institute for Extraterrestrial Physics, Garching, The Johns Hopkins University, Durham University, the University of Edinburgh, Queen's University Belfast, the Harvard-Smithsonian Center for Astrophysics, the Las Cumbres Observatory Global Telescope Network Incorporated, the National Central University of Taiwan, the Space Telescope Science Institute, the National Aeronautics and Space Administration under Grant No.
@@
 \appendix
+
+\section{Notes to Self}
+
+\subsubsection{Backgrounds}
+
+Zodiacal background is expressed as a function of the minimum zodiacal background in \texttt{pynrc}.
+Average across the sky has zfact = 2.5.
 

### 2016-12-10 ms.tex
I added a lot more detail to the section on how to observe really bright stars.

@@
 
-\section{Transferring to Directly Calibrated Sources}
+\section{Transferring to Directly Calibrated Sources - the NIRCam Flux Ladder}
 
@@
 As an independent check on those transfers, NIRCam can be used to observe those directly calibrated sources and transfer from the brightest ($K \sim -3$) sources all the way to the faintest calibrators ($K \sim 16$).
-Figure \ref{fig:sensitivityLadder} shows a schematic of the steps.
-NIRCam can observe the the Midcourse Survey Experiment (MSX) calibrators \citep{price2004msxCal}, as discussed in Section \ref{sec:brightStarMode}.
-The same instrument configuration, source location would be used to transfer to a JWST standard.
+Figure \ref{fig:sensitivityLadder} shows a schematic of the steps beginning with Midcourse Survey Experiment (MSX) calibrators \citep{price2004msxCal}.
+
+The methodology of the flux ladder is that only one type of change is made in each step - either an instrument re-configuration is made on the same source or a new source is measured with the same instrument configuration.
+As listed in Table \ref{tab:conversionSteps}, the direct calibrator would be observed in a neutral density square, subarray and medium band filter while using the coronagraphic pupil.
+For the next step, this same instrument configuration will be used on a bright JWST standard, such as HD 37962 (G2 V, K=6.27).
+Getting sufficient signal to noise (S/N$\sim$200) on a faint calibrator such as P330E (G2 V, K=11.4) would require unfeasibly long integration times and more steps so the bright calibrators are preferred for steps 2 and 3.
 
@@
 \caption{Conversion from Directly Calibrated Source to Deep Calibrator}\label{tab:conversionSteps}
-\begin{tabular}{lrrrrrrr}
+\begin{tabular}{lrrrrrrrr}
 \hline \hline
-Step		& Source						& Spectral Type	& K Mag		& ND Filter		& Subarray	& Filter & t$_{exp} (s) $\\
+Step		& Source						& Spectral Type	& $K_\mathrm{src}$		& ND Square		& Subarray	& Filter & t$_\mathrm{exp} (s) $ &$K_\mathrm{sat}$\\
 \hline \hline
-1		& MSX Calibrator\tablenotemark{a}	& A1 V to M0 III		& -3 to 0.1		& On	&	64$\times$64	& F430M &  0.2 \\
-2		& Bright JWST Calibrator			& G2 V			& 6	  		& On &	64$\times$64	& F430M &  220 \\
-3		& Bright JWST Calibrator			& G2 V			& 6  			& Off &	64$\times$64	& F430M &  0.1 \\
-4		& Faint Calibrator				& G2 V			& 16 			& Off &	64$\times$64	& F430M &  94 \\
-5		& Faint Calibrator				& G2 V			& 16 			& Off &	Full Frame	& F430M &  107 \\
-6		& Faint Calibrator				& G2 V			& 16 			& Off &	Full Frame  	& F444W &  21 \\
+1		& MSX Calibrator\tablenotemark{a}	& A1 V to M0 III		& -3 to 0.1		& On	&	64$\times$64	& F430M &  0.2 & -4.0 \\
+2		& Bright JWST Calibrator			& G2 V			& 6.5	  		& On &	64$\times$64	& F430M &  220 & -4.0 \\
+3		& Bright JWST Calibrator			& G2 V			& 6.5  		& Off &	64$\times$64	& F430M &  0.1 & 6.2 \\
+4		& Faint Calibrator				& G2 V			& 16 			& Off &	64$\times$64	& F430M &  94 & 6.2 \\
+5		& Faint Calibrator				& G2 V			& 16 			& Off &	Full Frame	& F430M &  107 & 12 \\
+6		& Faint Calibrator				& G2 V			& 16 			& Off &	Full Frame  	& F444W &  21 & 13.7 \\
 \hline
@@
 \tablenotetext{a}{Any directly calibrated bright source such as the MSX calibrators \citep{price2004msxCal}, (which include Sirius and Vega) or alternatively $\alpha$ Cen A.
-The exposure times given are the times needed to reach at least SNR=200, rounded up to the next group up the ramp.}
+The exposure times given are the times needed to reach at least SNR=200, rounded up to the next group up the ramp.
+The saturation limit is the 80\% well depth for 2 non-destructive reads up the ramp following a reset.}
 \vspace{0.05in}
@@
 
-\subsection{Ways to Observe Really Bright Stars With NIRCam}\label{sec:brightStarMode}
+The bright JWST calibrator can be used to convert from the ND filter with a coronagraphic pupil mask to direct imaging.
+This instrument configuration is now capable of observing faint calibrators (K$\sim$16) with only $\sim$ 100 sec of integration time.
+The final three steps would be to convert from subarray imaging to full frame imaging and change the filter, which would require a model for the stellar flux in these bands.
+Either a well-characterized white dwarf spectrum of a known standard or a faint G2 V standard from an open cluster would be good candidates for this transfer of filters.
 
-There are several ways to improve saturation limits:
+\subsection{Ways to Observe Bright Stars}\label{sec:brightStarMode}
+
+There are several ways to improve saturation limits with NIRCam:
 \begin{itemize}
-\item Cut down the aperture size with a Lyot stop. These have 19\% throughput, but make the PSF shapes strange.
-\item Use a neutral density square in the coronagraph mask.
-The neutral density filters have an attenuation of around 10$^3$ or 7.5 mags.
+\item \textbf{Lyot Stop} Cut down the aperture size with a Lyot stop. These have 19\% throughput (1.8 mags). Additionally, this broadens the PSF - see Figure \ref{fig:psfComparison}.
+The broadening spreads light out by a similar factor (1.8 mags) for a total of 3.5 mags.
+\item \textbf{Neutral Density Square} The neutral density filters have an attenuation of around 10$^3$ or 7.5 mags.
 A color correction would have to be applied for the neutral density filter (since it is wavelength dependent) when transferring to an un-occulted region.
-Additionally, the Lyot stop that must be in place to use the neutral density filter has a throughput of 19\%, so the total improvement is 8.8 mags
-\item Use a long wavelength grism to spread out the light - this could be used in conjunction with a neutral density square
+Additionally, the Lyot stop that must be in place to use the neutral density filter so the total improvement is 11 mags over direct imaging.
+\item \textbf{Grisms} For long wavelength observations, one can use grism to spread out the light.
+This mode still has a saturation limit of $K$=4.6 to 3.5 for the F322W2  filter \citep{greene2016wfss}, which does not reach to the MSX standards.
+This could be potentially combined with the coronagraph, but both at once hasn't been explored much.
+One could potentially observe small pieces of the spectrum at a time with a subarray that moves along the spectrum, but this would likely be harder to implement.
+\item \textbf{DHS} The dispersed Hartmann Sensor (DHS) reduces the pupil throughput and spreads the light out to reach saturation limits of $K$=0.2 to 1.5 depending on spectral type \citep{schlawin2017dhs}.
+This would also have to be read out with a moving subarray to observe the MSX stars.
 \item Use a narrowband filter, such as F121N
 \item Use a small subarray - 64 $\times$ 64 is supported for science. There will be an engineering jitter monitoring test with an 8 $\times$ 8 subarray 
+\item \textbf{Weak Lens} The Weak Lenses spread light out over many pixels which can be helpful for bright stars.
+However, one needs to read out larger sized subarrays to encompass the entire hexagonal PSF so this somewhat cancels out.
 \end{itemize}
 
-One could also defocus the stars with a weak lens, but the longer read times needed to capture the hexagon of the weak lens end up with saturation limits that are not as good as the coronagraph.
+Of the many options here, the most feasible method is the neutral density square with the Lyot Coronagraphic pupil mask.
 

### 2016-12-13 ms.tex
I fleshed out the NIRCam flux ladder section.

@@
 
-The methodology of the flux ladder is that only one type of change is made in each step - either an instrument re-configuration is made on the same source or a new source is measured with the same instrument configuration.
-As listed in Table \ref{tab:conversionSteps}, the direct calibrator would be observed in a neutral density square, subarray and medium band filter while using the coronagraphic pupil.
-For the next step, this same instrument configuration will be used on a bright JWST standard, such as HD 37962 (G2 V, K=6.27).
-Getting sufficient signal to noise (S/N$\sim$200) on a faint calibrator such as P330E (G2 V, K=11.4) would require unfeasibly long integration times and more steps so the bright calibrators are preferred for steps 2 and 3.
-
 \begin{figure}[!t]
 \centering
-\includegraphics[width=.6\columnwidth]{flux_ladder.pdf}
-\caption{Sensitivity ladder going a sub-array, neutral density filter observation a MSX standard to a full array, non-neutral density filter of a faint calibrator.}\label{fig:sensitivityLadder}
+\includegraphics[width=.55\columnwidth]{flux_ladder.pdf}
+\caption{Sensitivity ladder going a sub-array, neutral density filter observation a MSX standard to a full array, non-neutral density filter of a faint calibrator.
+An intermediate standard can be used to check the NIRCam transfers against other observatories and instruments.}\label{fig:sensitivityLadder}
 \end{figure}
@@
 
-The bright JWST calibrator can be used to convert from the ND filter with a coronagraphic pupil mask to direct imaging.
-This instrument configuration is now capable of observing faint calibrators (K$\sim$16) with only $\sim$ 100 sec of integration time.
-The final three steps would be to convert from subarray imaging to full frame imaging and change the filter, which would require a model for the stellar flux in these bands.
+The methodology of the flux ladder is that only one type of change is made in each step - either an instrument re-configuration is made on the same source or a new source is measured with the same instrument configuration.
+As listed in Table \ref{tab:conversionSteps}, the direct calibrator would be observed in a neutral density square, subarray and medium band filter while using the coronagraphic pupil.
+For the next step, this same instrument configuration will be used on a bright JWST standard, such as HD 37962 (G2 V, $K$=6.27).
+Getting sufficient signal to noise (S/N$\sim$200) on a faint calibrator such as P-330E (G2 V, $K$=11.4) would require unfeasibly long integration times and more steps so the bright calibrators are preferred for steps 2 and 3.
+
+This bright JWST standard would be used to transfer from the the ND filter with a coronagraphic pupil mask to direct imaging.
+This conversion step can independently be checked against other instruments' measurements of the bright JWST calibrator, such as by STIS with HST and also tied to other JWST calibrators.
+The next step would be to use the same direct image configuration and subarray size to observe a faint JWST calibrator around $K \sim$15.
+S/N ratios of 200 can be achieved in 94 seconds in this mode.
+This calibrator star would now be observable in full frame mode without saturation so the next step would be a conversion from subarray to full frame on the same source.
+To calibrate the wide band filters, such as F444W, one final step would be needed to go from the medium to wide band photometry using a model for the star.
 Either a well-characterized white dwarf spectrum of a known standard or a faint G2 V standard from an open cluster would be good candidates for this transfer of filters.
+
+Figure \ref{fig:sensitivityLadder} shows that an intermediate JWST standard such as P-330 E can be used to check transfers and detector linearity corrections.
+This step would not be direct link in the NIRCam flux ladder since it would require more transfers to achieve the end goal of full frame wide band imaging, but serves as another check on the transfers from bright to faint targets.
 
@@
 Additionally, the Lyot stop that must be in place to use the neutral density filter so the total improvement is 11 mags over direct imaging.
+Care must be taken with dithering to ensure that non-uniform optical depth of the neutral density filter doesn't affect the photometry.
 \item \textbf{Grisms} For long wavelength observations, one can use grism to spread out the light.

### 2016-12-13 ms.tex
I re-organized repeat text about the flux ladder.

@@
 
-There are several ways to improve saturation limits with NIRCam:
+There are several ways to improve saturation limits with NIRCam over direct imaging:
 \begin{itemize}
@@
 Of the many options here, the most feasible method is the neutral density square with the Lyot Coronagraphic pupil mask.
-
 Sensitivity and saturation limits make use of \texttt{pysynphot} \citep{lim2015pysynphot} with Phoenix stellar models \citep{allard2012phoenix} ranging from 4.0 to 5.0 in log(g).
@@
 Figure \ref{fig:msxNCfilterOverlap} also shows model spectra from \citet{castelli2004models} for the MSX calibrator stars in \citet{price2004msxCal} near these bandpasses.
-The flux has been normalized for each star at 3.6~$\mu$m and then offset for clarity
+The flux has been normalized for each star at 3.6~$\mu$m and then offset for clarity.
 We use the nearest match between the stellar types from the Simbad database and the suggested \citet{castelli2004models} parameters\footnote{http://www.stsci.edu/hst/observatory/crds/castelli\_kurucz\_atlas.html}.

### 2016-12-16 ms.tex
I added a lot more explanation to the introduction and the cluster choices.

@@
 Many studies of dark energy make use of Type Ia Supernovae as standard candles and improvements to the absolute flux calibration are important for improving their luminosity distances.
+JWST will have no standard calibration sources onboard so all calibration must be performed with astronomical sources.
+
+The JWST flux calibration effort has been described in \citet{gordon2009fluxplan1} and \citet{gordon2011fluxplan2}.
+It is still being developed and refined.
+Figure \ref{fig:JWStcalsWideF} shows several of the sources that will be used for flux calibration.
+These include three categories: 1) hot stars (white dwarf and OB stars) 2) G-stars (which are solar-like) and 3) A-type stars.
+The variety of spectra used in JWST calibration can mitigate against biases when models are used to convert flux in one filter to the expected flux in another filter.
+
+The original flux calibration effort has mainly bright stars ($K \lesssim 15$).
+Example spectra for these calibrators are shown in Figure \ref{fig:JWStcalsWideF} with saturation and sensitivity limits of NIRCam's wide filters.
+Many of these spectra will saturate the NIRCam detectors when used in full frame (shown as the middle parts of the black ``error bars'').
+Furthermore, there may be systematic errors when observing faint targets and low detector well depths.
+\textcolor{red}{[Have a detector person - Karl, Jarron or George read the rest of this paragraph:]}
+As an example of a systematic detector effect, consider charge traps within a detector.
+These traps would tend to decrease the measured number of electrons per second on the first exposure because they would trap electrons  that would not be read out by an amplifier.
+For bright sources, the effect of the traps would be smaller since they would quickly be a small fraction of the flux.
+For faint sources, however, the traps would be a larger fraction of the incoming electrons.
+
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.6\columnwidth]{nircam_wide_filters.png}
+\caption{The NIRCam subarray saturation, full frame saturation and 10~$\sigma$ sensitivity limits for wide band imaging from \citet{gordon2011fluxplan2}.
+The three values are shown as upper, middle and lower limit error bars respectively.
+For comparison, three classes of JWST calibrators are shown: hot stars including white dwarfs (blue), A-type stars (green) and G-type stars (red).
+Additional faint calibrators are needed to extend the sample from \citet{gordon2011fluxplan2} towards the faint limits of NIRCam.}\label{fig:JWStcalsWideF}
+\end{figure}
+
+In this report, we discuss a NIRCam-led effort to identify and calibrate stars to add to the JWST sample on the fainter end around $K \approx 15$.
+We choose the method of \citet{rieke2008absIRcal}, which uses solar-like stars for flux calibration.
+The basic rationale is that the Solar spectrum is well measured across JWST's wavelengths \citep[0.6~$\mu$m to 29~$\mu$m][]{gardner2006SSRv} and has highly accurate models for its spectrum.
+When solar-like stars are identified, one can use these models to convert from one photometric or spectroscopic band to another.
+We identify solar-like stars in open clusters because it allows us to average over multiple stars and to cross-calibrate with bright references within the cluster.
+The color magnitude diagram of the cluster also allows us to identify solar like stars and aids in the corrections for extinction.
 
 \section{Cluster Properties}
+
+Our team examined open clusters from the WEBDA database\footnote{https://www.univie.ac.at/webda/webda.html} to find clusters most suitable for flux calibration with solar-like stars.
+The parameters under consideration were the the following:
+\begin{itemize}
+\item {\bf Age:} For the methods to work, the solar-mass stars must be on the main sequence.
+This means the age of the cluster must be between 0.2 Gyr (??) and 8 Gyr (??) using Dartmouth evolutionary models \citep{dotter2008dartmouth}.
+\item {\bf Extinction} Extinction should be as small as possible to minimize the effects of extinction correction to photometry. This generally means E(B-V) $\lesssim < 0.1$.
+\item {\bf Distance Modulus} The cluster must be distant enough to not saturate NIRCam's wide filters in full frame mode.
+\item {\bf Metallicity}
+\item {\bf Compactness}
+\item {\bf Ancillary data}
+\end{itemize}
+
+\begin{figure}
+\centering
+\includegraphics[width=.4\columnwidth]{cluster_visibilty.pdf}
+\caption{Visibility windows for the three open clusters considered in this report.
+The planned commissioning period is shown with vertical blue dashed lines.}\label{fig:clusterVis}
+\end{figure}
 
@@
 We therefore did a literature search for the most recent available cluster parameters.
+Table \ref{tab:clusterProp} shows the properties gathered from the literature.
+The most up-to-date literature values indicate that all three clusters have low extinction with E(B-V) $<$ 0.1.
+Including uncertainties, the extinctions are actually all consistent with 0.06, but it should be noted that the NGC 2506 uncertainties are likely underestimated since their were derived from a standard error of the mean and may not include systematics.
 
@@
 Zodiacal background is expressed as a function of the minimum zodiacal background in \texttt{pynrc}.
-Average across the sky has zfact = 2.5.
+From the code documentation: average across the sky has zfact = 2.5.
 

### 2016-12-17 ms.tex
I added some isochrones to justify the age choices.

@@
 \item {\bf Age:} For the methods to work, the solar-mass stars must be on the main sequence.
-This means the age of the cluster must be between 0.2 Gyr (??) and 8 Gyr (??) using Dartmouth evolutionary models \citep{dotter2008dartmouth}.
+If we require that a solar mass star have $T_{\rm eff}$ = 5780 +/- 100 K, the cluster would have to be between 0.3 Gyr and 10 Gyr using Dartmouth evolutionary models \citep{dotter2008dartmouth}.
+Furthermore, the age should be $\lesssim$7 Gyr to avoid main sequence turnoff of near-solar stars.
 \item {\bf Extinction} Extinction should be as small as possible to minimize the effects of extinction correction to photometry. This generally means E(B-V) $\lesssim < 0.1$.
@@
 
+Thanks to Daniel Kiminki and John Stauffer for the selection of open clusters for this work and for finding targets based on initial data.
 Funding for the NIRCam team is provided by NASA Goddard Spaceflight Center.
@@
 From the code documentation: average across the sky has zfact = 2.5.
+In these models solar B-V=0.65 for 1~M$_\odot$ at 4.25 Gyr.
+
+\subsection{Isochrones}
+
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.7\columnwidth]{hr_isochrones.pdf}
+\caption{The Dartmouth isochrones \citep{dotter2008dartmouth}, for [Fe/H]=0, show that the age of the cluster should be $\lesssim 7 $Gyr before main sequence turnoff should begin to affect the identification of solar analogs.
+The red vertical line represents solar B-V.}\label{fig:isochrones}
+\end{figure}
 

### 2016-12-20 ms.tex
I added more info on distance modulus selection for the clusters.

@@
 Furthermore, the age should be $\lesssim$7 Gyr to avoid main sequence turnoff of near-solar stars.
-\item {\bf Extinction} Extinction should be as small as possible to minimize the effects of extinction correction to photometry. This generally means E(B-V) $\lesssim < 0.1$.
+\item {\bf Extinction} Extinction should be as small as possible to minimize the effects of extinction correction to photometry. Of the clusters found, E(B-V) $\lesssim < 0.1$.
 \item {\bf Distance Modulus} The cluster must be distant enough to not saturate NIRCam's wide filters in full frame mode.
+The most easily saturated filter for G stars is the F090W, which corresponds to a G2~V star of 15.9.
+This means the distance modulus should be 12.6 for a solar absolute K=3.28 \citep{binney1998book}.
+The longer wide band filters (F200W, F277W, F356W, and F444W) will not saturate for a distance modulus larger than 11.8.
+\textcolor{red}{Calculate with extinction!}
 \item {\bf Metallicity}

### 2016-12-21 ms.tex
I added more description of the cluster selection criteria.

@@
 \textcolor{red}{Calculate with extinction!}
-\item {\bf Metallicity}
-\item {\bf Compactness}
-\item {\bf Ancillary data}
+\item {\bf Metallicity} Ideally, the cluster should have near-solar metallicity. NGC 2420 and NGC 6811 have -0.08 $<=$ [Fe/H] $<=$ 0.05. NGC 2506, is metal poor at [Fe/H]=-0.32.
+\item {\bf Compactness} The cluster should be relatively compact compared to NIRCam's FOV (2'$\times$2' per module). We selected clusters $\lesssim 15\arcmin$
+\item {\bf Ancillary data} The clusters should have ancillary photometry from multiple observatories for cross-calibration. We preferred clusters with 2MASS, WISE and IRAC measurements.
+\item {\bf Visibility} The clusters should be spread out to ensure that at least one is visible during the commissioning period.
 \end{itemize}
+
+With all these considerations in play, we selected NGC 2420 as the best fit for the multiple criteria.
+NGC 2506 and NGC 6811 are next-best fits and have somewhat complimentary visibility windows, visible in Figure \ref{fig:clusterVis}.
 

### 2016-12-21 ms.tex
I finished the cluster selection criteria section, moved notes-to-self to the appendix and added a caveat about the neutral density square surface non-uniformity.

@@
 JWST will have no standard calibration sources onboard so all calibration must be performed with astronomical sources.
+While there were internal lamps in original designs, the envelopes for the filaments did not make it through testing so the sources were removed.
 
@@
 The most easily saturated filter for G stars is the F090W, which corresponds to a G2~V star of 15.9.
-This means the distance modulus should be 12.6 for a solar absolute K=3.28 \citep{binney1998book}.
-The longer wide band filters (F200W, F277W, F356W, and F444W) will not saturate for a distance modulus larger than 11.8.
-\textcolor{red}{Calculate with extinction!}
-\item {\bf Metallicity} Ideally, the cluster should have near-solar metallicity. NGC 2420 and NGC 6811 have -0.08 $<=$ [Fe/H] $<=$ 0.05. NGC 2506, is metal poor at [Fe/H]=-0.32.
+This means the true distance modulus $(m - M)_0$ should be 12.6 for a solar absolute K=3.28 \citep{binney1998book}.
+The longer wavelength wide band filters (F200W, F277W, F356W, and F444W) will not saturate for a true distance modulus larger than 11.8.
+If one assumes an extinction of E(B-V) = 0.05 and a Galactic average extinction law \citep{cardelli1989}, the visual distance moduli $(m- M)_V$ should be an additional 0.1 mag.
+\item {\bf Metallicity} Ideally, the cluster should have near-solar metallicity so that the solar mass stars have solar luminosity and solar spectra. 
 \item {\bf Compactness} The cluster should be relatively compact compared to NIRCam's FOV (2'$\times$2' per module). We selected clusters $\lesssim 15\arcmin$
 \item {\bf Ancillary data} The clusters should have ancillary photometry from multiple observatories for cross-calibration. We preferred clusters with 2MASS, WISE and IRAC measurements.
-\item {\bf Visibility} The clusters should be spread out to ensure that at least one is visible during the commissioning period.
+\item {\bf Visibility} The clusters should be spread out in ecliptic longitude to ensure that at least one is visible during the commissioning period.
 \end{itemize}
@@
 With all these considerations in play, we selected NGC 2420 as the best fit for the multiple criteria.
-NGC 2506 and NGC 6811 are next-best fits and have somewhat complimentary visibility windows, visible in Figure \ref{fig:clusterVis}.
+The only parameter that is not satisfied is the distance modulus, so additional sources or conversions are needed for the F070W, F090W, F115W and F150W filters.
+At the time NGC 2420 was selected, the JWST throughputs were smaller than the measured values so it saturated fewer filters.
+One way to calibrate these short wavelength, wide filters is to use subarrays.
+The subarray to full frame conversion can be checked with medium band filters.
+NGC 2506 and NGC 6811 are next-best fits and have somewhat complimentary visibility windows, visible in Figure \ref{fig:clusterVis}. NGC 2420 and NGC 6811 have -0.08 $<=$ [Fe/H] $<=$ 0.05.
+NGC 2506, is metal poor at [Fe/H]=-0.32, so corrections must be made for changes to G2 V spectra due to metallicity.
 
@@
 
-\section{Pan-Starrs Photometry}
+\section{Pan-Starrs}
+\subsection{Pan-Starrs Photometry}
 
-We obtained $grizy$ Pan-Starrs photometry for all three clusters \citep{magnier2013photLadder,schlafly2012photcal,tonry2012panstarrsPhot}.
+We obtained $grizy$ Pan-Starrs photometry\citep{magnier2013photLadder,schlafly2012photcal,tonry2012panstarrsPhot} for all three clusters.
 We also looked up the $g$ - $r$ colors
@@
 
-\section{UKIRT Photometry}
+\subsection{UKIRT Photometry}
 
@@
 The Hectospec instrument on the MMT \citep{fabricant2005hectospec,mink2007hectoFibers} was used to obtain spectra of candidate solar analogs in the clusters .
-
-\subsection{Notes on using \texttt{mkclass}}
-
-\subsubsection{Code System}
-The library is organized into files like \texttt{t130l50p00.rbn}.
-The \texttt{t130} specifies 10 $\times$ the class coding system of O3 through M9 visible in the code \texttt{code3spt.c}.
-In this case, \texttt{t130} means code 13.0 and type B7.
-The luminosity class is next \texttt{l50} means V.
-We use the \texttt{libnor36} library, which appears to work with the "Roughtype 2" method for non-rectified data.
-The code runs into segmentation faults if attempting Roughtype 1 with the \texttt{libnor36} library.
 
@@
 
+\subsubsection{Complications with Flat Fielding}
+The ND filters are not uniform spatially.
+Correcting for any pinholes or blemishes in the ND square surface will likely dominate the error budget for the ND square absolute calibration.
+Accurate positioning can help align the source to the same location on the neutral density square and dithering can be used to check the surface irregularities.
+
 \section*{Acknowledgements}
@@
 \section{Notes to Self}
+
+\subsection{Notes on using \texttt{mkclass}}
+
+\subsubsection{Code System}
+The library is organized into files like \texttt{t130l50p00.rbn}.
+The \texttt{t130} specifies 10 $\times$ the class coding system of O3 through M9 visible in the code \texttt{code3spt.c}.
+In this case, \texttt{t130} means code 13.0 and type B7.
+The luminosity class is next \texttt{l50} means V.
+We use the \texttt{libnor36} library, which appears to work with the "Roughtype 2" method for non-rectified data.
+The code runs into segmentation faults if attempting Roughtype 1 with the \texttt{libnor36} library.
 

### 2016-12-22 ms.tex
I updated and cleaned up the description of imaging direct standards. Going to send this out to the Abs Cal WG.

@@
 The longer wavelength wide band filters (F200W, F277W, F356W, and F444W) will not saturate for a true distance modulus larger than 11.8.
-If one assumes an extinction of E(B-V) = 0.05 and a Galactic average extinction law \citep{cardelli1989}, the visual distance moduli $(m- M)_V$ should be an additional 0.1 mag.
+If one assumes an extinction of E(B-V) = 0.05 and a Galactic average extinction law \citep{cardelli1989}, the visual distance moduli $(m- M)_V$ should be an additional 0.14 mag.
 \item {\bf Metallicity} Ideally, the cluster should have near-solar metallicity so that the solar mass stars have solar luminosity and solar spectra. 
@@
 The primary JWST standards for absolute calibration have been tied to directly calibrated photometric sources through transfers, such as with HST's STIS instrument.
-As an independent check on those transfers, NIRCam can be used to observe those directly calibrated sources and transfer from the brightest ($K \sim -3$) sources all the way to the faintest calibrators ($K \sim 16$).
-Figure \ref{fig:sensitivityLadder} shows a schematic of the steps beginning with Midcourse Survey Experiment (MSX) calibrators \citep{price2004msxCal}.
+As an independent check on those transfers, NIRCam can be used to observe directly calibrated stars (such as the MSX calibrators \citep{price2004msxCal}) and step down in brightness to faint standards used in JWST calibration.
+Figure \ref{fig:sensitivityLadder} shows a schematic of the steps beginning with Midcourse Survey Experiment (MSX) calibrators (as bright as $K \sim -3$) to faint JWST standards ($K \sim 16$).
 
@@
 \includegraphics[width=.55\columnwidth]{flux_ladder.pdf}
-\caption{Sensitivity ladder going a sub-array, neutral density filter observation a MSX standard to a full array, non-neutral density filter of a faint calibrator.
+\caption{Schematic sensitivity ladder going from an MSX standard (with a sub-array, neutral density filter observation) to a faint JWST standard (with a full array, full throughput observation).
 An intermediate standard can be used to check the NIRCam transfers against other observatories and instruments.}\label{fig:sensitivityLadder}
@@
 3		& Bright JWST Calibrator			& G2 V			& 6.5  		& Off &	64$\times$64	& F430M &  0.1 & 6.2 \\
-4		& Faint Calibrator				& G2 V			& 16 			& Off &	64$\times$64	& F430M &  94 & 6.2 \\
-5		& Faint Calibrator				& G2 V			& 16 			& Off &	Full Frame	& F430M &  107 & 12 \\
-6		& Faint Calibrator				& G2 V			& 16 			& Off &	Full Frame  	& F444W &  21 & 13.7 \\
+4		& Faint JWST Calibrator			& G2 V			& 16 			& Off &	64$\times$64	& F430M &  94 & 6.2 \\
+5		& Faint JWST Calibrator			& G2 V			& 16 			& Off &	Full Frame	& F430M &  107 & 12 \\
+6		& Faint JWST Calibrator			& G2 V			& 16 			& Off &	Full Frame  	& F444W &  21 & 13.7 \\
 \hline
@@
 
-The methodology of the flux ladder is that only one type of change is made in each step - either an instrument re-configuration is made on the same source or a new source is measured with the same instrument configuration.
+The methodology of the flux ladder is that only one change is made per step - either an instrument re-configuration is made on the same source or a new source is measured with the same instrument configuration.
 As listed in Table \ref{tab:conversionSteps}, the direct calibrator would be observed in a neutral density square, subarray and medium band filter while using the coronagraphic pupil.
 For the next step, this same instrument configuration will be used on a bright JWST standard, such as HD 37962 (G2 V, $K$=6.27).
-Getting sufficient signal to noise (S/N$\sim$200) on a faint calibrator such as P-330E (G2 V, $K$=11.4) would require unfeasibly long integration times and more steps so the bright calibrators are preferred for steps 2 and 3.
+Getting sufficient signal to noise (S/N$\gtrsim$200) on an intermediate JWST calibrator such as P-330E (G2 V, $K$=11.4) with the neutral density square in place would require unfeasibly long integration times so the bright calibrators are preferred for steps 2 and 3.
 
-This bright JWST standard would be used to transfer from the the ND filter with a coronagraphic pupil mask to direct imaging.
-This conversion step can independently be checked against other instruments' measurements of the bright JWST calibrator, such as by STIS with HST and also tied to other JWST calibrators.
+This bright JWST standard would be used to transfer from the ND filter with a coronagraphic pupil mask to direct imaging.
+This conversion step can independently be checked against other instruments' measurements of the bright JWST calibrator, such as by STIS with HST.
 The next step would be to use the same direct image configuration and subarray size to observe a faint JWST calibrator around $K \sim$15.
@@
 To calibrate the wide band filters, such as F444W, one final step would be needed to go from the medium to wide band photometry using a model for the star.
-Either a well-characterized white dwarf spectrum of a known standard or a faint G2 V standard from an open cluster would be good candidates for this transfer of filters.
+Either a well-characterized white dwarf spectrum of a known standard or a faint G2 V standard from an open cluster would be good models for this transfer of filters.
 
 Figure \ref{fig:sensitivityLadder} shows that an intermediate JWST standard such as P-330 E can be used to check transfers and detector linearity corrections.
-This step would not be direct link in the NIRCam flux ladder since it would require more transfers to achieve the end goal of full frame wide band imaging, but serves as another check on the transfers from bright to faint targets.
+This step would not be a ``rung'' in the NIRCam flux ladder since it would require more transfers to achieve the last step of full frame wide band imaging, but serves as another check on the transfers from bright to faint targets.
 
@@
 \item \textbf{Lyot Stop} Cut down the aperture size with a Lyot stop. These have 19\% throughput (1.8 mags). Additionally, this broadens the PSF - see Figure \ref{fig:psfComparison}.
-The broadening spreads light out by a similar factor (1.8 mags) for a total of 3.5 mags.
-\item \textbf{Neutral Density Square} The neutral density filters have an attenuation of around 10$^3$ or 7.5 mags.
+The broadening spreads light out by a similar factor (contributing 1.8 mags to saturation limits) for a total of 3.5 mags.
+\item \textbf{Neutral Density Square} The neutral density filters have an attenuation of 10$^3$ or 7.5 mags.
 A color correction would have to be applied for the neutral density filter (since it is wavelength dependent) when transferring to an un-occulted region.
-Additionally, the Lyot stop that must be in place to use the neutral density filter so the total improvement is 11 mags over direct imaging.
+Additionally, the Lyot stop that must be in place to use the neutral density filter so the total improvement on saturation limits is 11 mags over direct imaging.
 Care must be taken with dithering to ensure that non-uniform optical depth of the neutral density filter doesn't affect the photometry.
-\item \textbf{Grisms} For long wavelength observations, one can use grism to spread out the light.
-This mode still has a saturation limit of $K$=4.6 to 3.5 for the F322W2  filter \citep{greene2016wfss}, which does not reach to the MSX standards.
-This could be potentially combined with the coronagraph, but both at once hasn't been explored much.
-One could potentially observe small pieces of the spectrum at a time with a subarray that moves along the spectrum, but this would likely be harder to implement.
-\item \textbf{DHS} The dispersed Hartmann Sensor (DHS) reduces the pupil throughput and spreads the light out to reach saturation limits of $K$=0.2 to 1.5 depending on spectral type \citep{schlawin2017dhs}.
-This would also have to be read out with a moving subarray to observe the MSX stars.
-\item Use a narrowband filter, such as F121N
-\item Use a small subarray - 64 $\times$ 64 is supported for science. There will be an engineering jitter monitoring test with an 8 $\times$ 8 subarray 
+\item \textbf{Grisms} For long wavelength NIRCam observations ($2.4~\mu$m$ > \lambda < 5~\mu$m), one can use a grism to spread out the light.
+This mode still has a saturation limit of $K$=4.6 to 3.5 for the F322W2  filter and 2048$\times$64 subarray \citep{greene2016wfss}, which does not reach to the MSX standards.
+This could be potentially combined with the coronagraphic pupil, but this combination has been tested or explored in detail.
+One could potentially observe small pieces of the spectrum at a time with a subarray that are all combined to create a spectrum, but this would add time and may be difficult to implement.
+\item \textbf{DHS} For short wavelength NIRCam spectra ($1.0~\mu$m$ > \lambda < 2.0~\mu$m), one can use the Dispersed Hartmann Sensor.
+The dispersed Hartmann Sensor (DHS) reduces the pupil throughput and spreads the light out to reach saturation limits of $K$=0.2 to 1.5 depending on spectral type \citep{schlawin2017dhs} for a 2048$\times$64 subarray.
+This is not bright enough to observe the MSX calibrators.
+As with the long wavelength grisms, one would have to read small subarrays (e.g. 64$\times$64) to get to brighter limits.
+If one stitched together a spectrum from these subarrays along the spectrum, this could theoretically be used on all MSX stars.
+However, the time to build up 32 pieces
+\item \textbf{Extra Small Subarrays} There will be an engineering jitter monitoring test with an 8 $\times$ 8 subarray.
+There may be complications with calculating accurate integration times in this mode because any uncertainty's affecting a frame time could be a significant fraction of the $\sim$ 2 ms frame time.
+The background annulus would be limited for such small subarrays.
 \item \textbf{Weak Lens} The Weak Lenses spread light out over many pixels which can be helpful for bright stars.
-However, one needs to read out larger sized subarrays to encompass the entire hexagonal PSF so this somewhat cancels out.
+However, one needs to read out larger sized subarrays to encompass the entire hexagonal PSF so this somewhat cancels out the effect of spreading the light out over many pixels.
+For a very narrowband filter such as F212N, the K-band saturation limit for a weak lens observation with a 128$\times$128 subarray is 0.9 mag for a G2V star, which does not quite reach the MSX calibrators.
 \end{itemize}
@@
 Of the many options here, the most feasible method is the neutral density square with the Lyot Coronagraphic pupil mask.
-Sensitivity and saturation limits make use of \texttt{pysynphot} \citep{lim2015pysynphot} with Phoenix stellar models \citep{allard2012phoenix} ranging from 4.0 to 5.0 in log(g).
+Sensitivity and saturation limits make use of \texttt{pysynphot} \citep{lim2015pysynphot} with either Phoenix stellar models \citep{allard2012phoenix} or \citet{castelli2004models} models.
 
@@
 
-Figure \ref{fig:msxNCfilterOverlap} shows the MSX filters B1 and B2 as compared to the NIRCam long wavelength filters with some overlap and that the F430M filter is the best match with the MSX bands.
+Figure \ref{fig:msxNCfilterOverlap} shows the MSX filters B1 and B2 as compared to the NIRCam long wavelength filters -- we only include filters that have some overlap.
+The F430M filter is the best match with the MSX bands.
 Figure \ref{fig:msxNCfilterOverlap} also shows model spectra from \citet{castelli2004models} for the MSX calibrator stars in \citet{price2004msxCal} near these bandpasses.
 The flux has been normalized for each star at 3.6~$\mu$m and then offset for clarity.
-We use the nearest match between the stellar types from the Simbad database and the suggested \citet{castelli2004models} parameters\footnote{http://www.stsci.edu/hst/observatory/crds/castelli\_kurucz\_atlas.html}.
+We use the nearest match between the stellar types from the Simbad database and the suggested \citet{castelli2004models} parameters.\footnote{http://www.stsci.edu/hst/observatory/crds/castelli\_kurucz\_atlas.html}
 
 Observing these bright sources (which are bright naked eye stars) with JWST's NIRCam can be achieved with a combination of medium-band filters, small subarray sizes, a Lyot stop pupil mask (19\% transmission) and a neutral density (ND) filter.
-Using \texttt{webbpsf} and the throughputs in a program called \texttt{pynrc}, we calculate the saturation limits for 2 groups in RAPID mode and find a K-magnitude of saturation of -4.0 for an A1 V star like Sirius and -3.7 for an M3 III star like Gacrux.
+Using \texttt{webbpsf} and the throughputs in a NIRCam program called \texttt{pynrc}, we calculate the saturation limits for 2 groups in RAPID mode and find a K-magnitude of saturation of -4.0 for an A1 V star like Sirius and -3.7 for an M3 III star like Gacrux.
 This means that the entire sample of stars from \citet{price2004msxCal} are observable in this coronagraphic neutral density mode.
@@
 \subsubsection{Complications with PSF}
-A Lyot pupil mask must be used when imaging through the neutral density squares since the wedges that redirect light through NIRCam's corographic masks and neutral density squares are co-located with the Lyot stop pupil masks.
+A Lyot pupil mask must be used when imaging through the neutral density squares since the wedges that redirect light through NIRCam's coronagraphic masks and neutral density squares are co-located with the Lyot stop pupil masks.
 In addition to lowering the transmission by a factor of 0.19\%, the Lyot stops spread out the PSF as compared to direct imaging.
 Figure \ref{fig:psfComparison} shows example PSFs calculated with \texttt{webbpsf} \citep{perrin2012webbpsf}.
-Figure \ref{fig:psfDirect} shows the direct image PSF versus the the coronographic PSF (Figure \ref{fig:psfND}) both normalized to the peak pixel.
+Figure \ref{fig:psfDirect} shows the direct image PSF versus the the coronagraphic PSF (Figure \ref{fig:psfND}), both normalized to the peak pixel.
 
@@
 	}
-	\caption{The direct imaging PSF and coronagraphic PSF which is modified by the Lyot stop from \texttt{webbpsf}.
-Both images are normalized by the peak pixel value and have arbitrary array positions.
-Aperture photometry of the sources imaged through the corograph will have to use a large aperture encompassing the 6 outer peaks or apply careful background subtraction.
+	\caption{The \texttt{webbpsf} direct imaging PSF and coronagraphic PSF which is modified by the Lyot stop.
+Both images are normalized by the peak pixel value and have arbitrary array positions but the same height and width.
+Aperture photometry of the sources imaged through the coronograph will have to use a large aperture encompassing the 6 outer peaks or just use the central peak(s) and apply careful background subtraction.
 Both PSFs were calculated for NIRCam's long wavelength channel with a F430M filter.}
@@
 Correcting for any pinholes or blemishes in the ND square surface will likely dominate the error budget for the ND square absolute calibration.
-Accurate positioning can help align the source to the same location on the neutral density square and dithering can be used to check the surface irregularities.
+Positioning the sources consistently on the same pixel locations and using the same dither patterns will help with these errors.
+The dithers can be used to check the surface irregularities.
 
@@
 Thanks to Daniel Kiminki and John Stauffer for the selection of open clusters for this work and for finding targets based on initial data.
+Thanks to Richard Gray and Chris Corbally for their help in stellar classification and guidance with the Hectospec observations.
 Funding for the NIRCam team is provided by NASA Goddard Spaceflight Center.
@@
 
+%% The reference list follows the main body and any appendices.
+%% Use LaTeX's thebibliography environment to mark up your reference list.
+%% Note \begin{thebibliography} is followed by an empty set of
+%% curly braces.  If you forget this, LaTeX will generate the error
+%% "Perhaps a missing \item?".
+%%
+%% thebibliography produces citations in the text using \bibitem-\cite
+%% cross-referencing. Each reference is preceded by a
+%% \bibitem command that defines in curly braces the KEY that corresponds
+%% to the KEY in the \cite commands (see the first section above).
+%% Make sure that you provide a unique KEY for every \bibitem or else the
+%% paper will not LaTeX. The square brackets should contain
+%% the citation text that LaTeX will insert in
+%% place of the \cite commands.
+
+%% We have used macros to produce journal name abbreviations.
+%% AASTeX provides a number of these for the more frequently-cited journals.
+%% See the Author Guide for a list of them.
+
+%% Note that the style of the \bibitem labels (in []) is slightly
+%% different from previous examples.  The natbib system solves a host
+%% of citation expression problems, but it is necessary to clearly
+%% delimit the year from the author name used in the citation.
+%% See the natbib documentation for more details and options.
+
+\bibliographystyle{apj}
+\bibliography{abscal_biblio}
+
+\clearpage
+\pagebreak
+
 \appendix
@@
 
-%% The reference list follows the main body and any appendices.
-%% Use LaTeX's thebibliography environment to mark up your reference list.
-%% Note \begin{thebibliography} is followed by an empty set of
-%% curly braces.  If you forget this, LaTeX will generate the error
-%% "Perhaps a missing \item?".
-%%
-%% thebibliography produces citations in the text using \bibitem-\cite
-%% cross-referencing. Each reference is preceded by a
-%% \bibitem command that defines in curly braces the KEY that corresponds
-%% to the KEY in the \cite commands (see the first section above).
-%% Make sure that you provide a unique KEY for every \bibitem or else the
-%% paper will not LaTeX. The square brackets should contain
-%% the citation text that LaTeX will insert in
-%% place of the \cite commands.
+\subsection{UKIRT Calibration}
 
-%% We have used macros to produce journal name abbreviations.
-%% AASTeX provides a number of these for the more frequently-cited journals.
-%% See the Author Guide for a list of them.
-
-%% Note that the style of the \bibitem labels (in []) is slightly
-%% different from previous examples.  The natbib system solves a host
-%% of citation expression problems, but it is necessary to clearly
-%% delimit the year from the author name used in the citation.
-%% See the natbib documentation for more details and options.
-
-\bibliographystyle{apj}
-\bibliography{abscal_biblio}
-
-%\clearpage
+Our WFCAM data should be calibrated in a similar was as UKIDSS.
+Eiichi Egami says we can use the Viking Survey as an independent check on the UKIDSS flux calibration.
 

### 2017-02-07 ms.tex
I added a color mag diagram with G2 Vs identified.
I added a plot to show the field of view of the cluster, the G2 V stars and the NIRCam footprint.
I added some clarifications in the introduction and appendix.

@@
 The James Webb Space Telescope (JWST) offers unprecedented sensitivity and stability for science.
-Several of the science areas, such as supernovae measurements for dark energy measurements will require high accuracy absolute calibration.
+Several of the science areas, such as supernovae photometry for dark energy measurements will require high accuracy absolute calibration.
 We discuss a program to identify calibrators at the low end of the flux scale that will not saturate the NIRCam full frame mode.
@@
 It is still being developed and refined.
-Figure \ref{fig:JWStcalsWideF} shows several of the sources that will be used for flux calibration.
+Figure \ref{fig:JWStcalsWideF} shows several of the sources that will likely be used for flux calibration.
 These include three categories: 1) hot stars (white dwarf and OB stars) 2) G-stars (which are solar-like) and 3) A-type stars.
@@
 The size affects the number of DHS that can be included, so the noise in the DHS spectra over 1.1 -- 1.9$\mu$m at the given saturation limit for a 1 hour transit is shown in column 4 at native R $\sim$ \DHSresApprox\ resolution.}\label{tab:SatSNRsubA}
-\tablenotetext{a}{All parameters from \citet{pancino2010chem2420}.}
-\tablenotetext{b}{Parameters from \citet{anthonytwarog2016wiyn2506}. Error bars are formal standard errors of the mean, not necessarily capturing systematics.}
-\tablenotetext{c}{Parameters from \citet{molendaz2016spec6811}}
+\tablenotetext{a}{NGC 2420 parameters from \citet{pancino2010chem2420}.}
+\tablenotetext{b}{NGC 2506 parameters from \citet{anthonytwarog2016wiyn2506}. Error bars are formal standard errors of the mean, not necessarily capturing systematics.}
+\tablenotetext{c}{NGC 6811 parameters from \citet{molendaz2016spec6811}}
 \end{table}
@@
 The Hectospec instrument on the MMT \citep{fabricant2005hectospec,mink2007hectoFibers} was used to obtain spectra of candidate solar analogs in the clusters .
+
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.49\columnwidth]{colormag.pdf}
+\includegraphics[width=.49\columnwidth]{fov_ngc2420_spTypes.pdf}
+\caption{{\it Left} NGC 2420 color magnitude diagram with G2 V stars identified from classification. {\it Right} Field of view with NIRCam footprint.}\label{fig:NCFOV}
+\end{figure}
 
@@
 
+As a check on the maximum age, I downloaded Dartmouth Isochrones \citep{dotter2008dartmouth} and plotted the color-magnitude diagram in Figure \ref{fig:isochrones}.
+At 7 Gyr, the main sequence turnoff begins affecting the selection of stars near solar B-V.
+Nearly all open clusters are young ($\lesssim$ 5 Gyr) so this really only affects just NGC 188.
+
 \begin{figure}[!hbtp]

### 2017-02-10 ms.tex
I added a reference to NGC 188's age.
I changed the title to differentiate it from the STScI cal plan(s). Also added K band specificiation on magnitude.

@@
 
-\title{NIRCam Calibration Plan}
+\title{NIRCam Flux Calibration Plan}
 
@@
 \item {\bf Distance Modulus} The cluster must be distant enough to not saturate NIRCam's wide filters in full frame mode.
-The most easily saturated filter for G stars is the F090W, which corresponds to a G2~V star of 15.9.
+The most easily saturated filter for G stars is the F090W, which corresponds to a G2~V star of 15.9 in the $K$ band.
 This means the true distance modulus $(m - M)_0$ should be 12.6 for a solar absolute K=3.28 \citep{binney1998book}.
@@
 At 7 Gyr, the main sequence turnoff begins affecting the selection of stars near solar B-V.
-Nearly all open clusters are young ($\lesssim$ 5 Gyr) so this really only affects just NGC 188.
+Nearly all open clusters are young ($\lesssim$ 5 Gyr) so this really only affects just NGC 188 \citep[7.1 Gyr][]{elsanhoury2016ngc188}.
 

### 2017-02-14 ms.tex
I added some notes about NIRSpec, MIRI and possible problesm with white dwarfs after a discussion with George.

@@
 
+\subsection{Sections to Expand in this Report}
+
+George has some requests for this report.
+Consider adding notes on calibration of two more instruments.
+The solar spectrum is very well measured at infrared wavelengths, so it may be the best one for interpolation from optical/NIR into Far IR.
+\begin{enumerate}
+	\item MIRI: For the shorter wavelength MIRI bands (say F560W and F770W) photometry, George would like to observe the NIRCam faint G2V stars in order to have a sample of stars that have a highly accurate solar model
+	\item NIRSpec: We'd also want to test calibration of NIRSpec w/ our solar G2 V stars.
+George recommends the IFU or slits as opposed to MSA because it's less sensitive to positional accuracy.
+Note that we would only get 1 G2V star at a time.
+Also, beware that no bright stars from the cluster contaminate the field. MSA shutters that are stuck open may introduce significant amounts of stray light.
+\end{enumerate}
+Note, that George has two concerns about white dwarfs:
+\begin{enumerate}
+	\item debris disks emission - they have found that magnetic field trapping of dust around A stars can cause excess emission.
+White dwarfs have strong magnetic fields and could also trap nano-grain dust.
+George and Andras will probably write a paper on white dwarf dust in Fall of 2017.
+	\item uncertainties in the IR - white dwarfs don't have a lot of measurements in the IR.
+How can we be sure the models are good in the infrared?
+\end{enumerate}
+
 %% Use the figure environment and \plotone or \plottwo to include

### 2017-03-22 ms.tex
I updated the wording to the description of how the clusters were selected.

@@
 Furthermore, the age should be $\lesssim$7 Gyr to avoid main sequence turnoff of near-solar stars.
-\item {\bf Extinction} Extinction should be as small as possible to minimize the effects of extinction correction to photometry. Of the clusters found, E(B-V) $\lesssim < 0.1$.
+\item {\bf Extinction} Extinction should be as small as possible to minimize the effects of extinction correction to photometry. Of the clusters found, E(B-V) $\lesssim 0.1$.
 \item {\bf Distance Modulus} The cluster must be distant enough to not saturate NIRCam's wide filters in full frame mode.
@@
 The longer wavelength wide band filters (F200W, F277W, F356W, and F444W) will not saturate for a true distance modulus larger than 11.8.
-If one assumes an extinction of E(B-V) = 0.05 and a Galactic average extinction law \citep{cardelli1989}, the visual distance moduli $(m- M)_V$ should be an additional 0.14 mag.
-\item {\bf Metallicity} Ideally, the cluster should have near-solar metallicity so that the solar mass stars have solar luminosity and solar spectra. 
+If one assumes an extinction of E(B-V) = 0.05 and a Galactic average extinction law \citep{cardelli1989}, the visual distance modulus $(m- M)_V$ should be an additional 0.14 mag.
+Thus, to calibrate all filters, the visual distance modulus $(m- M)_V$ should be larger than 11.94.
+\item {\bf Metallicity} Ideally, the cluster should have near-solar metallicity so that the solar mass stars have a luminosity near 1 $L_\sun$ and a G2~V type spectrum.
 \item {\bf Compactness} The cluster should be relatively compact compared to NIRCam's FOV (2'$\times$2' per module). We selected clusters $\lesssim 15\arcmin$
@@
 The subarray to full frame conversion can be checked with medium band filters.
-NGC 2506 and NGC 6811 are next-best fits and have somewhat complimentary visibility windows, visible in Figure \ref{fig:clusterVis}. NGC 2420 and NGC 6811 have -0.08 $<=$ [Fe/H] $<=$ 0.05.
+NGC 2506 and NGC 6811 are next-best fits and have somewhat complimentary visibility windows, shown in Figure \ref{fig:clusterVis}. NGC 2420 and NGC 6811 have -0.08 $\le$ [Fe/H] $\le$ 0.05.
 NGC 2506, is metal poor at [Fe/H]=-0.32, so corrections must be made for changes to G2 V spectra due to metallicity.
@@
 
-The WEBDA database had parameters that were significantly different from the literature.
+After selecting the sources, we discovered that the WEBDA database had parameters that were significantly different from the literature for these individual clusters.
 For example E(B-V) = 0.16 for NGC 6811 whereas \citet{molendaz2016spec6811} has E(B-V) = 0.05.

### 2017-03-24 ms.tex
I added a description and example of the spectrum rectification procedure I created.

@@
 
+\clearpage
 \section{Spectral Typing of Candidate Analogs}
 The Hectospec instrument on the MMT \citep{fabricant2005hectospec,mink2007hectoFibers} was used to obtain spectra of candidate solar analogs in the clusters .
+We processed the data with the standard IDL routine \texttt{hsred}\footnote{https://www.mmto.org/node/536}
+
+We normalized the raw spectra output from \texttt{hsred} in order to pass it to a spectral rectification program \texttt{mkclass} \citep{gray2014classification}.
+The first step in the normalization was to get an approximately normalized curve from the strongly curved spectrum shown in Figure \ref{fig:SpecRect}.
+We fit an 8th order polynomial in log space to the flux as a function of wavelength.
+It is important to do the fit in log-space because in linear space there are regions (near 3800 $\AA$) where the flux drops to low values and the fit can have zero crossings.
+The resulting model (fit in linear space) results large negative values or NaNs when divided by the model, whereas the fit in log-space has no zero-crossings.
+The polynomial fit is done piecewise in 3 equally spaced regions to take on small scale curvature.
+
+The second step in the spectral rectification process is to normalize by the pseudo continuum and remove any residual curvature.
+This is again fit with an 8th order polynomial in a piecewise fashion in three equally spaced wavelength chunks.
+The modification for the second step is to do it in linear space (now that zero crossings will not occur) and also select only points greater than 1.0 to ensure they are continuum points.
+The two steps (with polynomial fits) and final resulting spectrum are shown for an example source in Figure \ref{fig:SpecRect}.
+
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.7\columnwidth]{O_0738209_p2134_rectification.pdf}
+\caption{The spectral rectification process happens in two steps 1) take out the strong curvature with a piecewise polynomial in log flux space (top panel) and 2) fit the points above 1.0 with a new piecewise polynomial in linear flux space.}\label{fig:SpecRect}
+\end{figure}
 

### 2017-03-26 ms.tex
I inserted the text for the stars classified in both runs.

@@
 The Hectospec instrument on the MMT \citep{fabricant2005hectospec,mink2007hectoFibers} was used to obtain spectra of candidate solar analogs in the clusters .
-We processed the data with the standard IDL routine \texttt{hsred}\footnote{https://www.mmto.org/node/536}
+We processed the data with the standard IDL routine \texttt{HSRED}\footnote{https://www.mmto.org/node/536}
 
-We normalized the raw spectra output from \texttt{hsred} in order to pass it to a spectral rectification program \texttt{mkclass} \citep{gray2014classification}.
+We normalized the raw spectra output from \texttt{HSRED} in order to pass it to a spectral rectification program \texttt{mkclass} \citep{gray2014classification}.
 The first step in the normalization was to get an approximately normalized curve from the strongly curved spectrum shown in Figure \ref{fig:SpecRect}.
@@
 \caption{{\it Left} NGC 2420 color magnitude diagram with G2 V stars identified from classification. {\it Right} Field of view with NIRCam footprint.}\label{fig:NCFOV}
+\end{figure}
+
+Figure \ref{fig:NCFOV} shows the photometry and positions of sources after 1 pass with Hectospec/MMT and Figure \ref{fig:NCFOV2ndrun} shows after a 2nd set of observations with Hectospec/MMT.
+
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.49\columnwidth]{colormag_two_runs.pdf}
+\includegraphics[width=.49\columnwidth]{fov_ngc2420_two_runs.pdf}
+\caption{We observed additional stars with Hectospec on the MMT search for additional G2~V sources. This shows the same plot as Figure \ref{figNCFOV} after a second Hectospec fiber configuration.
+{\it Left} NGC 2420 color magnitude diagram with G2 V stars identified from classification. {\it Right} Field of view with NIRCam footprint.}\label{fig:NCFOV2ndrun}
 \end{figure}

### 2017-03-26 ms.tex
I described how NGC 2506 has worse resolution because of the 600 gpm grating. Also, I updated the NGC 2420 classified stars plots to include F9-V and G2 IV-V classification.

@@
 \includegraphics[width=.49\columnwidth]{fov_ngc2420_two_runs.pdf}
-\caption{We observed additional stars with Hectospec on the MMT search for additional G2~V sources. This shows the same plot as Figure \ref{figNCFOV} after a second Hectospec fiber configuration.
+\caption{We observed additional stars with Hectospec on the MMT search for additional G2~V sources. This shows the same plot as Figure \ref{fig:NCFOV} after a second Hectospec fiber configuration.
 {\it Left} NGC 2420 color magnitude diagram with G2 V stars identified from classification. {\it Right} Field of view with NIRCam footprint.}\label{fig:NCFOV2ndrun}
 \end{figure}
+
+During the observing run in the Fall of 2016, the 600 gpm (1.9 - 2.2 $\AA$ resolution element) grating had to be removed for fixing and so we were forced to observe NGC 2506 with the 270 gpm (4.5 - 5.2 $\AA$ resolution element).
+This
 

### 2017-03-31 ms.tex
I added more details about the Hectospec configurations.

@@
 \section{Spectral Typing of Candidate Analogs}
+
+\subsection{Hectospec Observations}
+We observed NGC~2420 with two fiber configurations in the Spring and Fall of 2016.
+We used the 600 gpm grating (1.9 - 2.2 $\AA$ resolution element) to match with existing spectral template libraries with 3.6 $\AA$ resolution.
+We selected the central wavelength to be 4800 $\AA$ which means that the wavelength coverage is about 3550 to 6050 $\AA$, which covers several import criteria for G-star classification many of which are concentrated between 4000 and 4400 $\AA$.
+We obtained exposure times from 1.2 to 2 hours.
+The minimum fiber separation $\sim$20$\arcsec$ required that we observe in two configurations to increase the density of stars for which we had spectral classification.
+During the observing run in the Fall of 2016, the 600 gpm (1.9 - 2.2 $\AA$ resolution element) grating had to be removed for fixing and so we were forced to observe NGC 2506 with the 270 gpm (4.5 - 5.2 $\AA$ resolution element).
+
 The Hectospec instrument on the MMT \citep{fabricant2005hectospec,mink2007hectoFibers} was used to obtain spectra of candidate solar analogs in the clusters .
-We processed the data with the standard IDL routine \texttt{HSRED}\footnote{https://www.mmto.org/node/536}
+We processed the data with the standard IDL routine \texttt{HSRED}\footnote{https://www.mmto.org/node/536}, which applies automatic bias and flat field corrections, spectral extraction and wavelength calibration.
+\texttt{HSRED} can apply flux calibration for F-type stars, but we elected to rectify the spectra
 
@@
 We fit an 8th order polynomial in log space to the flux as a function of wavelength.
-It is important to do the fit in log-space because in linear space there are regions (near 3800 $\AA$) where the flux drops to low values and the fit can have zero crossings.
-The resulting model (fit in linear space) results large negative values or NaNs when divided by the model, whereas the fit in log-space has no zero-crossings.
+It is important to do the fit in log-space because in linear space there are regions (near 3800 $\AA$) where the best-fit polynomial drops to low values and the fit can have zero crossings.
+If this polynomial model (fit in linear space) is used to rectify the spectrum, the rectified spectrum will have large negative values or NaNs when divided by the model, whereas the fit in log-space has no zero-crossings and reduced systematics at low fluxes.
 The polynomial fit is done piecewise in 3 equally spaced regions to take on small scale curvature.
@@
 \includegraphics[width=.7\columnwidth]{O_0738209_p2134_rectification.pdf}
-\caption{The spectral rectification process happens in two steps 1) take out the strong curvature with a piecewise polynomial in log flux space (top panel) and 2) fit the points above 1.0 with a new piecewise polynomial in linear flux space.}\label{fig:SpecRect}
+\caption{The spectral rectification process happens in two steps 1) take out the strong curvature with a piecewise polynomial in log flux space (top panel) and 2) fit the points above 1.0 with a new piecewise polynomial in linear flux space.
+The resulting spectrum is used for classification.}\label{fig:SpecRect}
 \end{figure}
@@
 \end{figure}
-
-During the observing run in the Fall of 2016, the 600 gpm (1.9 - 2.2 $\AA$ resolution element) grating had to be removed for fixing and so we were forced to observe NGC 2506 with the 270 gpm (4.5 - 5.2 $\AA$ resolution element).
-This
 

### 2017-04-07 ms.tex
I added some notes from our discussion today on 64x64 subarray timing as well as more details on the Pan-Starrs color-magnitude diagrams.

@@
 We obtained $grizy$ Pan-Starrs photometry\citep{magnier2013photLadder,schlafly2012photcal,tonry2012panstarrsPhot} for all three clusters.
-We also looked up the $g$ - $r$ colors
+We also looked estimated the Pan-Starrs $g$ - $r$ colors from a Pickles G2~V spectrum using \texttt{pysynphot} \citep{lim2015pysynphot}, the measured extinction shown in Table \ref{tab:clusterProp} with a Milky Way Diffuse R(V)=3.1 \citet{cardelli1989} extinction law.
+Figure \ref{fig:cmdPS} shows the Pan-Starrs color magnitude diagram for the three clusters along with vertical bars with the expected solar $g$ - $r$ color for each cluster.
 
@@
 The dithers can be used to check the surface irregularities.
+
+\subsubsection{Clocking Issues for Small Subarrays}
+
+Marcia and Jarron have brought up this issue in a NIRCam STScI+External team telecon on on April 6, 2017. 
+There are either 2 or 3 extra (rows? pixels?) at the end of an integration due to a rounding error.
+So this could change the integration time for a 64$\times$64.
+This is a known bug in the ASIC micro-code.
 

### 2017-04-07 ms.tex
I added additional details on the Pan Starrs photometry as well as the correct position for the vertical bar showing the solar color.

--- 2017-03-31 ms.tex
@@
 \newcommand{\DHSgap}{0.04}
-
+\newcommand{\degree}{^\circ}
 \newcommand{\SOSSrange}{0.6 - 2.5~$\mu$m}
@@
 
-We obtained $grizy$ Pan-Starrs photometry\citep{magnier2013photLadder,schlafly2012photcal,tonry2012panstarrsPhot} for all three clusters.
-We also looked up the $g$ - $r$ colors
+We obtained $grizy$ Pan-Starrs photometry \citep{magnier2013photLadder,schlafly2012photcal,tonry2012panstarrsPhot} for all three clusters.
+Additionally, we used \citet{janes2013keplerPhot} B and V photometry for NGC~6811 which is in the Kepler field because there were more faint source detections.
+We also estimated the Pan-Starrs $g$ - $r$ and B-V colors from a Pickles G2~V spectrum using \texttt{pysynphot} \citep{lim2015pysynphot}, the measured extinction shown in Table \ref{tab:clusterProp} with a Milky Way Diffuse R(V)=3.1 \citet{cardelli1989} extinction law.
+Figure \ref{fig:cmdPS} shows the Pan-Starrs and \citet{janes2013keplerPhot} color magnitude diagram for the three clusters along with vertical bars with the expected solar color for each cluster: $g-r$ =0.42, $g-r$ = 0.43 and B-V = 0.67 for NGC~2420, NGC~2506 and NGC~6811 respectively.
+Note that the initial selection of NGC~2420 stars ignored the small extinction and put a higher priority on stars bluer than solar.
 
@@
 	}
-	\caption{Color-magnitudes of the 3 clusters.}
+	\caption{Color-magnitudes of the three clusters.
+	The main sequence in each cluster was fit with a polynomial and then three priority levels were chosen for follow-up spectroscopy.
+	The first priority targets were near-solar $g-r$ or B-V colors ($\pm 0.04, 0.03, 0.05$) that were within $\pm$4\arcmin\ of the cluster center (to concentrate in the NIRCam field of view).
+	The second priority were near-solar $g-r$ or B-V colors but with a wider field of view (1$\degree$) to include G2~V stars that could be observed with larger dithers.
+	Thirdly, any remaining main sequence stars that were within the 1$\degree$ hectospec field of view with reasonable signal to noise were selected to allow for errors in photometric color predictions and enable star cluster science at the main sequence turnoff point.}
 	\label{fig:cmdPS}

### 2017-04-07 ms.tex
I made edits to the abstract, intro and description of timing issues.

@@
 
-\title{NIRCam Flux Calibration Plan}
+\title{NIRCam Faint and Bright Flux Calibration Plan}
 
@@
 We obtain ground based photometry and spectroscopy of three clusters to find solar analog G2 V stars and a solar model spectrum to infer the fluxes in the NIRCam bands.
-Additionally, we discuss some of the NIRCam modes that can be used to tie JWST calibrations directly to primary calibrator stars.
+Additionally, we discuss some of the NIRCam modes that can be used to tie JWST calibrations directly to bright stars which have been calibrated against emissive reference spheres with the Midcourse Space Experiment (MSX).
 \end{abstract}
@@
 
-The James Webb Space Telescope \citep[JWST; e.g.][]{gardner2006SSRv} will need absolute calibration for many of its science goals.
-Many studies of dark energy make use of Type Ia Supernovae as standard candles and improvements to the absolute flux calibration are important for improving their luminosity distances.
-JWST will have no standard calibration sources onboard so all calibration must be performed with astronomical sources.
-While there were internal lamps in original designs, the envelopes for the filaments did not make it through testing so the sources were removed.
+The James Webb Space Telescope \citep[JWST; e.g.][]{gardner2006SSRv} will need absolute calibration to accomplish its science goals.
+One are where accurate flux calibration is especially important is dark energy science, which makes use of type Ia supernovae as standard candles.
+Absolute fluxes are especially important for improving type Ia supernova luminosity distances and thus the expansion history of the Universe.
+JWST will have no standard calibration sources onboard so all calibration must be performed with astronomical sources.\footnote{While NIRCam had internal lamps in original designs, the envelopes for the filaments broke during testing so the sources were removed.}
 
@@
 Observing these bright sources (which are bright naked eye stars) with JWST's NIRCam can be achieved with a combination of medium-band filters, small subarray sizes, a Lyot stop pupil mask (19\% transmission) and a neutral density (ND) filter.
-Using \texttt{webbpsf} and the throughputs in a NIRCam program called \texttt{pynrc}, we calculate the saturation limits for 2 groups in RAPID mode and find a K-magnitude of saturation of -4.0 for an A1 V star like Sirius and -3.7 for an M3 III star like Gacrux.
+Using \texttt{webbpsf} and the throughputs in a NIRCam program called \texttt{pynrc}, we calculate the saturation limits for 2 groups in RAPID mode and find a K-magnitude of saturation of $-$4.0 for an A1 V type star (Sirius is A1 V with K=$-$1.35) and $-$3.7 for an M3 III (Gacrux is $-$3.12).
 This means that the entire sample of stars from \citet{price2004msxCal} are observable in this coronagraphic neutral density mode.
@@
 Marcia and Jarron have brought up this issue in a NIRCam STScI+External team telecon on on April 6, 2017.
-There are either 2 or 3 extra (rows? pixels?) at the end of an integration due to a rounding error.
-So this could change the integration time for a 64$\times$64.
-This is a known bug in the ASIC micro-code.
+This is a known bug in the ASIC micro-code that can affect the integration times of small subarrays.
+There are sometimes unpredictable frames which will have an additional row time (so a 1/64) increase in frame time.
+This could potentially decrease the flux by 1.6\% so it is a concern for flux calibration, but it is also a rare occurrence, happening for 5 frames out of 8000.
+Multiple exposures and dither positions should help lessen this effect, especially if averaged with robust statistics.
 

### 2017-04-09 ms.tex
I began describing the UKIRT photometric data.
I added a figure to show the expected fluxes of the new program compared to the existing stars in the database.

@@
 \includegraphics[width=.6\columnwidth]{nircam_wide_filters.png}
-\caption{The NIRCam subarray saturation, full frame saturation and 10~$\sigma$ sensitivity limits for wide band imaging from \citet{gordon2011fluxplan2}.
+\includegraphics[width=.3\columnwidth]{calspec_and_new_clust.pdf}
+\caption{{\it Left:} The NIRCam subarray saturation, full frame saturation and 10~$\sigma$ sensitivity limits for wide band imaging from \citet{gordon2011fluxplan2}.
 The three values are shown as upper, middle and lower limit error bars respectively.
 For comparison, three classes of JWST calibrators are shown: hot stars including white dwarfs (blue), A-type stars (green) and G-type stars (red).
-Additional faint calibrators are needed to extend the sample from \citet{gordon2011fluxplan2} towards the faint limits of NIRCam.}\label{fig:JWStcalsWideF}
+Additional faint calibrators are needed to extend the sample from \citet{gordon2011fluxplan2} towards the faint limits of NIRCam.
+{\it Right:} The new expected G2 V calibrators as compared to the faintest G-type star in the calibration plan.}\label{fig:JWStcalsWideF}
 \end{figure}
@@
 \subsection{UKIRT Photometry}
+
+We observed all three clusters with WFCAM on the UKIRT telescope.
+This is the same instrument, pipeline and telescope for the UKIDSS survey.
+As recommended by the pipeline team, we used aperture photometry number 3 (1\arcsec\ radius) for the fluxes in the J, H and K bands.
 

### 2017-04-11 ms.tex
I got rid of the figure with the NIRCam FOV and fibers since it's not redundant with another one. Also put in a comment that this is a draft in progress.
I added some updates to my replica of the AbsCal Plan report figure with the three clusters.

@@
 
-%\slugcomment{DHS White Paper}
+\slugcomment{\textcolor{red}{NOTE, this is a work in progress}}
 
@@
 The James Webb Space Telescope \citep[JWST; e.g.][]{gardner2006SSRv} will need absolute calibration to accomplish its science goals.
-One are where accurate flux calibration is especially important is dark energy science, which makes use of type Ia supernovae as standard candles.
+One area where accurate flux calibration is especially important is dark energy science, which makes use of type Ia supernovae as standard candles.
 Absolute fluxes are especially important for improving type Ia supernova luminosity distances and thus the expansion history of the Universe.
@@
 \centering
-\includegraphics[width=.6\columnwidth]{nircam_wide_filters.png}
-\includegraphics[width=.3\columnwidth]{calspec_and_new_clust.pdf}
+\includegraphics[width=.48\columnwidth]{nircam_wide_filters.png}
+\includegraphics[width=.48\columnwidth]{calspec_and_new_clust.pdf}
 \caption{{\it Left:} The NIRCam subarray saturation, full frame saturation and 10~$\sigma$ sensitivity limits for wide band imaging from \citet{gordon2011fluxplan2}.
@@
 \caption{One of WFCam's 4 detectors near the cluster NGC 2420 which encompasses 315 objects from the 2MASS point source catalog.}\label{fig:wfcam3}
-\end{figure}
-
-\section{NIRCam Footprint}
-\begin{figure}[!hbtp]
-\centering
-\includegraphics[width=.4\columnwidth]{nircam_fov_fibers.pdf}
-\caption{NGC 2420 fibers on the first pass with the FOV of both the A and B modules of NIRCam.
-Only 10 stars fit within NIRCam's FOV.}\label{fig:NCFOV}
 \end{figure}

### 2017-04-14 ms.tex
I made several more updates to the labels and description of the NIRCam sat/sens figure.

@@
 \centering
-\includegraphics[width=.48\columnwidth]{nircam_wide_filters.png}
+%\includegraphics[width=.48\columnwidth]{nircam_wide_filters.png}
 \includegraphics[width=.48\columnwidth]{calspec_and_new_clust.pdf}
-\caption{{\it Left:} The NIRCam subarray saturation, full frame saturation and 10~$\sigma$ sensitivity limits for wide band imaging from \citet{gordon2011fluxplan2}.
+\caption{{\it Left:} The NIRCam subarray saturation, full frame saturation and 10~$\sigma$ sensitivity limits for wide band imaging from \citet{gordon2011fluxplan2} in one hour.
 The three values are shown as upper, middle and lower limit error bars respectively.
@@
 Additional faint calibrators are needed to extend the sample from \citet{gordon2011fluxplan2} towards the faint limits of NIRCam.
-{\it Right:} The new expected G2 V calibrators as compared to the faintest G-type star in the calibration plan.}\label{fig:JWStcalsWideF}
+Example G2~V \citet{castelli2004models} models are shown for stars expected in the three clusters NGC~6811, NGC~2420 and NGC~2506.
+}\label{fig:JWStcalsWideF}
 \end{figure}

### 2017-04-17 ms.tex
small wording updates to abstract, fig 1 caption and Hectospec observations section.

@@
 We discuss a program to identify calibrators at the low end of the flux scale that will not saturate the NIRCam full frame mode.
-We obtain ground based photometry and spectroscopy of three clusters to find solar analog G2 V stars and a solar model spectrum to infer the fluxes in the NIRCam bands.
+We obtained ground based photometry and spectroscopy of three clusters to find solar analog G2 V stars and a solar model spectrum to infer the fluxes in the NIRCam bands.
 Additionally, we discuss some of the NIRCam modes that can be used to tie JWST calibrations directly to bright stars which have been calibrated against emissive reference spheres with the Midcourse Space Experiment (MSX).
@@
 \includegraphics[width=.48\columnwidth]{calspec_and_new_clust.pdf}
-\caption{{\it Left:} The NIRCam subarray saturation, full frame saturation and 10~$\sigma$ sensitivity limits for wide band imaging from \citet{gordon2011fluxplan2} in one hour.
-The three values are shown as upper, middle and lower limit error bars respectively.
-For comparison, three classes of JWST calibrators are shown: hot stars including white dwarfs (blue), A-type stars (green) and G-type stars (red).
+\caption{CALSPEC models are plotted in comparison to NIRCam saturation and sensitivity limits, as shown in \citet{gordon2011fluxplan2}.
+The three values shown for each wideband filter are the subarray saturation (upper error limit), full frame saturation (middle circle) and 10~$\sigma$ sensitivity limit in one hour of imaging (lower error limit).
+Three classes of JWST calibrators are shown: hot stars including white dwarfs (blue), A-type stars (green) and G-type stars (red).
 Additional faint calibrators are needed to extend the sample from \citet{gordon2011fluxplan2} towards the faint limits of NIRCam.
@@
 We selected the central wavelength to be 4800 $\AA$ which means that the wavelength coverage is about 3550 to 6050 $\AA$, which covers several import criteria for G-star classification many of which are concentrated between 4000 and 4400 $\AA$.
-We obtained exposure times from 1.2 to 2 hours.
+We obtained exposure times of 1.7 hours (Spring 2016) and 2 hours (Fall 2016).
 The minimum fiber separation $\sim$20$\arcsec$ required that we observe in two configurations to increase the density of stars for which we had spectral classification.

### 2017-04-18 ms.tex
I added a section on the white dwarf network Guatham is working on and how it compares to NIRCam sensitivity limits.

@@
 It is still being developed and refined.
-Figure \ref{fig:JWStcalsWideF} shows several of the sources that will likely be used for flux calibration.
+Figure \ref{fig:JWSTcalsWideF} shows several of the sources that will likely be used for flux calibration.
 These include three categories: 1) hot stars (white dwarf and OB stars) 2) G-stars (which are solar-like) and 3) A-type stars.
@@
 The original flux calibration effort has mainly bright stars ($K \lesssim 15$).
-Example spectra for these calibrators are shown in Figure \ref{fig:JWStcalsWideF} with saturation and sensitivity limits of NIRCam's wide filters.
-Many of these spectra will saturate the NIRCam detectors when used in full frame (shown as the middle parts of the black ``error bars'').
+Example spectra for these calibrators are shown in Figure \ref{fig:JWSTcalsWideF} with saturation and sensitivity limits of NIRCam's wide filters.
+Many of these spectra will saturate the NIRCam detectors when used in full frame (shown as the middle parts of the black ``error bars'') for wide-band filters.
 Furthermore, there may be systematic errors when observing faint targets and low detector well depths.
@@
 For faint sources, however, the traps would be a larger fraction of the incoming electrons.
+Therefore, the charge traps (if not corrected for) would tend to decrease the flux of faint sources as compared to bright targets.
 
@@
 Additional faint calibrators are needed to extend the sample from \citet{gordon2011fluxplan2} towards the faint limits of NIRCam.
+We discuss an effort to add G2~V type stars in open clusters to the calibration sample.
 Example G2~V \citet{castelli2004models} models are shown for stars expected in the three clusters NGC~6811, NGC~2420 and NGC~2506.
-}\label{fig:JWStcalsWideF}
+}\label{fig:JWSTcalsWideF}
 \end{figure}
@@
 \item {\bf Metallicity} Ideally, the cluster should have near-solar metallicity so that the solar mass stars have a luminosity near 1 $L_\sun$ and a G2~V type spectrum.
-\item {\bf Compactness} The cluster should be relatively compact compared to NIRCam's FOV (2'$\times$2' per module). We selected clusters $\lesssim 15\arcmin$
+\item {\bf Compactness} The cluster should be relatively compact compared to NIRCam's FOV (2'$\times$2' per module).
+We selected clusters with WEBDA diameters $\lesssim 15\arcmin$
 \item {\bf Ancillary data} The clusters should have ancillary photometry from multiple observatories for cross-calibration. We preferred clusters with 2MASS, WISE and IRAC measurements.
@@
 The subarray to full frame conversion can be checked with medium band filters.
-NGC 2506 and NGC 6811 are next-best fits and have somewhat complimentary visibility windows, shown in Figure \ref{fig:clusterVis}. NGC 2420 and NGC 6811 have -0.08 $\le$ [Fe/H] $\le$ 0.05.
+NGC 2506 and NGC 6811 are next-best fits and have somewhat complimentary visibility windows, shown in Figure \ref{fig:clusterVis}. NGC 2420 and NGC 6811 have -0.05 $\le$ [Fe/H] $\le$ 0.04.
 NGC 2506, is metal poor at [Fe/H]=-0.32, so corrections must be made for changes to G2 V spectra due to metallicity.
@@
 After selecting the sources, we discovered that the WEBDA database had parameters that were significantly different from the literature for these individual clusters.
-For example E(B-V) = 0.16 for NGC 6811 whereas \citet{molendaz2016spec6811} has E(B-V) = 0.05.
+For example E(B-V)$_\mathrm{WEBDA}$ = 0.16 for NGC 6811 whereas \citet{molendaz2016spec6811} has E(B-V) = 0.05.
 We therefore did a literature search for the most recent available cluster parameters.
@@
 Figure \ref{fig:cmdPS} shows the Pan-Starrs and \citet{janes2013keplerPhot} color magnitude diagram for the three clusters along with vertical bars with the expected solar color for each cluster: $g-r$ =0.42, $g-r$ = 0.43 and B-V = 0.67 for NGC~2420, NGC~2506 and NGC~6811 respectively.
-Note that the initial selection of NGC~2420 stars ignored the small extinction and put a higher priority on stars bluer than solar.
+Note that the initial selection of NGC~2420 stars ignored the small extinction and put a higher priority on stars slightly bluer than solar.
 
@@
 
+\section{Faint White Dwarf Network}
+\citet{narayan2016wdnetwork} identified faint (V$\sim$18-19) DA white dwarfs for calibration of surveys such as with LSST, DECam, JWST and PanSTARRS.
+These sources are faint enough to avoid saturation with large aperture telescopes and have atmospheres largely characterizable with just two parameters T$_\mathrm{eff}$ and $\log(g)$.
+The fact that these DA dwarfs' atmospheres are dominated by hydrogen means that they are relatively simple to model at high resolution for calibrating photometric bandpasses.
+
+Figure \ref{fig:wideFiltWDCalspec} shows NIRCam sensitivity limits (10$\sigma$ in 1 hour), the CALSPEC database and representative G2~V stars identified in this paper which were already displayed in Figure \ref{fig:JWSTcalsWideF}.
+Additionally, four stars from \citet{narayan2016wdnetwork} are shown using the WD1657+343 white dwarf model (without extinction) as a placeholder.
+These WD stars nicely extend the sample of stars much deeper into the NIRCam sensitivity limit than previous targets.
+However, there is the possibility that the models for the stars in \citet{narayan2016wdnetwork} may not work effectively for the near-infrared.
+If there are small dust particles surrounding these white dwarfs, they could produce near-IR or mid-IR excesses.
+Additionally, there are few measurements into the infrared so extrapolation would be required.
+
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.49\columnwidth]{calspec_and_new_clust_wd.pdf}
+\caption{The NIRCam saturation and sensitivities are shown as in Figure \ref{fig:JWSTcalsWideF}.
+This time, we show the CALSPEC stars, G2~V open cluster stars and placeholder spectra for WD stars from \citet{narayan2016wdnetwork}.
+The faint WD stars .}\label{fig:wideFiltWDCalspec}
+\end{figure}
+
+\clearpage
 \section{Transferring to Directly Calibrated Sources - the NIRCam Flux Ladder}

### 2017-04-24 ms.tex
finished figure cap of faint white dwarf network stars.
I revised the discussion of NIRCam frame timing issues after discussing with Jarron.

@@
 The minimum fiber separation $\sim$20$\arcsec$ required that we observe in two configurations to increase the density of stars for which we had spectral classification.
-During the observing run in the Fall of 2016, the 600 gpm (1.9 - 2.2 $\AA$ resolution element) grating had to be removed for fixing and so we were forced to observe NGC 2506 with the 270 gpm (4.5 - 5.2 $\AA$ resolution element).
+During the observing run in the Fall of 2016, the 600 gpm (1.9 - 2.2 $\AA$ resolution element) grating had to be removed for repairs and so we were forced to observe NGC 2506 with the 270 gpm (4.5 - 5.2 $\AA$ resolution element).
 
@@
 If this polynomial model (fit in linear space) is used to rectify the spectrum, the rectified spectrum will have large negative values or NaNs when divided by the model, whereas the fit in log-space has no zero-crossings and reduced systematics at low fluxes.
-The polynomial fit is done piecewise in 3 equally spaced regions to take on small scale curvature.
+The polynomial fit is done piecewise in 3 equally spaced regions in order to model small scale curvature.
 
@@
 This time, we show the CALSPEC stars, G2~V open cluster stars and placeholder spectra for WD stars from \citet{narayan2016wdnetwork}.
-The faint WD stars .}\label{fig:wideFiltWDCalspec}
+The faint WD stars extend much farther into the NIRCam sensitivity wells than the CALSPEC and solar analog stars.}\label{fig:wideFiltWDCalspec}
 \end{figure}
@@
 As an independent check on those transfers, NIRCam can be used to observe directly calibrated stars (such as the MSX calibrators \citep{price2004msxCal}) and step down in brightness to faint standards used in JWST calibration.
-Figure \ref{fig:sensitivityLadder} shows a schematic of the steps beginning with Midcourse Survey Experiment (MSX) calibrators (as bright as $K \sim -3$) to faint JWST standards ($K \sim 16$).
+Figure \ref{fig:sensitivityLadder} shows a schematic of the steps beginning with Midcourse Space Experiment (MSX) calibrators (as bright as $K \sim -3$) to faint JWST standards ($K \sim 16$).
 
@@
 The exposure times given are the times needed to reach at least SNR=200, rounded up to the next group up the ramp.
-The saturation limit is the 80\% well depth for 2 non-destructive reads up the ramp following a reset.}
+The saturation limit is at 80\% well depth for 2 non-destructive reads up the ramp following a reset.}
 \vspace{0.05in}
@@
 Aperture photometry of the sources imaged through the coronograph will have to use a large aperture encompassing the 6 outer peaks or just use the central peak(s) and apply careful background subtraction.
-Both PSFs were calculated for NIRCam's long wavelength channel with a F430M filter.}
+Both PSFs were calculated for NIRCam's long wavelength channel with a F430M filter.\vspace{0.05in}}
 	\label{fig:psfComparison}
@@
 Marcia and Jarron have brought up this issue in a NIRCam STScI+External team telecon on on April 6, 2017.
-This is a known bug in the ASIC micro-code that can affect the integration times of small subarrays.
-There are sometimes unpredictable frames which will have an additional row time (so a 1/64) increase in frame time.
-This could potentially decrease the flux by 1.6\% so it is a concern for flux calibration, but it is also a rare occurrence, happening for 5 frames out of 8000.
-Multiple exposures and dither positions should help lessen this effect, especially if averaged with robust statistics.
+Jarron explained further on April 24, 2017.
+This is a known bug in the ASIC micro-code that can affect the frame times of small subarrays.
+The bug creates extra line overheads on small subarrays.
+For example, for a 32$\times$32 subarray, there are sometimes 2 line overheads and sometimes 3 line overheads about $\sim$40/60 \% of the time.
+Tony Magoncelli has found a way to deterministically predict when these extra frame times will occur.
+However, JWST will not produce enough data in flight to deterministically predict when the extra frame times occur so you'd have to average many frames together.
+For a 64$\times$ 64 subarray, there are almost always 2 line overheads.
+At a rate of about 5/8000 frames of test data, there were 3 line overheads.
+So, in the worst case unlucky scenario with 64$\times$64 subarray data in RAPID mode with 2 groups up the ramp, there could be an extra 1/64 or 1.6 \% increase in the slope due to the ASIC micro code.
+Given that 64$\times$64 frame time is only 0.05 s long, you could easily include hundreds of frames to average out the frame time issue with almost no change in efficiency since JWST acquisition, exposure and dithering overheads would be a much larger fraction of the time.
+I would estimate this would have less than 0.01\% of an effect on flux calibration.
 

### 2017-05-03 ms.tex
added a note about subarray full frame conversion.

@@
 \end{enumerate}
+Also, George has one idea with regards to subarray versus full frame imaging.
+Maybe we could a bright calibrator star (K$\sim$ 6) on the neutral density filter so that it doesn't saturate full frame.
+Then, observe the bright star in subarray and full frame to check the conversion from subarray to full frame for a given filter.
+Another idea would be to use a narrow-band filter to check the subarray/full frame conversion.
 

### 2017-05-04 ms.tex
I updated spectral rectification description with a continuous cubic spline instead of a piecewise polynomial.

@@
 The first step in the normalization was to get an approximately normalized curve from the strongly curved spectrum shown in Figure \ref{fig:SpecRect}.
-We fit an 8th order polynomial in log space to the flux as a function of wavelength.
+We fit a cubic spline in log space to the flux as a function of wavelength.
+The fit is iterated 3 times with 2$\sigma$ outlier rejection to account for strong spectral lines and cosmic rays.
 It is important to do the fit in log-space because in linear space there are regions (near 3800 $\AA$) where the best-fit polynomial drops to low values and the fit can have zero crossings.
 If this polynomial model (fit in linear space) is used to rectify the spectrum, the rectified spectrum will have large negative values or NaNs when divided by the model, whereas the fit in log-space has no zero-crossings and reduced systematics at low fluxes.
-The polynomial fit is done piecewise in 3 equally spaced regions in order to model small scale curvature.
 
 The second step in the spectral rectification process is to normalize by the pseudo continuum and remove any residual curvature.
-This is again fit with an 8th order polynomial in a piecewise fashion in three equally spaced wavelength chunks.
-The modification for the second step is to do it in linear space (now that zero crossings will not occur) and also select only points greater than 1.0 to ensure they are continuum points.
-The two steps (with polynomial fits) and final resulting spectrum are shown for an example source in Figure \ref{fig:SpecRect}.
+This is again fit with a cubic spline with 3 iterations of outlier rejection.
+The modification for the second step is to do it in linear space (now that zero crossings will not occur) and also select only points greater than 0.95 to ensure they are continuum points.
+The two steps (with cubic spline fits) and final resulting spectrum are shown for an example source in Figure \ref{fig:SpecRect}.
 
@@
 \centering
-\includegraphics[width=.7\columnwidth]{O_0738209_p2134_rectification.pdf}
-\caption{The spectral rectification process happens in two steps 1) take out the strong curvature with a piecewise polynomial in log flux space (top panel) and 2) fit the points above 1.0 with a new piecewise polynomial in linear flux space.
+\includegraphics[width=.7\columnwidth]{images/O_0738284_p2131_spec.pdf}
+\caption{The spectral rectification process happens in two steps 1) take out the strong curvature with a robust cubic spline in log flux space (top panel) and 2) fit the points above 0.95 with a cubic spline in linear flux space.
 The resulting spectrum is used for classification.}\label{fig:SpecRect}

### 2017-05-05 ms.tex
I put in a comparison of the spline fit rectification to piecewise polynomial.

@@
 {\it Left} NGC 2420 color magnitude diagram with G2 V stars identified from classification. {\it Right} Field of view with NIRCam footprint.}\label{fig:NCFOV2ndrun}
+\end{figure}
+
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.49\columnwidth]{colormag_two_runs.pdf}
+\includegraphics[width=.49\columnwidth]{images/colormagNGC_2420_spline_rect.pdf}
+\caption{\texttt{mkclass} is sensitive to the type of normalization I put into the rectified spectra.
+On the left, I used a piecewise 8th order polynomial.
+On the right side, I used a robust spline fit.
+The spline fit reduces some of the crazy giants identified as G5 V, but also identifies some stars with near-solar colors as G8 V.}\label{fig:splineVsPiecewiseCM}
 \end{figure}

### 2017-05-06 ms.tex
I added a few clarifications to the spectral rectification for input into mkclass.

@@
 During the observing run in the Fall of 2016, the 600 gpm (1.9 - 2.2 $\AA$ resolution element) grating had to be removed for repairs and so we were forced to observe NGC 2506 with the 270 gpm (4.5 - 5.2 $\AA$ resolution element).
+The spectral typing uncertainty grows with lower resolution.
 
@@
 It is important to do the fit in log-space because in linear space there are regions (near 3800 $\AA$) where the best-fit polynomial drops to low values and the fit can have zero crossings.
-If this polynomial model (fit in linear space) is used to rectify the spectrum, the rectified spectrum will have large negative values or NaNs when divided by the model, whereas the fit in log-space has no zero-crossings and reduced systematics at low fluxes.
+If this cubic spline model (fit in linear space) is used to rectify the spectrum, the rectified spectrum will have large negative values or NaNs when divided by the model, whereas the fit in log-space has no zero-crossings and reduced systematics at low fluxes.
 
@@
 \caption{The spectral rectification process happens in two steps 1) take out the strong curvature with a robust cubic spline in log flux space (top panel) and 2) fit the points above 0.95 with a cubic spline in linear flux space.
-The resulting spectrum is used for classification.}\label{fig:SpecRect}
+The resulting spectrum is used for classification.
+In this example it is source RA 07:38:28.4 +21:31.}\label{fig:SpecRect}
 \end{figure}

### 2017-05-08 ms.tex
I started removing sections that will only go in the supplement.

@@
 
-\section{Faint White Dwarf Network}
-\citet{narayan2016wdnetwork} identified faint (V$\sim$18-19) DA white dwarfs for calibration of surveys such as with LSST, DECam, JWST and PanSTARRS.
-These sources are faint enough to avoid saturation with large aperture telescopes and have atmospheres largely characterizable with just two parameters T$_\mathrm{eff}$ and $\log(g)$.
-The fact that these DA dwarfs' atmospheres are dominated by hydrogen means that they are relatively simple to model at high resolution for calibrating photometric bandpasses.
-
-Figure \ref{fig:wideFiltWDCalspec} shows NIRCam sensitivity limits (10$\sigma$ in 1 hour), the CALSPEC database and representative G2~V stars identified in this paper which were already displayed in Figure \ref{fig:JWSTcalsWideF}.
-Additionally, four stars from \citet{narayan2016wdnetwork} are shown using the WD1657+343 white dwarf model (without extinction) as a placeholder.
-These WD stars nicely extend the sample of stars much deeper into the NIRCam sensitivity limit than previous targets.
-However, there is the possibility that the models for the stars in \citet{narayan2016wdnetwork} may not work effectively for the near-infrared.
-If there are small dust particles surrounding these white dwarfs, they could produce near-IR or mid-IR excesses.
-Additionally, there are few measurements into the infrared so extrapolation would be required.
-
-\begin{figure}[!hbtp]
-\centering
-\includegraphics[width=.49\columnwidth]{calspec_and_new_clust_wd.pdf}
-\caption{The NIRCam saturation and sensitivities are shown as in Figure \ref{fig:JWSTcalsWideF}.
-This time, we show the CALSPEC stars, G2~V open cluster stars and placeholder spectra for WD stars from \citet{narayan2016wdnetwork}.
-The faint WD stars extend much farther into the NIRCam sensitivity wells than the CALSPEC and solar analog stars.}\label{fig:wideFiltWDCalspec}
-\end{figure}
-
-\clearpage
 \section{Transferring to Directly Calibrated Sources - the NIRCam Flux Ladder}
@@
 
-\appendix
-
-\section{Notes to Self}
-
-\subsection{Notes on using \texttt{mkclass}}
-
-\subsubsection{Code System}
-The library is organized into files like \texttt{t130l50p00.rbn}.
-The \texttt{t130} specifies 10 $\times$ the class coding system of O3 through M9 visible in the code \texttt{code3spt.c}.
-In this case, \texttt{t130} means code 13.0 and type B7.
-The luminosity class is next \texttt{l50} means V.
-We use the \texttt{libnor36} library, which appears to work with the "Roughtype 2" method for non-rectified data.
-The code runs into segmentation faults if attempting Roughtype 1 with the \texttt{libnor36} library.
-
-\subsubsection{Backgrounds}
-
-Zodiacal background is expressed as a function of the minimum zodiacal background in \texttt{pynrc}.
-From the code documentation: average across the sky has zfact = 2.5.
-In these models solar B-V=0.65 for 1~M$_\odot$ at 4.25 Gyr.
-
-\subsection{Isochrones}
-
-As a check on the maximum age, I downloaded Dartmouth Isochrones \citep{dotter2008dartmouth} and plotted the color-magnitude diagram in Figure \ref{fig:isochrones}.
-At 7 Gyr, the main sequence turnoff begins affecting the selection of stars near solar B-V.
-Nearly all open clusters are young ($\lesssim$ 5 Gyr) so this really only affects just NGC 188 \citep[7.1 Gyr][]{elsanhoury2016ngc188}.
-
-\begin{figure}[!hbtp]
-\centering
-\includegraphics[width=.7\columnwidth]{hr_isochrones.pdf}
-\caption{The Dartmouth isochrones \citep{dotter2008dartmouth}, for [Fe/H]=0, show that the age of the cluster should be $\lesssim 7 $Gyr before main sequence turnoff should begin to affect the identification of solar analogs.
-The red vertical line represents solar B-V.}\label{fig:isochrones}
-\end{figure}
-
-\subsection{UKIRT Calibration}
-
-Our WFCAM data should be calibrated in a similar was as UKIDSS.
-Eiichi Egami says we can use the Viking Survey as an independent check on the UKIDSS flux calibration.
-
-\subsection{Sections to Expand in this Report}
-
-George has some requests for this report.
-Consider adding notes on calibration of two more instruments.
-The solar spectrum is very well measured at infrared wavelengths, so it may be the best one for interpolation from optical/NIR into Far IR.
-\begin{enumerate}
-	\item MIRI: For the shorter wavelength MIRI bands (say F560W and F770W) photometry, George would like to observe the NIRCam faint G2V stars in order to have a sample of stars that have a highly accurate solar model
-	\item NIRSpec: We'd also want to test calibration of NIRSpec w/ our solar G2 V stars.
-George recommends the IFU or slits as opposed to MSA because it's less sensitive to positional accuracy.
-Note that we would only get 1 G2V star at a time.
-Also, beware that no bright stars from the cluster contaminate the field. MSA shutters that are stuck open may introduce significant amounts of stray light.
-\end{enumerate}
-Note, that George has two concerns about white dwarfs:
-\begin{enumerate}
-	\item debris disks emission - they have found that magnetic field trapping of dust around A stars can cause excess emission.
-White dwarfs have strong magnetic fields and could also trap nano-grain dust.
-George and Andras will probably write a paper on white dwarf dust in Fall of 2017.
-	\item uncertainties in the IR - white dwarfs don't have a lot of measurements in the IR.
-How can we be sure the models are good in the infrared?
-\end{enumerate}
-Also, George has one idea with regards to subarray versus full frame imaging.
-Maybe we could a bright calibrator star (K$\sim$ 6) on the neutral density filter so that it doesn't saturate full frame.
-Then, observe the bright star in subarray and full frame to check the conversion from subarray to full frame for a given filter.
-Another idea would be to use a narrow-band filter to check the subarray/full frame conversion.
-
 %% Use the figure environment and \plotone or \plottwo to include

### 2017-05-08 ms.tex
I added a few more details about the reference sphere observations with MSX.

@@
 The primary JWST standards for absolute calibration have been tied to directly calibrated photometric sources through transfers, such as with HST's STIS instrument.
-As an independent check on those transfers, NIRCam can be used to observe directly calibrated stars (such as the MSX calibrators \citep{price2004msxCal}) and step down in brightness to faint standards used in JWST calibration.
-Figure \ref{fig:sensitivityLadder} shows a schematic of the steps beginning with Midcourse Space Experiment (MSX) calibrators (as bright as $K \sim -3$) to faint JWST standards ($K \sim 16$).
+As an independent check on those transfers, NIRCam can be used to observe directly calibrated stars (such as the midcourse space experiment (MSX) calibrators \citep{price2004msxCal}) and step down in brightness to faint standards used in JWST calibration.
+The MSX ejected 1 cm radius reference spheres made of 6061-T6 aluminum alloy coated with Martin Black.
+Five of these spheres were ejected during the cryogenic lifetime of MSX's SPIRIT III sensor.
+These spheres were observed for about 1/3 of an orbital period and then at least one star was observed in the same data collection event.
 
@@
 
+Figure \ref{fig:sensitivityLadder} shows a schematic of the steps beginning with MSX calibrators (as bright as $K \sim -3$) to faint JWST standards ($K \sim 16$).
 The methodology of the flux ladder is that only one change is made per step - either an instrument re-configuration is made on the same source or a new source is measured with the same instrument configuration.

### 2017-05-08 ms.tex
Cleaned up and updated the Hectospec classification section.

@@
 We processed the data with the standard IDL routine \texttt{HSRED}\footnote{https://www.mmto.org/node/536}, which applies automatic bias and flat field corrections, spectral extraction and wavelength calibration.
-\texttt{HSRED} can apply flux calibration for F-type stars, but we elected to rectify the spectra
+\texttt{HSRED} can apply flux calibration for F-type stars, but we elected to rectify the spectra.
+Flux calibration is not crucial to spectral typing G-type stars since the spectrum is relatively flat in the optical (Chris Corbally, priv. communication).
 
@@
 It is important to do the fit in log-space because in linear space there are regions (near 3800 $\AA$) where the best-fit polynomial drops to low values and the fit can have zero crossings.
-If this cubic spline model (fit in linear space) is used to rectify the spectrum, the rectified spectrum will have large negative values or NaNs when divided by the model, whereas the fit in log-space has no zero-crossings and reduced systematics at low fluxes.
+If this cubic spline model (fit in linear space) is used to rectify the spectrum, the rectified spectrum will have large negative values or NaNs when divided by the model, whereas the fit in log-space has no zero-crossings.
 
@@
 \includegraphics[width=.7\columnwidth]{images/O_0738284_p2131_spec.pdf}
-\caption{The spectral rectification process happens in two steps 1) take out the strong curvature with a robust cubic spline in log flux space (top panel) and 2) fit the points above 0.95 with a cubic spline in linear flux space.
+\caption{The Hectospec spectra are rectified in two steps 1) to take out the strong curvature with a robust cubic spline in log flux space (top panel) and 2) to fit the points above 0.95 with a cubic spline in linear flux space.
 The resulting spectrum is used for classification.
-In this example it is source RA 07:38:28.4 +21:31.}\label{fig:SpecRect}
+In this example for the source at 07:38:28.5 +21:31:39.7, spectral classification with \texttt{mkclass} eventually gives a spectral type of F8 IV.}\label{fig:SpecRect}
 \end{figure}
+
+\subsection{Spectral Classification}
+
+We used the automatic ``expert'' classification system \texttt{mkclass} \citep{gray2014classification} to classify the stars.
+This program is different from automated neural networks in that it directly uses the same methods as a human classifier does, rather than being trained on a specific set of data.
+The \texttt{mkclass} programs comes with a library of standards at 3.6$\AA$ resolution standards and 1.8$\AA$ standards.
+Our Hectospec data with the 600 gpm grating has a spectral resolution of 1.9 to 2.2$\AA$ so we convolve it with a Gaussian kernel to match the 3.6$\AA$ library.
+We use 3 iterations and ``roughtype'' 2.
 
@@
 \centering
-\includegraphics[width=.49\columnwidth]{colormag.pdf}
-\includegraphics[width=.49\columnwidth]{fov_ngc2420_spTypes.pdf}
-\caption{{\it Left} NGC 2420 color magnitude diagram with G2 V stars identified from classification. {\it Right} Field of view with NIRCam footprint.}\label{fig:NCFOV}
+\includegraphics[width=.49\columnwidth]{colormagNGC_2420.pdf}
+\includegraphics[width=.49\columnwidth]{fovNGC_2420.pdf}
+\caption{{\it Left:} A color magnitude diagram from the Pan Starrs photometry with the sources that were observed with Hectospec and classified by \texttt{mkclass}.
+The G2~V sources line up with with the expected solar $g-r$ from a Pickles G2~V spectrum (red vertical line).
+{\it Right} The field of view of the Pan-Starrs photometry over-plotted with the same sources.
+Two rectangles are drawn to represent the field of view of the NIRCam module A and module B.
+Up to 3 G2~V sources may be observed simultaneously with NIRCam and more can be included with a dither pattern.
+The NIRISS field of view is similar to one of NIRCam's modules and could observe 2 G2~V sources at a time. }\label{fig:ngc2420ClassCM}
 \end{figure}
 
-Figure \ref{fig:NCFOV} shows the photometry and positions of sources after 1 pass with Hectospec/MMT and Figure \ref{fig:NCFOV2ndrun} shows after a 2nd set of observations with Hectospec/MMT.
-
-\begin{figure}[!hbtp]
-\centering
-\includegraphics[width=.49\columnwidth]{colormag_two_runs.pdf}
-\includegraphics[width=.49\columnwidth]{fov_ngc2420_two_runs.pdf}
-\caption{We observed additional stars with Hectospec on the MMT search for additional G2~V sources. This shows the same plot as Figure \ref{fig:NCFOV} after a second Hectospec fiber configuration.
-{\it Left} NGC 2420 color magnitude diagram with G2 V stars identified from classification. {\it Right} Field of view with NIRCam footprint.}\label{fig:NCFOV2ndrun}
-\end{figure}
-
-\begin{figure}[!hbtp]
-\centering
-\includegraphics[width=.49\columnwidth]{colormag_two_runs.pdf}
-\includegraphics[width=.49\columnwidth]{images/colormagNGC_2420_spline_rect.pdf}
-\caption{\texttt{mkclass} is sensitive to the type of normalization I put into the rectified spectra.
-On the left, I used a piecewise 8th order polynomial.
-On the right side, I used a robust spline fit.
-The spline fit reduces some of the crazy giants identified as G5 V, but also identifies some stars with near-solar colors as G8 V.}\label{fig:splineVsPiecewiseCM}
-\end{figure}
+Figure \ref{fig:ngc2420ClassCM} shows the spectral types output by \texttt{mkclass} in both color-magnitude space as well as the field of view with boxes to represent the NIRCam arrays for NGC~2420.
+A single pointing could include 3 G2~V sources and more can be covered with a dither pattern.
+In \ref{fig:ngc2420ClassCM} we compare the observed Pan-Starrs colors of the G2~V spectral type stars to a Pickles library spectrum.
+After applying a R(V)=3.1 \citet{cardelli1989} Milky Way Diffuse extinction law with E(B-V)=0.04, the Pickles spectrum lines up very closely (within 0.021) of the expected $g-r$=0.042.
 

### 2017-05-08 ms.tex
I added more details to the by eye classification.

@@
 After applying a R(V)=3.1 \citet{cardelli1989} Milky Way Diffuse extinction law with E(B-V)=0.04, the Pickles spectrum lines up very closely (within 0.021) of the expected $g-r$=0.042.
+
+\subsection{Visual Classification}
+
+As recommended by C. Corbally, the \texttt{mkclass} classifications of near-solar stars were checked by eye.
+A graphical user interface explorer was made to compare template classification spectra with the observed Hectospec spectra\footnote{https://github.com/eas342/mkclassfication\_viewer}.
+Figure \ref{fig:0738284p2133class} shows the Hectospec spectrum of a source at 07:38:28.4 +21:33 that \texttt{mkclass} identifies as G2~V.
+The line ratios of Ca I 4226~$\AA$, H$\delta$, H$\gamma$ and Fe I lines are most consistent with a G2 V type.
+
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.95\columnwidth]{O_0738284_p2133_class_g2v.pdf}
+\caption{An example G2~V source found by \texttt{mkclass} (07:38:28.4 +21:33) is visually checked against spectral templates.
+Of particular importance for temperature classification are the Ca I 4226~$\AA$, H$\delta$, H$\gamma$ and Fe I lines highlighted above \citep{gray2009specClass}.
+Two standards (G2 V and G1.5 V) are shown for comparison.}\label{fig:0738284p2133class}
+\end{figure}
 

### 2017-05-10 ms.tex
I incorporated the suggestions George gave me.

@@
 Furthermore, there may be systematic errors when observing faint targets and low detector well depths.
-\textcolor{red}{[Have a detector person - Karl, Jarron or George read the rest of this paragraph:]}
 As an example of a systematic detector effect, consider charge traps within a detector.
@@
 \end{figure}
+
+These clusters also allow for accurate calibration of MIRI imager with solar analogs.
+For example, a typical G2~V star in NGC~2420 can be measured in the MIRI F1000W filter with a signal to ratio of about 150 in 1000 seconds of integration.
+Although this integration time is considerably longer than for NIRCam imaging, they are still comparable to the 1800 second slew time charged in APT.
+Thus, it should require a smaller time allocation for a 1000 sec MIRI flux standard observation than two flux standards separated in the sky with NIRCam.
 
@@
 
+These steps will be adequate to calibrate to within a few percent.
+To obtain the most accurate possible calibration to 2MASS requires that slight photometric offsets in the 2MASS catalog in different areas of the sky be identified and corrected.
+These offsets can be identified by looking of the behavior of 2MASS-W1 colors, selecting a subset of stars (e.g., between A and mid-G) that are particularly well behaved in this color (e.g., no strong absorptions).
+Once this step has been completed, it will still be necessary to tie the corrected 2MASS system into true absolute calibration.
+
 \clearpage
@@
 \subsection{Hectospec Observations}
+
+We used the Hectospec instrument on the MMT \citep{fabricant2005hectospec,mink2007hectoFibers} to obtain spectra of candidate solar analogs in the clusters.
 We observed NGC~2420 with two fiber configurations in the Spring and Fall of 2016.
 We used the 600 gpm grating (1.9 - 2.2 $\AA$ resolution element) to match with existing spectral template libraries with 3.6 $\AA$ resolution.
-We selected the central wavelength to be 4800 $\AA$ which means that the wavelength coverage is about 3550 to 6050 $\AA$, which covers several import criteria for G-star classification many of which are concentrated between 4000 and 4400 $\AA$.
+We selected the central wavelength to be 4800 $\AA$ which means that the wavelength coverage is about 3550 to 6050 $\AA$, which covers several import features for G-star classification many of which are concentrated between 4000 and 4400 $\AA$.
 We obtained exposure times of 1.7 hours (Spring 2016) and 2 hours (Fall 2016).
@@
 
-The Hectospec instrument on the MMT \citep{fabricant2005hectospec,mink2007hectoFibers} was used to obtain spectra of candidate solar analogs in the clusters .
 We processed the data with the standard IDL routine \texttt{HSRED}\footnote{https://www.mmto.org/node/536}, which applies automatic bias and flat field corrections, spectral extraction and wavelength calibration.
@@
 This calibrator star would now be observable in full frame mode without saturation so the next step would be a conversion from subarray to full frame on the same source.
+Since the solar analog flux standards identified in this program are in a cluster, there are many sources available for photometry.
+It may be advantageous to make an additional measurement to confirm the subarray to full frame conversion using a concentration of stars in a cluster over a range in magnitude.
 To calibrate the wide band filters, such as F444W, one final step would be needed to go from the medium to wide band photometry using a model for the star.
@@
 A color correction would have to be applied for the neutral density filter (since it is wavelength dependent) when transferring to an un-occulted region.
-Additionally, the Lyot stop that must be in place to use the neutral density filter so the total improvement on saturation limits is 11 mags over direct imaging.
+Additionally, the Lyot stop must be in place to use the neutral density filter so the total improvement on saturation limits is 11 mags over direct imaging.
 Care must be taken with dithering to ensure that non-uniform optical depth of the neutral density filter doesn't affect the photometry.
@@
 This mode still has a saturation limit of $K$=4.6 to 3.5 for the F322W2  filter and 2048$\times$64 subarray \citep{greene2016wfss}, which does not reach to the MSX standards.
-This could be potentially combined with the coronagraphic pupil, but this combination has been tested or explored in detail.
+This could be potentially combined with the coronagraphic pupil, but this combination has not been tested or explored in detail.
 One could potentially observe small pieces of the spectrum at a time with a subarray that are all combined to create a spectrum, but this would add time and may be difficult to implement.
@@
 If one stitched together a spectrum from these subarrays along the spectrum, this could theoretically be used on all MSX stars.
-However, the time to build up 32 pieces
+However, as with the grism mode above, there would be significant changes and additions to the flight software to implement a mode that would build a spectrum out of 32 different subarrays.
 \item \textbf{Extra Small Subarrays} There will be an engineering jitter monitoring test with an 8 $\times$ 8 subarray.
-There may be complications with calculating accurate integration times in this mode because any uncertainty's affecting a frame time could be a significant fraction of the $\sim$ 2 ms frame time.
+There may be complications with calculating accurate integration times in this mode because any uncertainties affecting a frame time could be a significant fraction of the $\sim$ 2 ms frame time.
 The background annulus would be limited for such small subarrays.
@@
 
-Figure \ref{fig:msxNCfilterOverlap} shows the MSX filters B1 and B2 as compared to the NIRCam long wavelength filters -- we only include filters that have some overlap.
-The F430M filter is the best match with the MSX bands.
-Figure \ref{fig:msxNCfilterOverlap} also shows model spectra from \citet{castelli2004models} for the MSX calibrator stars in \citet{price2004msxCal} near these bandpasses.
-The flux has been normalized for each star at 3.6~$\mu$m and then offset for clarity.
-We use the nearest match between the stellar types from the Simbad database and the suggested \citet{castelli2004models} parameters.\footnote{http://www.stsci.edu/hst/observatory/crds/castelli\_kurucz\_atlas.html}
-
-Observing these bright sources (which are bright naked eye stars) with JWST's NIRCam can be achieved with a combination of medium-band filters, small subarray sizes, a Lyot stop pupil mask (19\% transmission) and a neutral density (ND) filter.
+Observing the MSX flux standards (which are bright naked eye stars) with JWST's NIRCam can be achieved with a combination of medium-band filters, small subarray sizes, a Lyot stop pupil mask (19\% transmission) and a neutral density (ND) filter.
 Using \texttt{webbpsf} and the throughputs in a NIRCam program called \texttt{pynrc}, we calculate the saturation limits for 2 groups in RAPID mode and find a K-magnitude of saturation of $-$4.0 for an A1 V type star (Sirius is A1 V with K=$-$1.35) and $-$3.7 for an M3 III (Gacrux is $-$3.12).
@@
 
-\begin{figure}[!hbtp]
-\centering
-\includegraphics[width=.55\columnwidth]{msx_nircam_filt.pdf}
-\caption{NIRCam filter throughputs (top), MSX filter throughputs \citep{egan1999msxGuide} (middle) and model spectra of MSX calibrator stars (bottom).
-F430M best matches the MSX filters.}\label{fig:msxNCfilterOverlap}
-\end{figure}
+\subsection{Checking the subarray}
+The solar analog P330-E is a commonly used standard because of its similarity to the sun.
+P330-E fits as an offshoot of the flux calibration ladder in Figure \ref{fig:sensitivityLadder} as ``Intermediate JWST Standard.'' 
+This standard is too bright for full frame NIRCam imaging in wide filters, but it is worth noting that the narrowband filters such as F212N can be used in full frame just at the limit of saturation.
+This may serve as a useful conversion check between subarray and full frame imaging.
 

### 2017-05-10 ms.tex
I added a few more notes about George's idea of a transfer all the way from alpha Cen A to P330-E.

@@
 For the next step, this same instrument configuration will be used on a bright JWST standard, such as HD 37962 (G2 V, $K$=6.27).
-Getting sufficient signal to noise (S/N$\gtrsim$200) on an intermediate JWST calibrator such as P-330E (G2 V, $K$=11.4) with the neutral density square in place would require unfeasibly long integration times so the bright calibrators are preferred for steps 2 and 3.
+Getting sufficient signal to noise (S/N$\gtrsim$200) on an intermediate JWST calibrator such as P-330E (G2 V, $K$=11.4) with the neutral density square in place would require long integration times so the bright calibrators are preferred for steps 2 and 3.
+
+However, if sufficient time is available for calibration, it is possible to convert from an MSX standard to an intermediate JWST standard in one step.
+To begin, the F212N filter could be selected in the filter wheel to observe a bright MSX star with the neutral density filter and Lyot pupil mask.
+The same setup could be arranged on P330-E and observed for 7.5 hours to achieve a SNR=200.
+If the F212N filter is used to observe P330-E with a full frame mode, it just barely is observable with 2 groups in RAPID mode before reaching full well saturation.
+The advantage with this single step from subarray neutral density filters to full frame direct imaging is that it is fewer steps.
+The disadvantage is that there would be a large disparity in detector well depth between the vertical and horizontal steps on this ladder.
 

### 2017-05-11 ms.tex
This is the draft I'm sending to the AbsFlux WG. I went through and edited and cleaned up the writeup.

@@
 Absolute fluxes are especially important for improving type Ia supernova luminosity distances and thus the expansion history of the Universe.
-JWST will have no standard calibration sources onboard so all calibration must be performed with astronomical sources.\footnote{While NIRCam had internal lamps in original designs, the envelopes for the filaments broke during testing so the sources were removed.}
+JWST will have no standard calibration sources onboard so all calibration must be performed with astronomical sources.
 
@@
 If one assumes an extinction of E(B-V) = 0.05 and a Galactic average extinction law \citep{cardelli1989}, the visual distance modulus $(m- M)_V$ should be an additional 0.14 mag.
-Thus, to calibrate all filters, the visual distance modulus $(m- M)_V$ should be larger than 11.94.
+Thus, to calibrate all wide band filters in full frame mode, the visual distance modulus $(m- M)_V$ should be larger than 11.94.
 \item {\bf Metallicity} Ideally, the cluster should have near-solar metallicity so that the solar mass stars have a luminosity near 1 $L_\sun$ and a G2~V type spectrum.
@@
 This is the same instrument, pipeline and telescope for the UKIDSS survey.
-As recommended by the pipeline team, we used aperture photometry number 3 (1\arcsec\ radius) for the fluxes in the J, H and K bands.
+As recommended by the UKIRT pipeline team (Mike Irwin, private communication), we used aperture photometry number 3 (1\arcsec\ radius) for the fluxes in the J, H and K bands.
 
@@
 Our Hectospec data with the 600 gpm grating has a spectral resolution of 1.9 to 2.2$\AA$ so we convolve it with a Gaussian kernel to match the 3.6$\AA$ library.
-We use 3 iterations and ``roughtype'' 2.
+We use 3 iterations, the \texttt{mkclass} default.
 
@@
 \includegraphics[width=.49\columnwidth]{fovNGC_2420.pdf}
-\caption{{\it Left:} A color magnitude diagram from the Pan Starrs photometry with the sources that were observed with Hectospec and classified by \texttt{mkclass}.
+\caption{{\it Left:} A color magnitude diagram from the Pan Starrs photometry of NGC~2420 with the sources that were observed with Hectospec and classified by \texttt{mkclass}.
 The G2~V sources line up with with the expected solar $g-r$ from a Pickles G2~V spectrum (red vertical line).
@@
 As an independent check on those transfers, NIRCam can be used to observe directly calibrated stars (such as the midcourse space experiment (MSX) calibrators \citep{price2004msxCal}) and step down in brightness to faint standards used in JWST calibration.
-The MSX ejected 1 cm radius reference spheres made of 6061-T6 aluminum alloy coated with Martin Black.
+The MSX ejected 1 cm radius reference spheres made of 6061-T6 aluminum alloy coated with Martin Black, for which the thermal and emissive properties were well understood.
 Five of these spheres were ejected during the cryogenic lifetime of MSX's SPIRIT III sensor.
@@
 Figure \ref{fig:sensitivityLadder} shows a schematic of the steps beginning with MSX calibrators (as bright as $K \sim -3$) to faint JWST standards ($K \sim 16$).
-The methodology of the flux ladder is that only one change is made per step - either an instrument re-configuration is made on the same source or a new source is measured with the same instrument configuration.
+The methodology of the flux ladder is that only one change is made per step - either an instrument re-configuration is made on the same source (a horizontal move) or a new source is measured with the same instrument configuration (a vertical move).
 As listed in Table \ref{tab:conversionSteps}, the direct calibrator would be observed in a neutral density square, subarray and medium band filter while using the coronagraphic pupil.
@@
 Getting sufficient signal to noise (S/N$\gtrsim$200) on an intermediate JWST calibrator such as P-330E (G2 V, $K$=11.4) with the neutral density square in place would require long integration times so the bright calibrators are preferred for steps 2 and 3.
-
-However, if sufficient time is available for calibration, it is possible to convert from an MSX standard to an intermediate JWST standard in one step.
-To begin, the F212N filter could be selected in the filter wheel to observe a bright MSX star with the neutral density filter and Lyot pupil mask.
-The same setup could be arranged on P330-E and observed for 7.5 hours to achieve a SNR=200.
-If the F212N filter is used to observe P330-E with a full frame mode, it just barely is observable with 2 groups in RAPID mode before reaching full well saturation.
-The advantage with this single step from subarray neutral density filters to full frame direct imaging is that it is fewer steps.
-The disadvantage is that there would be a large disparity in detector well depth between the vertical and horizontal steps on this ladder.
 
@@
 Since the solar analog flux standards identified in this program are in a cluster, there are many sources available for photometry.
-It may be advantageous to make an additional measurement to confirm the subarray to full frame conversion using a concentration of stars in a cluster over a range in magnitude.
+It may be useful to make additional measurements to confirm the subarray to full frame conversion using a concentration of stars in a cluster over a range in magnitude.
 To calibrate the wide band filters, such as F444W, one final step would be needed to go from the medium to wide band photometry using a model for the star.
@@
 
+\subsection{Using intermediate Standards to Check the Flux Ladder}
+
 Figure \ref{fig:sensitivityLadder} shows that an intermediate JWST standard such as P-330 E can be used to check transfers and detector linearity corrections.
-This step would not be a ``rung'' in the NIRCam flux ladder since it would require more transfers to achieve the last step of full frame wide band imaging, but serves as another check on the transfers from bright to faint targets.
+The solar analog P330-E is a commonly used standard because of its similarity to the sun.
+This step would not be an essential ``rung'' in the NIRCam flux ladder (since it involves more steps) but a useful check on other transfers.
+
+However, if sufficient time is available for calibration, it is possible to convert from an MSX standard to full frame imaging in a narrowband mode in one step by using an intermediate JWST standard.
+To begin, the F212N filter could be selected in the filter wheel to observe a bright MSX star with the neutral density filter and Lyot pupil mask.
+The same setup could be arranged on P330-E and observed for 7.5 hours to achieve a SNR=200.
+If the F212N filter is used to image P330-E with a full frame direct imaging mode, it is just barely is observable with 2 groups in RAPID mode before reaching full well saturation.
+The F212N filter is chosen since there are few stellar absorption lines in this filter.
+The advantage with this single transfer from an MSX standard to a full frame P330-E image is that it fewer steps than the ladder described above.
+The disadvantage is that there would be a large disparity in detector well depth between the vertical and horizontal steps on this ladder.
+If flux calibration time is available, this alternative flux ladder or simply the ``offshoot'' would serve as a check on the conversion from faint to bright targets.
 
@@
 However, one needs to read out larger sized subarrays to encompass the entire hexagonal PSF so this somewhat cancels out the effect of spreading the light out over many pixels.
-For a very narrowband filter such as F212N, the K-band saturation limit for a weak lens observation with a 128$\times$128 subarray is 0.9 mag for a G2V star, which does not quite reach the MSX calibrators.
+For a very narrowband filter such as F212N, the K-band saturation limit for a weak lens observation with a 128$\times$128 subarray is 0.9 mag (Vega mag) for a G2V star, which does not quite reach the MSX calibrators.
 \end{itemize}
@@
 
-\subsection{Tie-in to MSX}
+\subsection{Observing MSX Stars}
 
 Observing the MSX flux standards (which are bright naked eye stars) with JWST's NIRCam can be achieved with a combination of medium-band filters, small subarray sizes, a Lyot stop pupil mask (19\% transmission) and a neutral density (ND) filter.
-Using \texttt{webbpsf} and the throughputs in a NIRCam program called \texttt{pynrc}, we calculate the saturation limits for 2 groups in RAPID mode and find a K-magnitude of saturation of $-$4.0 for an A1 V type star (Sirius is A1 V with K=$-$1.35) and $-$3.7 for an M3 III (Gacrux is $-$3.12).
+Using \texttt{webbpsf} and the throughputs in a NIRCam program called \texttt{pynrc}\footnote{https://github.com/JarronL/pynrc.git}, we calculate the saturation limits for 2 groups in RAPID mode and find a K-magnitude of saturation of $-$4.0 for an A1 V type star (Sirius is A1 V with K=$-$1.35) and $-$3.7 for an M3 III (Gacrux is $-$3.12).
 This means that the entire sample of stars from \citet{price2004msxCal} are observable in this coronagraphic neutral density mode.
-
-\subsection{Checking the subarray}
-The solar analog P330-E is a commonly used standard because of its similarity to the sun.
-P330-E fits as an offshoot of the flux calibration ladder in Figure \ref{fig:sensitivityLadder} as ``Intermediate JWST Standard.'' 
-This standard is too bright for full frame NIRCam imaging in wide filters, but it is worth noting that the narrowband filters such as F212N can be used in full frame just at the limit of saturation.
-This may serve as a useful conversion check between subarray and full frame imaging.
 
@@
 A Lyot pupil mask must be used when imaging through the neutral density squares since the wedges that redirect light through NIRCam's coronagraphic masks and neutral density squares are co-located with the Lyot stop pupil masks.
-In addition to lowering the transmission by a factor of 0.19\%, the Lyot stops spread out the PSF as compared to direct imaging.
+In addition to lowering the transmission by a factor of 19\%, the Lyot stops spread out the PSF as compared to direct imaging.
 Figure \ref{fig:psfComparison} shows example PSFs calculated with \texttt{webbpsf} \citep{perrin2012webbpsf}.

### 2017-07-05 ms.tex
re-ordered the author list to push George higher up
added some details about the shorter flux ladder using P330-E.

@@
 
-\author{E. Schlawin, Jarron Leisenring, M. Rieke, G. Rieke, K. Misselt}
+\author{E. Schlawin, G. Rieke, Jarron Leisenring, M. Rieke, K. Misselt}
 \affil{Steward Observatory, Tucson AZ 85721}
@@
 Five of these spheres were ejected during the cryogenic lifetime of MSX's SPIRIT III sensor.
-These spheres were observed for about 1/3 of an orbital period and then at least one star was observed in the same data collection event.
+These spheres were observed for about 1/3 of an orbital period and then at least one star was observed in the same data collection event as the reference sphere.
 
@@
 \centering
-\includegraphics[width=.55\columnwidth]{flux_ladder.pdf}
+\includegraphics[width=.8\columnwidth]{flux_ladder.pdf}
 \caption{Schematic sensitivity ladder going from an MSX standard (with a sub-array, neutral density filter observation) to a faint JWST standard (with a full array, full throughput observation).
-An intermediate standard can be used to check the NIRCam transfers against other observatories and instruments.}\label{fig:sensitivityLadder}
+Each observation step is labeled in the bottom corner of each image schematic.
+An intermediate standard (shown with green connecting arrows) can be used to check the NIRCam transfers against other observatories and instruments.}\label{fig:sensitivityLadder}
 \end{figure}
@@
 
-\subsection{Using intermediate Standards to Check the Flux Ladder}
+\subsection{Using Intermediate Standards to Check the Flux Ladder}
 
@@
 
-However, if sufficient time is available for calibration, it is possible to convert from an MSX standard to full frame imaging in a narrowband mode in one step by using an intermediate JWST standard.
-To begin, the F212N filter could be selected in the filter wheel to observe a bright MSX star with the neutral density filter and Lyot pupil mask.
+However, if sufficient time is available for calibration, it is possible to convert from an MSX standard to full frame imaging in a narrowband mode in 3 steps by using an intermediate JWST standard.
+This shorter ladder is illustrated in Figure \ref{fig:sensitivityLadderP330E}.
+To begin, the F212N filter would be selected in the filter wheel to observe a bright MSX star with the neutral density filter and Lyot pupil mask.
 The same setup could be arranged on P330-E and observed for 7.5 hours to achieve a SNR=200.
@@
 The advantage with this single transfer from an MSX standard to a full frame P330-E image is that it fewer steps than the ladder described above.
-The disadvantage is that there would be a large disparity in detector well depth between the vertical and horizontal steps on this ladder.
+The disadvantage is that there would be a large disparity in detector well depth between the steps on this ladder.
 If flux calibration time is available, this alternative flux ladder or simply the ``offshoot'' would serve as a check on the conversion from faint to bright targets.
+
+\begin{figure}[!t]
+\centering
+\includegraphics[width=.32\columnwidth]{flux_ladder_p330e.pdf}
+\caption{Schematic of an alternative sensitivity ladder to Figure \ref{fig:sensitivityLadder}.
+This ladder would use the intermediate-brightness JWST standard P330-E (G2~V type) to transfer from an MSX star to full frame imaging in a narrowband filter.
+The observing time needed for step 2 is considerable, but if allocated (7.5 hr to get SNR=200), this provides a way to calibrate full frame imaging with fewer transfers than the 6 step method above.
+The disadvantage of this method is that each step involves a large disparity in well depths.}\label{fig:sensitivityLadderP330E}
+\end{figure}
 

### 2017-07-05 ms.tex
added example stars for the flux calibration ladder.

@@
 1		& MSX Calibrator\tablenotemark{a}	& A1 V to M0 III		& -3 to 0.1		& On	&	64$\times$64	& F430M &  0.2 & -4.0 \\
-2		& Bright JWST Calibrator			& G2 V			& 6.5	  		& On &	64$\times$64	& F430M &  220 & -4.0 \\
+2		& Bright JWST Calibrator			& A0 V, G2 V		& 6.5	  		& On &	64$\times$64	& F430M &  220 & -4.0 \\
 3		& Bright JWST Calibrator			& G2 V			& 6.5  		& Off &	64$\times$64	& F430M &  0.1 & 6.2 \\
@@
 \vspace{0.05in}
+\end{table}
+
+\begin{table}[!b]
+\centering
+\caption{Example Stars for Each Calibrator Step.}\label{tab:stepStars}
+\begin{tabular}{lrrr}
+\hline \hline
+Step	(s)	& Source						& Spectral Type	& $K_\mathrm{src}$\tablenotemark{a}	\\
+\hline \hline
+1		& $\alpha$ Cen (Sirius)			& A1 V 			& -1.35		\\
+1		& $\gamma$ Dra (Eltanin)			& K5 III 			& -1.35		\\
+1		& $\alpha$ Lyr (Vega)			& A0 V 			& 0.13		\\
+2 - 3		& HD 37962					& G2 V			& 6.27	  	\\
+2 - 3		& HD 38949					& G1 V			& 6.44	  	\\
+4 - 6		& 07:38:17.1 +21:36:22 (NGC 2420)	& G2 V			& 15.6 		\\
+\hline
+\end{tabular}
+\tablenotetext{a}{NOTE, these magnitudes from Simbad may have up to 5\% systematics for steps 1-3..}
+\vspace{0.05in} f
 \end{table}
@@
 The observing time needed for step 2 is considerable, but if allocated (7.5 hr to get SNR=200), this provides a way to calibrate full frame imaging with fewer transfers than the 6 step method above.
-The disadvantage of this method is that each step involves a large disparity in well depths.}\label{fig:sensitivityLadderP330E}
+The disadvantage of this method is that each step involves a large disparity in well depths.
+The steps are labeled B1 through B3 do distinguish between these and steps 1-6 in Figure \ref{fig:sensitivityLadder}.}\label{fig:sensitivityLadderP330E}
 \end{figure}

### 2017-10-04 ms.tex
added some photometry notes and cluster physical distances.

@@
 The longer wavelength wide band filters (F200W, F277W, F356W, and F444W) will not saturate for a true distance modulus larger than 11.8.
-If one assumes an extinction of E(B-V) = 0.05 and a Galactic average extinction law \citep{cardelli1989}, the visual distance modulus $(m- M)_V$ should be an additional 0.14 mag.
-Thus, to calibrate all wide band filters in full frame mode, the visual distance modulus $(m- M)_V$ should be larger than 11.94.
+If one assumes an extinction of E(B-V) = 0.05 and a Galactic average extinction law \citep{cardelli1989}, the visual distance modulus $(m- M)_V$ should be an additional 0.15 mag.
+Thus, to calibrate all wide band filters in full frame mode, the visual distance modulus $(m- M)_V$ should be larger than 11.95.
 \item {\bf Metallicity} Ideally, the cluster should have near-solar metallicity so that the solar mass stars have a luminosity near 1 $L_\sun$ and a G2~V type spectrum.
@@
 \caption{Cluster Parameters}\label{tab:clusterProp}
-\begin{tabular}{lrrrc}
+\begin{tabular}{lrrrrc}
 \hline \hline
-Cluster   					&  E(B-V) 			& Distance Mod 	& [Fe/H] 			& Age \\
-          					&     				&    (m - M)$_V$	& 	dex 			& Gyr \\
+Cluster   					&  E(B-V) 			& Distance Mod 	& [Fe/H] 			& Age 		& Distance\\
+          					&     				&    (m - M)$_V$	& 	dex 			& Gyr 		& kpc	\\
 \hline \hline
-NGC 2420\tablenotemark{a}	& 0.04 $\pm$0.03	&  11.88 $\pm$ 0.27	& -0.05 $\pm$ 0.03	& 3 $\pm$ 1 \\
-NGC 2506\tablenotemark{b}	& 0.058 $\pm$ 0.001	&  12.75 $\pm$ 0.10 	& -0.32 $\pm$ 0.03	& 1.85 $\pm$ 0.05 \\
-NGC 6811\tablenotemark{c}	& 0.05 $\pm$0.02	& 10.29 $\pm$ 0.14	& 0.04 $\pm$ 0.01 	& 1.0 $\pm$ 0.1 \\
+NGC 2420\tablenotemark{b}	& 0.04 $\pm$0.03	&  11.88 $\pm$ 0.27	& -0.05 $\pm$ 0.03	& 3 $\pm$ 1 	& 2.2 $\pm$ 0.3 \\
+NGC 2506\tablenotemark{c}	& 0.058 $\pm$ 0.001	&  12.75 $\pm$ 0.10 	& -0.32 $\pm$ 0.03	& 1.85 $\pm$ 0.05 & 3.3 $\pm$ 0.2 \\
+NGC 6811\tablenotemark{d}	& 0.05 $\pm$0.02	& 10.29 $\pm$ 0.14	& 0.04 $\pm$ 0.01 	& 1.0 $\pm$ 0.1 & 1.1 $\pm$ 0.1 \\
 \hline
@@
 The size affects the number of DHS that can be included, so the noise in the DHS spectra over 1.1 -- 1.9$\mu$m at the given saturation limit for a 1 hour transit is shown in column 4 at native R $\sim$ \DHSresApprox\ resolution.}\label{tab:SatSNRsubA}
-\tablenotetext{a}{NGC 2420 parameters from \citet{pancino2010chem2420}.}
-\tablenotetext{b}{NGC 2506 parameters from \citet{anthonytwarog2016wiyn2506}. Error bars are formal standard errors of the mean, not necessarily capturing systematics.}
-\tablenotetext{c}{NGC 6811 parameters from \citet{molendaz2016spec6811}}
+\tablenotetext{a}{Distance calculated by taking the visual distance modulus $(m-M)_V$ and subtracting the expected extinction for a Galactic average extinction law \citep{cardelli1989}.}
+\tablenotetext{b}{NGC 2420 parameters from \citet{pancino2010chem2420}.}
+\tablenotetext{c}{NGC 2506 parameters from \citet{anthonytwarog2016wiyn2506}. Error bars are formal standard errors of the mean, not necessarily capturing systematics.}
+\tablenotetext{d}{NGC 6811 parameters from \citet{molendaz2016spec6811}}
 \end{table}
@@
 Either a well-characterized white dwarf spectrum of a known standard or a faint G2 V standard from an open cluster would be good models for this transfer of filters.
+
+Table \ref{tab:conversionStep} shows the saturation limits for each mode as well as the
 
@@
 
+\appendix
+
+\section{Relative Spectral Response Passbands}
+
+There are 2 kinds of spectral response that can be used to perform synthetic photometr.
+Here we note the difference between then.
+
+\subsection{QE-Based Passband}
+The QE-based passbands can be used to calculate synthetic photometry.
+
+\begin{equation}
+T_{int} = \int{f_\lambda \lambda R_{QE} d\lambda} 
+\end{equation}
+where $f_\lambda$ is the specific flux, $\lambda$ is wavelength and $R_{QE}$ is the quantum-efficiency based passband \citep[e.g][]{bessel2000fundamentalPhot}.
+
+\subsection{Photon Based Passbands}
+The photon-counting RSRs are designed to be integrated directly over stellar spectra.
+\begin{equation}
+T_{int} = \int{f_\lambda R_{\lambda} d\lambda} 
+\end{equation}
+where $R_{\lambda}$ is the photon-counting passband \citep[e.g][]{cohen2003}.
+
+\section{Additional Notes}
+
+Christopher W - points out we should look at the APOGEE data. I see there's overlap for NGC 2420.
+
 %% The reference list follows the main body and any appendices.

### 2018-01-23 ms.tex
Per Ralph Bohlin's comments, I added a table of MSX stars for reference.

@@
 	\includegraphics[width=0.5\textwidth]{sources_ngc2420.png}
-	\label{fig:cmdNGC6811}
+	\label{fig:cmdNGC2420}
 	}
@@
 The primary JWST standards for absolute calibration have been tied to directly calibrated photometric sources through transfers, such as with HST's STIS instrument.
-As an independent check on those transfers, NIRCam can be used to observe directly calibrated stars (such as the midcourse space experiment (MSX) calibrators \citep{price2004msxCal}) and step down in brightness to faint standards used in JWST calibration.
+As an independent check on those transfers, NIRCam can be used to observe directly calibrated stars (such as the midcourse space experiment (MSX) calibrators \citep{price2004msxCal}, listed in Table \ref{tab:msxStars}) and step down in brightness to faint standards used in JWST calibration.
 The MSX ejected 1 cm radius reference spheres made of 6061-T6 aluminum alloy coated with Martin Black, for which the thermal and emissive properties were well understood.
@@
 \tablenotetext{a}{NOTE, these magnitudes from Simbad may have up to 5\% systematics for steps 1-3..}
-\vspace{0.05in} f
+\vspace{0.05in}
+\end{table}
+
+\begin{table}
+\centering
+\caption{MSX Calibrator Stars and Fluxes.}\label{tab:msxStars}
+\begin{tabular}{cccccc}
+Star Name & Common Name & Spectral Type & K mag\tablenotemark{a} & B$_1$  & B$_2$ \\
+      & &  & & 10$^{-15}$ W/cm$^{-2}$ & 10$^{-15}$ W/cm$^{-2}$ \\
+\hline \hline
+$\alpha$ Boo & Arcturus & K1.5 III & -2.91 & 56.0 $\pm$ 0.4 & 87.3 $\pm$ 0.5 \\
+$\alpha$ Tau & Aldebaran & K5+ III & -3.04 & 47.6 $\pm$ 0.3 & 74.2 $\pm$ 0.4 \\
+$\alpha$ Lyr & Vega & A0 V & 0.13 & 3.33 $\pm$ 0.04 & 5.34 $\pm$ 0.05 \\
+$\beta$ Gem & Pollux & K0 III & -1.11 & 9.55 $\pm$ 0.08 & 15.0 $\pm$ 0.1 \\
+$\gamma$ Dra & Eltanin & K5 III & -1.35 & 11.2 $\pm$ 0.1 & 17.3 $\pm$ 0.2 \\
+$\gamma$ Cru & Gacrux & M3.4 III & -3.12 & 63.1 $\pm$ 0.6 & 98.2 $\pm$ 0.9 \\
+$\beta$ And & Mirach & M0 III & -1.87 & 18.3 $\pm$ 0.3 & 30.0 $\pm$ 0.5 \\
+$\alpha$ Cma & Sirius & A1 V & -1.35 & 11.8 $\pm$ 0.1\tablenotemark{b}& 18.9 $\pm$ 0.2\tablenotemark{b} \\
+\end{tabular}
+\tablenotetext{a}{K Magnitudes from Simbad}
+\tablenotetext{b}{Scaling the Vega fluxes by the assigned -1.36 Vega Magnitude of Sirius using Table 3 in \citet{price2004msxCal}.}
 \end{table}
@@
 
-Table \ref{tab:conversionStep} shows the saturation limits for each mode as well as the
+Table \ref{tab:conversionSteps} shows the saturation limits for each mode as well as the time needed to achieve a SNR of 200.
 
@@
 This means that the entire sample of stars from \citet{price2004msxCal} are observable in this coronagraphic neutral density mode.
+There are some difficulties and potential pitfalls when attempting a multi-step ladder, so we describe these below.
+
+\subsubsection{Implementation}
+The APT science nor engineering template permit dithered subarray imaging with a 64$\times$64 subarray through a neutral density filter.
+This prohibits executing Step 1 in Cycle 1 observing.
+It is possible that in Cycle 2, more modes will be implemented including dithered subarray 64$\times$64 subarray imaging with a neutral density filter in place.
+
+\subsubsection{Difficulty in Obtaining Accuracy}
+The goal of the flux calibration effort is to achieve 1\% absolute flux calibration so the it is important to keep this mind.
+The sum total error of all the steps of the NIRCam flux ladder must contribute less than 1\% so if the 6 errors are independent, the each must incur less than 0.4\% error.
+In the pessimistic case that the errors are correlated, each step should have less than 0.17\%.
+So, a signal to noise of 600 would be desired for each step on the ladder.
 
@@
 
-\subsubsection{Clocking Issues for Small Subarrays}
+\subsubsection{Clocking Issues for Small Subarrays - now resolved}
 
-Marcia and Jarron have brought up this issue in a NIRCam STScI+External team telecon on on April 6, 2017.
+Marcia and Jarron previously brought up up this issue in a NIRCam STScI+External team telecon on on April 6, 2017.
 Jarron explained further on April 24, 2017.
-This is a known bug in the ASIC micro-code that can affect the frame times of small subarrays.
+This was a known bug in the ASIC micro-code that can affect the frame times of small subarrays.
 The bug creates extra line overheads on small subarrays.
@@
 Tony Magoncelli has found a way to deterministically predict when these extra frame times will occur.
-However, JWST will not produce enough data in flight to deterministically predict when the extra frame times occur so you'd have to average many frames together.
+However, JWST did not produce enough data in flight to deterministically predict when the extra frame times occur so you'd have to average many frames together.
 For a 64$\times$ 64 subarray, there are almost always 2 line overheads.
@@
 Given that 64$\times$64 frame time is only 0.05 s long, you could easily include hundreds of frames to average out the frame time issue with almost no change in efficiency since JWST acquisition, exposure and dithering overheads would be a much larger fraction of the time.
-I would estimate this would have less than 0.01\% of an effect on flux calibration.
+Thus, this would have less than 0.01\% of an effect on flux calibration.
+Fortunately, the ASIC microcode was updated to fix this problem so there is no deterministic predictable timing for all subarrays, which was confirmed by Jarron Leisenring.
 

### 2018-04-20 ms.tex
added a few notes about the flux ladder & APT templates.

@@
 If one assumes an extinction of E(B-V) = 0.05 and a Galactic average extinction law \citep{cardelli1989}, the visual distance modulus $(m- M)_V$ should be an additional 0.15 mag.
-Thus, to calibrate all wide band filters in full frame mode, the visual distance modulus $(m- M)_V$ should be larger than 11.95.
+Thus, to calibrate all wide band filters longer than F200W in full frame mode, the visual distance modulus $(m- M)_V$ should be larger than 11.95.
 \item {\bf Metallicity} Ideally, the cluster should have near-solar metallicity so that the solar mass stars have a luminosity near 1 $L_\sun$ and a G2~V type spectrum.
@@
 
-\section{Transferring to Directly Calibrated Sources - the NIRCam Flux Ladder}
+\section{Transferring to Directly Calibrated Sources - the NIRCam Flux Ladder\footnote{This idea has been discussed, but cannot be executed until Cycle 2 due to limitations of observing templates}}
 
@@
 
-\subsubsection{Implementation}
+\subsubsection{Implementation}\label{sec:ImpIssue}
 The APT science nor engineering template permit dithered subarray imaging with a 64$\times$64 subarray through a neutral density filter.

### 2019-04-11 ms.tex
added color-magnitude diagrams with near-G2 Vs labeled.
started modifying the title to focus on faint G2V solar analogs
got rid of flux ladder stuff and made edits to first few pages.

--- 2017-10-04 ms.tex
@@
 
-\shorttitle{NIRCam Flux Calibration}
+\shorttitle{Distant Suns}
 \shortauthors{Schlawin et al.}
@@
 
-\title{NIRCam Faint and Bright Flux Calibration Plan}
+\title{Distant Suns for JWST Flux Calibration}
 
@@
 
-\author{E. Schlawin, G. Rieke, Jarron Leisenring, M. Rieke, K. Misselt}
+\author{E. Schlawin, G. Rieke, Christopher Willmer, Jarron Leisenring, M. Rieke, K. Misselt}
 \affil{Steward Observatory, Tucson AZ 85721}
@@
 
-\altaffiltext{1}{Hubble Postdoctoral Fellow}
+%\altaffiltext{1}{Hubble Postdoctoral Fellow}
 
@@
 One area where accurate flux calibration is especially important is dark energy science, which makes use of type Ia supernovae as standard candles.
-Absolute fluxes are especially important for improving type Ia supernova luminosity distances and thus the expansion history of the Universe.
+Absolute fluxes are especially important for improving type Ia supernova luminosity distances and thus the expansion history of the Universe \citep[e.g.][]{narayan2016wdnetwork,betoule2014cosmologySN}.
+For exoplanet host stars in the era of Gaia distances, absolutely calibrated photometry is used to make precision measurements of stellar radii, which in turn give high precision planet radii.
+For exoplanet host stars in the era of Gaia distances, absolutely calibrated photometry is used to make precision measurements of stellar radii, which in turn give high precision planet radii \citep[e.g.][]{stassun2017gaiaRadiiMasses}.
 JWST will have no standard calibration sources onboard so all calibration must be performed with astronomical sources.
@@
 Many of these spectra will saturate the NIRCam detectors when used in full frame (shown as the middle parts of the black ``error bars'') for wide-band filters.
+The 
 Furthermore, there may be systematic errors when observing faint targets and low detector well depths.
@@
 If we require that a solar mass star have $T_{\rm eff}$ = 5780 +/- 100 K, the cluster would have to be between 0.3 Gyr and 10 Gyr using Dartmouth evolutionary models \citep{dotter2008dartmouth}.
-Furthermore, the age should be $\lesssim$7 Gyr to avoid main sequence turnoff of near-solar stars.
+Furthermore, the age should be $\lesssim$7 Gyr to avoid main sequence turnoff of F-type stars that would have similar colors to solar analogs.
 \item {\bf Extinction} Extinction should be as small as possible to minimize the effects of extinction correction to photometry. Of the clusters found, E(B-V) $\lesssim 0.1$.
 \item {\bf Distance Modulus} The cluster must be distant enough to not saturate NIRCam's wide filters in full frame mode.
-The most easily saturated filter for G stars is the F090W, which corresponds to a G2~V star of 15.9 in the $K$ band.
+The most easily saturated wide band filter for G stars is the F090W, which corresponds to a G2~V star of 15.9 in the $K$ band.
+While the F150W2 ``double-wide'' filter is more easily saturated than F090W, this is filter is unlikely to be used on faint Galaxies because (someone from deep field prog remind me?).
 This means the true distance modulus $(m - M)_0$ should be 12.6 for a solar absolute K=3.28 \citep{binney1998book}.
@@
 
-With all these considerations in play, we selected NGC 2420 as the best fit for the multiple criteria.
-The only parameter that is not satisfied is the distance modulus, so additional sources or conversions are needed for the F070W, F090W, F115W and F150W filters.
+With all these considerations in play, we selected NGC 2420 and NGC 2506 as the best fit for the multiple criteria.
+The only parameter that is not satisfied by NGC 2420 is the distance modulus, so additional sources or conversions are needed for the F070W, F090W, F115W and F150W filters.
 At the time NGC 2420 was selected, the JWST throughputs were smaller than the measured values so it saturated fewer filters.
@@
 The subarray to full frame conversion can be checked with medium band filters.
-NGC 2506 and NGC 6811 are next-best fits and have somewhat complimentary visibility windows, shown in Figure \ref{fig:clusterVis}. NGC 2420 and NGC 6811 have -0.05 $\le$ [Fe/H] $\le$ 0.04.
+NGC 2506 is the next-best fits and have somewhat complimentary visibility windows, shown in Figure \ref{fig:clusterVis}. NGC 2420 and NGC 6811 have -0.05 $\le$ [Fe/H] $\le$ 0.04.
 NGC 2506, is metal poor at [Fe/H]=-0.32, so corrections must be made for changes to G2 V spectra due to metallicity.
@@
 
-\clearpage
-
-\section{Transferring to Directly Calibrated Sources - the NIRCam Flux Ladder}
-
-The primary JWST standards for absolute calibration have been tied to directly calibrated photometric sources through transfers, such as with HST's STIS instrument.
-As an independent check on those transfers, NIRCam can be used to observe directly calibrated stars (such as the midcourse space experiment (MSX) calibrators \citep{price2004msxCal}) and step down in brightness to faint standards used in JWST calibration.
-The MSX ejected 1 cm radius reference spheres made of 6061-T6 aluminum alloy coated with Martin Black, for which the thermal and emissive properties were well understood.
-Five of these spheres were ejected during the cryogenic lifetime of MSX's SPIRIT III sensor.
-These spheres were observed for about 1/3 of an orbital period and then at least one star was observed in the same data collection event as the reference sphere.
-
-\begin{figure}[!t]
+\begin{figure*}[!t]
 \centering
-\includegraphics[width=.8\columnwidth]{flux_ladder.pdf}
-\caption{Schematic sensitivity ladder going from an MSX standard (with a sub-array, neutral density filter observation) to a faint JWST standard (with a full array, full throughput observation).
-Each observation step is labeled in the bottom corner of each image schematic.
-An intermediate standard (shown with green connecting arrows) can be used to check the NIRCam transfers against other observatories and instruments.}\label{fig:sensitivityLadder}
-\end{figure}
-
-\begin{table}[!b]
-\centering
-\caption{Conversion from Directly Calibrated Source to Deep Calibrator}\label{tab:conversionSteps}
-\begin{tabular}{lrrrrrrrr}
-\hline \hline
-Step		& Source						& Spectral Type	& $K_\mathrm{src}$		& ND Square		& Subarray	& Filter & t$_\mathrm{exp} (s) $ &$K_\mathrm{sat}$\\
-\hline \hline
-1		& MSX Calibrator\tablenotemark{a}	& A1 V to M0 III		& -3 to 0.1		& On	&	64$\times$64	& F430M &  0.2 & -4.0 \\
-2		& Bright JWST Calibrator			& A0 V, G2 V		& 6.5	  		& On &	64$\times$64	& F430M &  220 & -4.0 \\
-3		& Bright JWST Calibrator			& G2 V			& 6.5  		& Off &	64$\times$64	& F430M &  0.1 & 6.2 \\
-4		& Faint JWST Calibrator			& G2 V			& 16 			& Off &	64$\times$64	& F430M &  94 & 6.2 \\
-5		& Faint JWST Calibrator			& G2 V			& 16 			& Off &	Full Frame	& F430M &  107 & 12 \\
-6		& Faint JWST Calibrator			& G2 V			& 16 			& Off &	Full Frame  	& F444W &  21 & 13.7 \\
-\hline
-\end{tabular}
-\tablenotetext{a}{Any directly calibrated bright source such as the MSX calibrators \citep{price2004msxCal}, (which include Sirius and Vega) or alternatively $\alpha$ Cen A.
-The exposure times given are the times needed to reach at least SNR=200, rounded up to the next group up the ramp.
-The saturation limit is at 80\% well depth for 2 non-destructive reads up the ramp following a reset.}
-\vspace{0.05in}
-\end{table}
-
-\begin{table}[!b]
-\centering
-\caption{Example Stars for Each Calibrator Step.}\label{tab:stepStars}
-\begin{tabular}{lrrr}
-\hline \hline
-Step	(s)	& Source						& Spectral Type	& $K_\mathrm{src}$\tablenotemark{a}	\\
-\hline \hline
-1		& $\alpha$ Cen (Sirius)			& A1 V 			& -1.35		\\
-1		& $\gamma$ Dra (Eltanin)			& K5 III 			& -1.35		\\
-1		& $\alpha$ Lyr (Vega)			& A0 V 			& 0.13		\\
-2 - 3		& HD 37962					& G2 V			& 6.27	  	\\
-2 - 3		& HD 38949					& G1 V			& 6.44	  	\\
-4 - 6		& 07:38:17.1 +21:36:22 (NGC 2420)	& G2 V			& 15.6 		\\
-\hline
-\end{tabular}
-\tablenotetext{a}{NOTE, these magnitudes from Simbad may have up to 5\% systematics for steps 1-3..}
-\vspace{0.05in} f
-\end{table}
-
-Figure \ref{fig:sensitivityLadder} shows a schematic of the steps beginning with MSX calibrators (as bright as $K \sim -3$) to faint JWST standards ($K \sim 16$).
-The methodology of the flux ladder is that only one change is made per step - either an instrument re-configuration is made on the same source (a horizontal move) or a new source is measured with the same instrument configuration (a vertical move).
-As listed in Table \ref{tab:conversionSteps}, the direct calibrator would be observed in a neutral density square, subarray and medium band filter while using the coronagraphic pupil.
-For the next step, this same instrument configuration will be used on a bright JWST standard, such as HD 37962 (G2 V, $K$=6.27).
-Getting sufficient signal to noise (S/N$\gtrsim$200) on an intermediate JWST calibrator such as P-330E (G2 V, $K$=11.4) with the neutral density square in place would require long integration times so the bright calibrators are preferred for steps 2 and 3.
-
-This bright JWST standard would be used to transfer from the ND filter with a coronagraphic pupil mask to direct imaging.
-This conversion step can independently be checked against other instruments' measurements of the bright JWST calibrator, such as by STIS with HST.
-The next step would be to use the same direct image configuration and subarray size to observe a faint JWST calibrator around $K \sim$15.
-S/N ratios of 200 can be achieved in 94 seconds in this mode.
-This calibrator star would now be observable in full frame mode without saturation so the next step would be a conversion from subarray to full frame on the same source.
-Since the solar analog flux standards identified in this program are in a cluster, there are many sources available for photometry.
-It may be useful to make additional measurements to confirm the subarray to full frame conversion using a concentration of stars in a cluster over a range in magnitude.
-To calibrate the wide band filters, such as F444W, one final step would be needed to go from the medium to wide band photometry using a model for the star.
-Either a well-characterized white dwarf spectrum of a known standard or a faint G2 V standard from an open cluster would be good models for this transfer of filters.
-
-Table \ref{tab:conversionStep} shows the saturation limits for each mode as well as the
-
-\subsection{Using Intermediate Standards to Check the Flux Ladder}
-
-Figure \ref{fig:sensitivityLadder} shows that an intermediate JWST standard such as P-330 E can be used to check transfers and detector linearity corrections.
-The solar analog P330-E is a commonly used standard because of its similarity to the sun.
-This step would not be an essential ``rung'' in the NIRCam flux ladder (since it involves more steps) but a useful check on other transfers.
-
-However, if sufficient time is available for calibration, it is possible to convert from an MSX standard to full frame imaging in a narrowband mode in 3 steps by using an intermediate JWST standard.
-This shorter ladder is illustrated in Figure \ref{fig:sensitivityLadderP330E}.
-To begin, the F212N filter would be selected in the filter wheel to observe a bright MSX star with the neutral density filter and Lyot pupil mask.
-The same setup could be arranged on P330-E and observed for 7.5 hours to achieve a SNR=200.
-If the F212N filter is used to image P330-E with a full frame direct imaging mode, it is just barely is observable with 2 groups in RAPID mode before reaching full well saturation.
-The F212N filter is chosen since there are few stellar absorption lines in this filter.
-The advantage with this single transfer from an MSX standard to a full frame P330-E image is that it fewer steps than the ladder described above.
-The disadvantage is that there would be a large disparity in detector well depth between the steps on this ladder.
-If flux calibration time is available, this alternative flux ladder or simply the ``offshoot'' would serve as a check on the conversion from faint to bright targets.
-
-\begin{figure}[!t]
-\centering
-\includegraphics[width=.32\columnwidth]{flux_ladder_p330e.pdf}
-\caption{Schematic of an alternative sensitivity ladder to Figure \ref{fig:sensitivityLadder}.
-This ladder would use the intermediate-brightness JWST standard P330-E (G2~V type) to transfer from an MSX star to full frame imaging in a narrowband filter.
-The observing time needed for step 2 is considerable, but if allocated (7.5 hr to get SNR=200), this provides a way to calibrate full frame imaging with fewer transfers than the 6 step method above.
-The disadvantage of this method is that each step involves a large disparity in well depths.
-The steps are labeled B1 through B3 do distinguish between these and steps 1-6 in Figure \ref{fig:sensitivityLadder}.}\label{fig:sensitivityLadderP330E}
-\end{figure}
-
-\subsection{Ways to Observe Bright Stars}\label{sec:brightStarMode}
-
-There are several ways to improve saturation limits with NIRCam over direct imaging:
-\begin{itemize}
-\item \textbf{Lyot Stop} Cut down the aperture size with a Lyot stop. These have 19\% throughput (1.8 mags). Additionally, this broadens the PSF - see Figure \ref{fig:psfComparison}.
-The broadening spreads light out by a similar factor (contributing 1.8 mags to saturation limits) for a total of 3.5 mags.
-\item \textbf{Neutral Density Square} The neutral density filters have an attenuation of 10$^3$ or 7.5 mags.
-A color correction would have to be applied for the neutral density filter (since it is wavelength dependent) when transferring to an un-occulted region.
-Additionally, the Lyot stop must be in place to use the neutral density filter so the total improvement on saturation limits is 11 mags over direct imaging.
-Care must be taken with dithering to ensure that non-uniform optical depth of the neutral density filter doesn't affect the photometry.
-\item \textbf{Grisms} For long wavelength NIRCam observations ($2.4~\mu$m$ > \lambda < 5~\mu$m), one can use a grism to spread out the light.
-This mode still has a saturation limit of $K$=4.6 to 3.5 for the F322W2  filter and 2048$\times$64 subarray \citep{greene2016wfss}, which does not reach to the MSX standards.
-This could be potentially combined with the coronagraphic pupil, but this combination has not been tested or explored in detail.
-One could potentially observe small pieces of the spectrum at a time with a subarray that are all combined to create a spectrum, but this would add time and may be difficult to implement.
-\item \textbf{DHS} For short wavelength NIRCam spectra ($1.0~\mu$m$ > \lambda < 2.0~\mu$m), one can use the Dispersed Hartmann Sensor.
-The dispersed Hartmann Sensor (DHS) reduces the pupil throughput and spreads the light out to reach saturation limits of $K$=0.2 to 1.5 depending on spectral type \citep{schlawin2017dhs} for a 2048$\times$64 subarray.
-This is not bright enough to observe the MSX calibrators.
-As with the long wavelength grisms, one would have to read small subarrays (e.g. 64$\times$64) to get to brighter limits.
-If one stitched together a spectrum from these subarrays along the spectrum, this could theoretically be used on all MSX stars.
-However, as with the grism mode above, there would be significant changes and additions to the flight software to implement a mode that would build a spectrum out of 32 different subarrays.
-\item \textbf{Extra Small Subarrays} There will be an engineering jitter monitoring test with an 8 $\times$ 8 subarray.
-There may be complications with calculating accurate integration times in this mode because any uncertainties affecting a frame time could be a significant fraction of the $\sim$ 2 ms frame time.
-The background annulus would be limited for such small subarrays.
-\item \textbf{Weak Lens} The Weak Lenses spread light out over many pixels which can be helpful for bright stars.
-However, one needs to read out larger sized subarrays to encompass the entire hexagonal PSF so this somewhat cancels out the effect of spreading the light out over many pixels.
-For a very narrowband filter such as F212N, the K-band saturation limit for a weak lens observation with a 128$\times$128 subarray is 0.9 mag (Vega mag) for a G2V star, which does not quite reach the MSX calibrators.
-\end{itemize}
-
-Of the many options here, the most feasible method is the neutral density square with the Lyot Coronagraphic pupil mask.
-Sensitivity and saturation limits make use of \texttt{pysynphot} \citep{lim2015pysynphot} with either Phoenix stellar models \citep{allard2012phoenix} or \citet{castelli2004models} models.
-
-\subsection{Observing MSX Stars}
-
-Observing the MSX flux standards (which are bright naked eye stars) with JWST's NIRCam can be achieved with a combination of medium-band filters, small subarray sizes, a Lyot stop pupil mask (19\% transmission) and a neutral density (ND) filter.
-Using \texttt{webbpsf} and the throughputs in a NIRCam program called \texttt{pynrc}\footnote{https://github.com/JarronL/pynrc.git}, we calculate the saturation limits for 2 groups in RAPID mode and find a K-magnitude of saturation of $-$4.0 for an A1 V type star (Sirius is A1 V with K=$-$1.35) and $-$3.7 for an M3 III (Gacrux is $-$3.12).
-This means that the entire sample of stars from \citet{price2004msxCal} are observable in this coronagraphic neutral density mode.
-
-\subsubsection{Complications with PSF}
-A Lyot pupil mask must be used when imaging through the neutral density squares since the wedges that redirect light through NIRCam's coronagraphic masks and neutral density squares are co-located with the Lyot stop pupil masks.
-In addition to lowering the transmission by a factor of 19\%, the Lyot stops spread out the PSF as compared to direct imaging.
-Figure \ref{fig:psfComparison} shows example PSFs calculated with \texttt{webbpsf} \citep{perrin2012webbpsf}.
-Figure \ref{fig:psfDirect} shows the direct image PSF versus the the coronagraphic PSF (Figure \ref{fig:psfND}), both normalized to the peak pixel.
-
-When using the ND filter and Lyot stop, the aperture photometry must account for the large secondary peaks of the PSF.
-This can be accomplished with a large aperture covering all the secondary peaks assuming that the background levels are low and that there are no nearby sources.
-Alternatively, one could extract the flux from the core of the PSF.
-
-\begin{figure*}
-\centering
-\subfloat[Direct Imaging PSF]{
-	\includegraphics[width=0.45\textwidth]{psf_direct.pdf}
-	\label{fig:psfDirect}
+\subfloat[NGC 2420]{
+	\includegraphics[width=0.5\textwidth]{colormag_NGC_2420_near_G2_V.pdf}
+	\label{fig:cmdNGC2420nearG2V}
 	}
 \subfloat[NGC 2506]{
-	\includegraphics[width=0.45\textwidth]{psf_ND.pdf}
-	\label{fig:psfND}
+	\includegraphics[width=0.5\textwidth]{colormag_NGC_2506_near_G2_V.pdf}
+	\label{fig:cmdNGC2506nearG2V}
 	}
-	\caption{The \texttt{webbpsf} direct imaging PSF and coronagraphic PSF which is modified by the Lyot stop.
-Both images are normalized by the peak pixel value and have arbitrary array positions but the same height and width.
-Aperture photometry of the sources imaged through the coronograph will have to use a large aperture encompassing the 6 outer peaks or just use the central peak(s) and apply careful background subtraction.
-Both PSFs were calculated for NIRCam's long wavelength channel with a F430M filter.\vspace{0.05in}}
-	\label{fig:psfComparison}
+\\
+\subfloat[NGC 6811]{
+	\includegraphics[width=0.5\textwidth]{colormag_NGC_6811_near_G2_V.pdf}
+	\label{fig:cmdNGC6811nearG2V}
+	}
+	\caption{Color-magnitudes of the three clusters with the near-solar stars identified from spectra.
+	}
+	\label{fig:cmdPSnearG2V}
 \end{figure*}
 
-\subsubsection{Complications with Flat Fielding}
-The ND filters are not uniform spatially.
-Correcting for any pinholes or blemishes in the ND square surface will likely dominate the error budget for the ND square absolute calibration.
-Positioning the sources consistently on the same pixel locations and using the same dither patterns will help with these errors.
-The dithers can be used to check the surface irregularities.
-
-\subsubsection{Clocking Issues for Small Subarrays}
-
-Marcia and Jarron have brought up this issue in a NIRCam STScI+External team telecon on on April 6, 2017.
-Jarron explained further on April 24, 2017.
-This is a known bug in the ASIC micro-code that can affect the frame times of small subarrays.
-The bug creates extra line overheads on small subarrays.
-For example, for a 32$\times$32 subarray, there are sometimes 2 line overheads and sometimes 3 line overheads about $\sim$40/60 \% of the time.
-Tony Magoncelli has found a way to deterministically predict when these extra frame times will occur.
-However, JWST will not produce enough data in flight to deterministically predict when the extra frame times occur so you'd have to average many frames together.
-For a 64$\times$ 64 subarray, there are almost always 2 line overheads.
-At a rate of about 5/8000 frames of test data, there were 3 line overheads.
-So, in the worst case unlucky scenario with 64$\times$64 subarray data in RAPID mode with 2 groups up the ramp, there could be an extra 1/64 or 1.6 \% increase in the slope due to the ASIC micro code.
-Given that 64$\times$64 frame time is only 0.05 s long, you could easily include hundreds of frames to average out the frame time issue with almost no change in efficiency since JWST acquisition, exposure and dithering overheads would be a much larger fraction of the time.
-I would estimate this would have less than 0.01\% of an effect on flux calibration.
+\clearpage
 

### 2019-05-22 ms.tex
updates to intro based on 2019 perspective

@@
 Several of the science areas, such as supernovae photometry for dark energy measurements will require high accuracy absolute calibration.
-We discuss a program to identify calibrators at the low end of the flux scale that will not saturate the NIRCam full frame mode.
-We obtained ground based photometry and spectroscopy of three clusters to find solar analog G2 V stars and a solar model spectrum to infer the fluxes in the NIRCam bands.
-Additionally, we discuss some of the NIRCam modes that can be used to tie JWST calibrations directly to bright stars which have been calibrated against emissive reference spheres with the Midcourse Space Experiment (MSX).
+We discuss a program to identify solar analog calibrators at the low end of the flux scale that will not saturate wide-band NIRCam imaging in full frame mode.
+We find that solar analog stars in NGC~2420 and NGC~2506 have the best properties for calibration in terms of extinction, age, distance and metallicity.
+We include a catalog of sources and absolutely calibrated photometry in the $g$, $r$, $i$, $z$, $J$, $H$, $K$ and IRAC1 3.6 $\mu$m bands.
+We also provide a catalog of solar analog candidates that are selected from optical spectroscopy that will serve as faint calibrator sources for JWST imaging.
+These faint calibrators serve wide band full frame imaging of current and future ground-based imagers.
 \end{abstract}
@@
 Absolute fluxes are especially important for improving type Ia supernova luminosity distances and thus the expansion history of the Universe \citep[e.g.][]{narayan2016wdnetwork,betoule2014cosmologySN}.
-For exoplanet host stars in the era of Gaia distances, absolutely calibrated photometry is used to make precision measurements of stellar radii, which in turn give high precision planet radii.
 For exoplanet host stars in the era of Gaia distances, absolutely calibrated photometry is used to make precision measurements of stellar radii, which in turn give high precision planet radii \citep[e.g.][]{stassun2017gaiaRadiiMasses}.
@@
 The JWST flux calibration effort has been described in \citet{gordon2009fluxplan1} and \citet{gordon2011fluxplan2}.
-It is still being developed and refined.
-Figure \ref{fig:JWSTcalsWideF} shows several of the sources that will likely be used for flux calibration.
+Figure \ref{fig:JWSTcalsWideF} shows several of the sources that are planned as targets for flux calibration.
 These include three categories: 1) hot stars (white dwarf and OB stars) 2) G-stars (which are solar-like) and 3) A-type stars.
@@
 Many of these spectra will saturate the NIRCam detectors when used in full frame (shown as the middle parts of the black ``error bars'') for wide-band filters.
-The 
 Furthermore, there may be systematic errors when observing faint targets and low detector well depths.
@@
 
-In this report, we discuss a NIRCam-led effort to identify and calibrate stars to add to the JWST sample on the fainter end around $K \approx 15$.
-We choose the method of \citet{rieke2008absIRcal}, which uses solar-like stars for flux calibration.
+In this paper, we discuss a JWST Flux Calibration Working Group effort to identify and calibrate stars to add to the JWST sample on the fainter end at $K \approx 15.4$ to $K \approx 16.3$.
+We use the solar analog method \citep{rieke2008absIRcal,johnson1965solarAnalogMethod,megessier1995solarAnalogCal} for flux calibration.
 The basic rationale is that the Solar spectrum is well measured across JWST's wavelengths \citep[0.6~$\mu$m to 29~$\mu$m][]{gardner2006SSRv} and has highly accurate models for its spectrum.
@@
 Christopher W - points out we should look at the APOGEE data. I see there's overlap for NGC 2420.
+BD = Bonner Durchmusterung catalog
+GSPC = Guide Star Photometric Catalog (e.g. GSPC P330-E)
 

### 2019-05-22 ms.tex
added niriss sat/sensitivy plot

@@
 \includegraphics[width=.48\columnwidth]{calspec_and_new_clust.pdf}
-\caption{CALSPEC models are plotted in comparison to NIRCam saturation and sensitivity limits, as shown in \citet{gordon2011fluxplan2}.
+\includegraphics[width=.48\columnwidth]{calspec_and_new_clust_niriss.pdf}
+\caption{CALSPEC models are plotted in comparison to JWST saturation and sensitivity limits for NIRCam (left) and NIRISS (right), as shown in \citet{gordon2011fluxplan2}.
 The three values shown for each wideband filter are the subarray saturation (upper error limit), full frame saturation (middle circle) and 10~$\sigma$ sensitivity limit in one hour of imaging (lower error limit).
@@
 If we require that a solar mass star have $T_{\rm eff}$ = 5780 +/- 100 K, the cluster would have to be between 0.3 Gyr and 10 Gyr using Dartmouth evolutionary models \citep{dotter2008dartmouth}.
-Furthermore, the age should be $\lesssim$7 Gyr to avoid main sequence turnoff of F-type stars that would have similar colors to solar analogs.
+Furthermore, the age should be $\lesssim$7 Gyr to avoid main sequence turnoff of F-type stars that have similar colors to solar analogs.
 \item {\bf Extinction} Extinction should be as small as possible to minimize the effects of extinction correction to photometry. Of the clusters found, E(B-V) $\lesssim 0.1$.
-\item {\bf Distance Modulus} The cluster must be distant enough to not saturate NIRCam's wide filters in full frame mode.
+\item {\bf Distance Modulus} The clusters should be distant enough that they do not saturate NIRCam or NIRISS wide-band imaging in full frame mode.
 The most easily saturated wide band filter for G stars is the F090W, which corresponds to a G2~V star of 15.9 in the $K$ band.

### 2022-09-13 ms.tex
updates for NGC 2506 LRIS

@@
 
-\slugcomment{\textcolor{red}{NOTE, this is a work in progress}}
+\slugcomment{\textcolor{red}{NOTE, this is will be morphed into a paper appendix}}
 
@@
 The James Webb Space Telescope (JWST) offers unprecedented sensitivity and stability for science.
-Several of the science areas, such as supernovae photometry for dark energy measurements will require high accuracy absolute calibration.
-We discuss a program to identify solar analog calibrators at the low end of the flux scale that will not saturate wide-band NIRCam imaging in full frame mode.
-We find that solar analog stars in NGC~2420 and NGC~2506 have the best properties for calibration in terms of extinction, age, distance and metallicity.
-We include a catalog of sources and absolutely calibrated photometry in the $g$, $r$, $i$, $z$, $J$, $H$, $K$ and IRAC1 3.6 $\mu$m bands.
-We also provide a catalog of solar analog candidates that are selected from optical spectroscopy that will serve as faint calibrator sources for JWST imaging.
-These faint calibrators serve wide band full frame imaging of current and future ground-based imagers.
+Most science areas in astronomy require flux calibration in order to convert brightness measurements into physical flux units.
+We discuss a program to identify solar analog calibrators at the low end of the flux scale that will not saturate most wide-band NIRCam imaging in full frame mode and that can also be used with other Science Instruments for faint calibration.
+We identified two star clusters: NGC~2420 and NGC~2506 to be the best balance of extinction, age, distance and metallicity, where solar type stars can be used for calibration.
+We use NGC~2506 for Cycle 1 JWST flux calibration due to its faintness, which saturates the fewest number of modes.
+We include a catalog of sources and absolutely calibrated photometry in the $K$ band using the WFCAM instrument on UKIRT.
+%$g$, $r$, $i$, $z$, $J$, $H$, $K$ and IRAC1 3.6 $\mu$m bands.
+We provide a small catalog of solar type stars within 1 spectral type of G2V from ground-based optical spectroscopy.
+These faint calibrators serve wide band full frame imaging of JWST as well as future ground-based imagers.
 \end{abstract}
@@
 
-The James Webb Space Telescope \citep[JWST; e.g.][]{gardner2006SSRv} will need absolute calibration to accomplish its science goals.
+The James Webb Space Telescope \citep[JWST; e.g.][]{gardner2006SSRv} will need absolute calibration to accomplish its science goals with a calibration program outlined in \citet{gordon2022absFlux1}.
 One area where accurate flux calibration is especially important is dark energy science, which makes use of type Ia supernovae as standard candles.
@@
 
-The JWST flux calibration effort has been described in \citet{gordon2009fluxplan1} and \citet{gordon2011fluxplan2}.
+The JWST flux calibration effort has been described in \citet{gordon2009fluxplan1}, \citet{gordon2011fluxplan2} and \citet{gordon2022absFlux1}.
 Figure \ref{fig:JWSTcalsWideF} shows several of the sources that are planned as targets for flux calibration.
@@
 We use the solar analog method \citep{rieke2008absIRcal,johnson1965solarAnalogMethod,megessier1995solarAnalogCal} for flux calibration.
-The basic rationale is that the Solar spectrum is well measured across JWST's wavelengths \citep[0.6~$\mu$m to 29~$\mu$m][]{gardner2006SSRv} and has highly accurate models for its spectrum.
+The basic rationale is that the Solar spectrum is well measured across JWST's wavelengths \citep[0.6~$\mu$m to 29~$\mu$m][]{gardner2006SSRv} and has highly accurate models for its spectrum \citep[e.g.][]{gueymard2018solarSpectrum}.
 When solar-like stars are identified, one can use these models to convert from one photometric or spectroscopic band to another.
@@
 The most easily saturated wide band filter for G stars is the F090W, which corresponds to a G2~V star of 15.9 in the $K$ band.
-While the F150W2 ``double-wide'' filter is more easily saturated than F090W, this is filter is unlikely to be used on faint Galaxies because (someone from deep field prog remind me?).
-This means the true distance modulus $(m - M)_0$ should be 12.6 for a solar absolute K=3.28 \citep{binney1998book}.
+While the F150W2 ``double-wide'' filter is more easily saturated than F090W, this is filter is not used as widely in extragalactic surveys, where the wide filters are preferred for photometric redshift \citep[e.g.][]{williams2018JWSTMockCatalog}.
+This means the true distance modulus $(m - M)_0$ should be 12.6 for a solar absolute K=3.27 \citep{willmer2018solarMagnitude}.
 The longer wavelength wide band filters (F200W, F277W, F356W, and F444W) will not saturate for a true distance modulus larger than 11.8.
@@
 
+No cluster could meet all criteria but some had a balance of desirable properties.
 With all these considerations in play, we selected NGC 2420 and NGC 2506 as the best fit for the multiple criteria.
@@
 The subarray to full frame conversion can be checked with medium band filters.
-NGC 2506 is the next-best fits and have somewhat complimentary visibility windows, shown in Figure \ref{fig:clusterVis}. NGC 2420 and NGC 6811 have -0.05 $\le$ [Fe/H] $\le$ 0.04.
+NGC 2420 has -0.05 $\le$ [Fe/H] $\le$ 0.04.
 NGC 2506, is metal poor at [Fe/H]=-0.32, so corrections must be made for changes to G2 V spectra due to metallicity.
 
-\begin{figure}
-\centering
-\includegraphics[width=.4\columnwidth]{cluster_visibilty.pdf}
-\caption{Visibility windows for the three open clusters considered in this report.
-The planned commissioning period is shown with vertical blue dashed lines.}\label{fig:clusterVis}
-\end{figure}
+%\begin{figure}
+%\centering
+%\includegraphics[width=.4\columnwidth]{cluster_visibilty.pdf}
+%\caption{Visibility windows for the three open clusters considered in this report.
+%The planned commissioning period is shown with vertical blue dashed lines.}\label{fig:clusterVis}
+%\end{figure}
 
@@
 After selecting the sources, we discovered that the WEBDA database had parameters that were significantly different from the literature for these individual clusters.
-For example E(B-V)$_\mathrm{WEBDA}$ = 0.16 for NGC 6811 whereas \citet{molendaz2016spec6811} has E(B-V) = 0.05.
+%For example E(B-V)$_\mathrm{WEBDA}$ = 0.16 for NGC 6811 whereas \citet{molendaz2016spec6811} has E(B-V) = 0.05.
 We therefore did a literature search for the most recent available cluster parameters.
 Table \ref{tab:clusterProp} shows the properties gathered from the literature.
-The most up-to-date literature values indicate that all three clusters have low extinction with E(B-V) $<$ 0.1.
-Including uncertainties, the extinctions are actually all consistent with 0.06, but it should be noted that the NGC 2506 uncertainties are likely underestimated since their were derived from a standard error of the mean and may not include systematics.
+Recent literature values indicate that both clusters have low extinction with E(B-V) $<$ 0.1.
 
@@
 NGC 2420\tablenotemark{b}	& 0.04 $\pm$0.03	&  11.88 $\pm$ 0.27	& -0.05 $\pm$ 0.03	& 3 $\pm$ 1 	& 2.2 $\pm$ 0.3 \\
-NGC 2506\tablenotemark{c}	& 0.058 $\pm$ 0.001	&  12.75 $\pm$ 0.10 	& -0.32 $\pm$ 0.03	& 1.85 $\pm$ 0.05 & 3.3 $\pm$ 0.2 \\
-NGC 6811\tablenotemark{d}	& 0.05 $\pm$0.02	& 10.29 $\pm$ 0.14	& 0.04 $\pm$ 0.01 	& 1.0 $\pm$ 0.1 & 1.1 $\pm$ 0.1 \\
+NGC 2506\tablenotemark{c}	& 0.080 $\pm$ 0.006	&  12.71\tablenotemark{a}	 	& -0.36 $\pm$ 0.10			& 2.01 $\pm$ 0.10 & 3.101 $\pm$ 0.017 \\
+%NGC 6811\tablenotemark{d}	& 0.05 $\pm$0.02	& 10.29 $\pm$ 0.14	& 0.04 $\pm$ 0.01 	& 1.0 $\pm$ 0.1 & 1.1 $\pm$ 0.1 \\
 \hline
@@
 The size affects the number of DHS that can be included, so the noise in the DHS spectra over 1.1 -- 1.9$\mu$m at the given saturation limit for a 1 hour transit is shown in column 4 at native R $\sim$ \DHSresApprox\ resolution.}\label{tab:SatSNRsubA}
-\tablenotetext{a}{Distance calculated by taking the visual distance modulus $(m-M)_V$ and subtracting the expected extinction for a Galactic average extinction law \citep{cardelli1989}.}
+\tablenotetext{a}{Distance calculated by taking the visual distance modulus $(m-M)_V$ and subtracting the expected extinction for a Galactic average extinction law  \citep{cardelli1989} applied to a 5800 K star.}
 \tablenotetext{b}{NGC 2420 parameters from \citet{pancino2010chem2420}.}
-\tablenotetext{c}{NGC 2506 parameters from \citet{anthonytwarog2016wiyn2506}. Error bars are formal standard errors of the mean, not necessarily capturing systematics.}
+\tablenotetext{c}{NGC 2506 parameters from \citet{knudstrup2020ngc2506properties}}
 \tablenotetext{d}{NGC 6811 parameters from \citet{molendaz2016spec6811}}
@@
 
-\section{Pan-Starrs}
-\subsection{Pan-Starrs Photometry}
+\section{Photometry}\label{sec:photometry}
+\subsection{Pan-Starrs Photometry}\label{sec:panStarsPhot}
 
-We obtained $grizy$ Pan-Starrs photometry \citep{magnier2013photLadder,schlafly2012photcal,tonry2012panstarrsPhot} for all three clusters.
-Additionally, we used \citet{janes2013keplerPhot} B and V photometry for NGC~6811 which is in the Kepler field because there were more faint source detections.
+We obtained $grizy$ Pan-Starrs photometry \citep{magnier2013photLadder,schlafly2012photcal,tonry2012panstarrsPhot} for all both clusters.
 We also estimated the Pan-Starrs $g$ - $r$ and B-V colors from a Pickles G2~V spectrum using \texttt{pysynphot} \citep{lim2015pysynphot}, the measured extinction shown in Table \ref{tab:clusterProp} with a Milky Way Diffuse R(V)=3.1 \citet{cardelli1989} extinction law.
-Figure \ref{fig:cmdPS} shows the Pan-Starrs and \citet{janes2013keplerPhot} color magnitude diagram for the three clusters along with vertical bars with the expected solar color for each cluster: $g-r$ =0.42, $g-r$ = 0.43 and B-V = 0.67 for NGC~2420, NGC~2506 and NGC~6811 respectively.
-Note that the initial selection of NGC~2420 stars ignored the small extinction and put a higher priority on stars slightly bluer than solar.
+Figure \ref{fig:cmdPS} shows the Pan-Starrs and \citet{janes2013keplerPhot} color magnitude diagram for the three clusters along with vertical bars with the expected solar color for each cluster: $g-r$ =0.42 and $g-r$ = 0.43 for NGC~2420 and NGC~2506 respectively.
+We identified main sequence stars by fitting an iterative sigma clipped 5th polynomial to the color as a function of magnitude.
+We then included all points within 0.04 mag and 0.03 mag from the polynomial as main sequence stars for NGC~2420 and NGC~2506, respectively.
+
+We created 3 levels of priority in assigning slit fibers (MMT Hectospec, NGC~2420) or slit masks (Keck LRIS~NGC 2506).
+The highest priority targets were the ones with $g-r > 0.3$ and $g-r \le0.45$ for NGC~2420 and $g-r > 0.38$ and $g-r \le 0.48$ for NGC~2506.
+We also prioritized targets within  $2 \times 4\arcmin $ for NGC~2420 and $9.5 \times 9.5\arcmin $ for NGC~2506 (based on the LRIS field of view).
+These priority levels preferred fiber or mask selection of stars within a small field of view most close to a G2V spectrum.
 
@@
 \\
-\subfloat[NGC 6811]{
-	\includegraphics[width=0.5\textwidth]{sources_ngc6811.png}
-	\label{fig:cmdNGC6811}
-	}
-	\caption{Color-magnitudes of the three clusters.
+%\subfloat[NGC 6811]{
+%	\includegraphics[width=0.5\textwidth]{sources_ngc6811.png}
+%	\label{fig:cmdNGC6811}
+%	}
+	\caption{Color-magnitudes of the two clusters.
 	The main sequence in each cluster was fit with a polynomial and then three priority levels were chosen for follow-up spectroscopy.
-	The first priority targets were near-solar $g-r$ or B-V colors ($\pm 0.04, 0.03, 0.05$) that were within $\pm$4\arcmin\ of the cluster center (to concentrate in the NIRCam field of view).
+	The first priority targets were near-solar $g-r = 0.42-0.43$ or ($\pm 0.04, 0.03$ for NGC~2420 and NGC~2506, respectively) that were within $\pm$4\arcmin\ of the cluster center (to concentrate in the Science Instrument field of view).
 	The second priority were near-solar $g-r$ or B-V colors but with a wider field of view (1$\degree$) to include G2~V stars that could be observed with larger dithers.
@@
 
-We observed all three clusters with WFCAM on the UKIRT telescope.
-This is the same instrument, pipeline and telescope for the UKIDSS survey.
+We observed both clusters with WFCAM on the UKIRT telescope in queue mode on October 11,25, 26, November 11 and December 29, 2016 (UTC).
+This is the same instrument, pipeline and telescope for the UKIDSS survey for the infrared $JHK$ bands.
+The data were processed automatically by the CASU IR Reduction Software (CIRDS) version 1.202 \citep{irwin2004vistaDataFlowWFCAM}, which created photometric catalogs for every detector array.
+We focused primarily on the one detector centered on the cluster.
 As recommended by the UKIRT pipeline team (Mike Irwin, private communication), we used aperture photometry number 3 (1\arcsec\ radius) for the fluxes in the J, H and K bands.
@@
 
-The stars within the clusters explored will be tied to the measurements of the Sun.
-\citet{rieke2008absIRcal} provide recommended adjustments to 2MASS photometry which match well with the Solar spectrum.
-We can use existing 2MASS measurements of stars within the UKIRT field of view as a reference for the UKIRT photometry.
-There are plenty of sources with 2MASS measurements.
-For NGC 2420, for example, there are 300-400 stars within the neighboring arrays and 800 near the cluster (many of which will be contaminated by crowding).
+We identified over 1000 WFCAM sources in common with the 2MASS survey \citep{skrutskie06}.
+We used these overlapping stars to check for offsets between the 2MASS survey on the WFCAM photometry, as shown in Figure \ref{fig:ukirtVs2MASS}.
+Fainter than $K=14$ gets into the low signal to noise regime for 2MASS, whereas $K<11.5$ approaches saturation with WFCAM, so the stars between those ranges are the most useful on cross-checking photometry.
+We find an offset of UKIRT K - 2MASS K = 0.007 if using all 2MASS and WFCAM points with $11.5 < K \le 14$.
 
@@
 \centering
-\includegraphics[width=.4\columnwidth]{aladin_ngc2420_wfcam_square.png}
-\caption{One of WFCam's 4 detectors near the cluster NGC 2420 which encompasses 315 objects from the 2MASS point source catalog.}\label{fig:wfcam3}
+\includegraphics[width=.9\columnwidth]{ukirt_2mass_NGC_2506.pdf}
+\caption{A comparison of UKIRT and 2MASS photometry for cross-matched sources.}\label{fig:ukirtVs2MASS}
 \end{figure}
+%
+%Straight Horzontal Lines
+%Median UKIRT J - 2MASS J = -0.0090
+%from  1356 points
+%Median UKIRT H - 2MASS H = 0.0130
+%from  1320 points
+%Median UKIRT K - 2MASS K = 0.0255
+%from  1084 points
 
-These steps will be adequate to calibrate to within a few percent.
-To obtain the most accurate possible calibration to 2MASS requires that slight photometric offsets in the 2MASS catalog in different areas of the sky be identified and corrected.
-These offsets can be identified by looking of the behavior of 2MASS-W1 colors, selecting a subset of stars (e.g., between A and mid-G) that are particularly well behaved in this color (e.g., no strong absorptions).
-Once this step has been completed, it will still be necessary to tie the corrected 2MASS system into true absolute calibration.
+%Median of all crossmatched points with K $>$ 12 and $| UKIRT - 2MASS | < 0.2$.
 
@@
 
-\subsection{Hectospec Observations}
+\subsection{Hectospec Observations}\label{sec:hectoObs}
 
-We used the Hectospec instrument on the MMT \citep{fabricant2005hectospec,mink2007hectoFibers} to obtain spectra of candidate solar analogs in the clusters.
+We used the Hectospec instrument on the MMT \citep{fabricant2005hectospec,mink2007hectoFibers} to obtain spectra of candidate solar analogs in NGC~2420.
 We observed NGC~2420 with two fiber configurations in the Spring and Fall of 2016.
@@
 
+\subsection{Keck LRIS Observations}\label{sec:keckLRIS}
+We observed NGC~2506 on December 6, 2018 with Keck LRIS using custom slit masks, with target priority outlined in Section \ref{sec:panStarsPhot}.
+We designed masks with slit widths of 0.7\arcsec $\times$ 5\arcsec, which matched well to the seeing on December 6, 2018 near 0.7\arcsec.
+We used the D560 dichroic and 600/4000 grating to collect blue spectra from 330 nm to 560 nm, which includes the temperature sensitive absorption lines from 400 to 450 nm.
+The slit and grating combination resulted in a resolution of $\sim$0.3 nm for our slit widths or smaller in the case of good seeing.
+The LRIS red arm was not used for spectral typing.
+We took dome flats and HgNeArCdZnKrXe  arc lamp exposures for wavelength calibration and direct observations of NGC~2506 field for source identification and alignment.
+
+We used the \texttt{pypeit} pipeline to extract spectra of all sources \citep{prochaska2020pypeit}.
+Some additional adjustments were needed to find spectral types of the stars.
+A -35 km/s velocity (wavelength) adjustment correction was needed to shift all spectra to match the stellar templates from the \texttt{mkclass} \citep{gray2014classification} library.
+As with the Hectospec data described in Section \ref{sec:hectoObs}, we rectify the spectra by fitting to a third order spline with a 2$\sigma$ iterative clipping rejection and 4 splin knots.
+
+Figure \ref{fig:SpecRectLRIS} shows the rectified spectra for one of the slit masks with several temperature-sensitive lines highlighted.
+
+\begin{figure}[!hbtp]
+\centering
+\includegraphics[width=.7\columnwidth]{all_spec_good_wavecal_2019-02-06-07_combined_spec_maskAnR1_rectified.pdf}
+\caption{Rectified LRIS spectra of Solar Analog candidates are shown for one slit mask.}\label{fig:SpecRectLRIS}
+\end{figure}
+
+\clearpage
 \subsection{Spectral Classification}
@@
 Our Hectospec data with the 600 gpm grating has a spectral resolution of 1.9 to 2.2$\AA$ so we convolve it with a Gaussian kernel to match the 3.6$\AA$ library.
+Our Keck LRIS data have a spectral resolution near 0.3$\AA$, so we use the 0.22$\AA$ spectral template library.
 We use 3 iterations, the \texttt{mkclass} default.
@@
 
+We show the final color magnitudes for NGC~2420 and NGC~2506 in Figure \ref{fig:finalCandidatesCM} after selection of spectroscopically confirmed near-G2V $pm$ 1 temperature class for targets that are within a compact field of view.
+
 \subsection{Visual Classification}
 
-As recommended by C. Corbally, the \texttt{mkclass} classifications of near-solar stars were checked by eye.
+The \texttt{mkclass} classifications of near-solar stars were checked by eye, which is a helpful verification for \texttt{mkclass} (Chris Corbally, private communication).
 A graphical user interface explorer was made to compare template classification spectra with the observed Hectospec spectra\footnote{https://github.com/eas342/mkclassfication\_viewer}.
 Figure \ref{fig:0738284p2133class} shows the Hectospec spectrum of a source at 07:38:28.4 +21:33 that \texttt{mkclass} identifies as G2~V.
-The line ratios of Ca I 4226~$\AA$, H$\delta$, H$\gamma$ and Fe I lines are most consistent with a G2 V type.
+The line ratios of Ca I 4226~$\AA$, H$\delta$, H$\gamma$ and Fe I lines are most consistent with a G2 V type, within 1 temperature class.
 
@@
 \subfloat[NGC 2506]{
-	\includegraphics[width=0.5\textwidth]{colormag_NGC_2506_near_G2_V.pdf}
+	\includegraphics[width=0.5\textwidth]{colormag_NGC_2506_near_G2_V_g-r.pdf}
 	\label{fig:cmdNGC2506nearG2V}
 	}
-\\
-\subfloat[NGC 6811]{
-	\includegraphics[width=0.5\textwidth]{colormag_NGC_6811_near_G2_V.pdf}
-	\label{fig:cmdNGC6811nearG2V}
-	}
-	\caption{Color-magnitudes of the three clusters with the near-solar stars identified from spectra.
-	}
-	\label{fig:cmdPSnearG2V}
-\end{figure*}
+%\\
+%\subfloat[NGC 6811]{
+%	\includegraphics[width=0.5\textwidth]{colormag_NGC_6811_near_G2_V.pdf}
+%	\label{fig:cmdNGC6811nearG2V}
+%	}
+%	\caption{Color-magnitudes of the three clusters with the near-solar stars identified from spectra.
+%	}
+%	\label{fig:cmdPSnearG2V}
+\end{figure*}\label{fig:finalCandidatesCM}
 
@@
 
-Thanks to Daniel Kiminki and John Stauffer for the selection of open clusters for this work and for finding targets based on initial data.
+Thanks to Dani Kiminki and John Stauffer for the selection of open clusters for this work and for finding targets based on initial data.
 Thanks to Richard Gray and Chris Corbally for their help in stellar classification and guidance with the Hectospec observations.
